### 2013-09-28 paper/paper.tex
added paper

\documentclass[12pt]{IEEEtran} % .... using IEEE Transaction style
\usepackage{graphics}

% the following is to get inch margins on a letter-size paper
\setlength{\topmargin}{0pt}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{9.0in}
\setlength{\footskip}{0.5in}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
\setlength{\textwidth}{6.5in}

\begin{document}
\title{A Java Wrapper For Embarresingly Parallel Programs}
\author{Jacob Schwartz}
\maketitle

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat
cupidatat non proident, sunt in culpa qui officia deserunt mollit anim
id est laborum.
\end{abstract}

\section{Introduction}

This is just a test. This is just a test (a line break follows)\\
this is just a test.

\subsection*{Background}

Figure \ref{fig:figure} shows .... Has to be compiled {\bf twice} to get the 
figure reference right. AODV \cite{aodv} is an ad hoc roting protocol.

Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat
cupidatat non proident, sunt in culpa qui officia deserunt mollit anim
id est laborum.

\begin{figure}[bht]
\begin{center}
{\resizebox{2in}{!}{\includegraphics{figures/drawing}}}
%        {x-dim}{y-dim}
% ! means proportional scaling
\end{center}
\caption{Caption of the figure.}
\label{fig:figure}
\end{figure}

\begin{itemize}
\item One
\item Two
\item There
\end{itemize}

\begin{enumerate}
\item One
\item Two
\item There
\end{enumerate}

\begin{description}
\item[Item 1:] Ut enim ad minim veniam, quis nostrud exercitation ullamco
laboris nisi ut aliquip ex ea commodo consequat.
\item[Item 2:]  Duis aute irure dolor in reprehenderit in voluptate
velit esse cillum dolore eu fugiat nulla pariatur.
\item[Item 3:]  Excepteur sint occaecat cupidatat non proident, sunt in
culpa qui officia deserunt mollit anim id est laborum.
\end{description}

\begin{table}[htdp]
\caption{default}
\begin{center}
\begin{tabular}{|c|c|}
\hline
jljljljl&jkkjk\\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

\section{Experiment}

The results of experiments are

$$\frac{3}{2}$$

shown in Figure~\ref{fig:graph}.

\begin{figure}[bht]
\begin{center}
%{\resizebox{3.4in}{!}{\includegraphics{experiment/plot}}}
%        {x-dim}{y-dim}
% ! means proportional scaling
\end{center}
\caption{Caption of the graph.}
\label{fig:graph}
\end{figure}

\begin{thebibliography}{1}

\bibitem{aodv}
C. Perkins,  E. Belding-Royer, and  S. Das, ``\emph{Ad hoc On-Demand
Distance Vector (AODV) Routing},'' IETF RFC 3561, July 2003.

\end{thebibliography}

\end{document}

### 2013-09-30 src/main/java/edu/unh/schwartz/parawrap/Chunk.java
Started test stuff

@@ -9,7 +9,7 @@ import java.io.IOException;
  * Piece of work to do be done by the <code>Worker</code>s. Also contains
  * statstical information that can be used to get the ideal configuration.
  */
-public final class Chunk
+public final class Chunk implements Comparable<Chunk>
 {
     /**
      * The number of header lines used in the output file.
@@ -161,6 +161,15 @@ public final class Chunk
     public String getOutFileName()
     {
         return this.directory.getAbsolutePath() + "out";
+    }
+
+    /**
+     * {@inheritDoc}
+     */
+    @Override 
+    public int compareTo(final Chunk c) 
+    {
+        return 0;
     }
 
     /**

### 2013-09-30 src/main/java/edu/unh/schwartz/parawrap/io/Manipulator.java

@@ -74,11 +74,11 @@ public final class Manipulator
                 dir.mkdir();
 
                 // Make the new file
-                final File in = new File(dir.getName() + "/in");
-                in.createNewFile();
+                // final File in = new File(dir.getName() + "/in");
+                // in.createNewFile();
 
                 // Write the content to a file
-                final PrintWriter inWriter = new PrintWriter(in);
+                final PrintWriter inWriter = new PrintWriter(dir.getAbsolutePath() + "/in");
                 inWriter.println(content);
                 inWriter.close();
 

### 2013-09-30 src/test/java/edu/unh/schwartz/parawrap/io/ManipulatorTest.java

@@ -1,0 +1,27 @@
+package edu.unh.schwartz.parawrap.io;
+
+import edu.unh.schwartz.parawrap.Chunk;
+import java.io.IOException;
+import java.util.concurrent.PriorityBlockingQueue;
+import org.junit.Test;
+
+import static org.junit.Assert.assertTrue;
+
+public class ManipulatorTest
+{
+    @Test
+    public void splitTest()
+    {
+        Manipulator manip = new Manipulator("^$");
+        try
+        {
+            manip.split("src/test/java/edu/unh/schwartz/parawrap/io/in.txt");
+        }
+        catch (IOException e)
+        {
+            assertTrue(e.getMessage(), false);
+        }
+        PriorityBlockingQueue<Chunk> splits = manip.getChunks();
+        assertTrue("Incorrect number of chunks" , splits.size() == 16);
+    }
+}

### 2013-09-30 src/test/java/edu/unh/schwartz/parawrap/io/SpliterTest.java

@@ -1,49 +1,0 @@
-package edu.unh.schwartz.parawrap.io;
-
-import edu.unh.schwartz.parawrap.Chunk;
-import java.io.IOException;
-import java.util.concurrent.PriorityBlockingQueue;
-
-/**
- * This is a test class for the splitter submodule. It takes a file and a 
- * regex pattern to split on. It will return a collection of strings that will
- * be the resulting split.
- */
-public class SpliterTest
-{
-    private Manipulator manip;
-
-    public SpliterTest(String regex)
-    {
-        manip = new Manipulator(regex);
-    }
-    
-    public PriorityBlockingQueue<Chunk> execute(String fileName) 
-        throws IOException
-    {
-        manip.split(fileName);
-        return manip.getChunks();
-    }
-
-    public static void main(String[] args)
-    {
-        if (args.length != 2)
-        {
-            System.err.println("There should be two arguments:");
-            System.err.println("\t- The Regex Pattern\n\t- A File Name");
-            return;
-        }
-        String regexPattern = args[0];
-        String fileName = args[1];
-        SpliterTest t = new SpliterTest(regexPattern);
-        try
-        {
-            PriorityBlockingQueue<Chunk> splits = t.execute(fileName);
-            System.out.println("Found " + splits.size() + " pieces");
-        }
-        catch (IOException e)
-        {
-            System.err.println(e.getMessage());
-        }
-    }
-}

### 2013-10-01 paper/paper.tex
Paper outline and new git ignore file

@@
-\documentclass[12pt]{IEEEtran} % .... using IEEE Transaction style
+\documentclass[12pt]{article} 
 \usepackage{graphics}
@@
 
-\subsection*{Background}
-
-Figure \ref{fig:figure} shows .... Has to be compiled {\bf twice} to get the 
-figure reference right. AODV \cite{aodv} is an ad hoc roting protocol.
-
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
-veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
-commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
-velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat
-cupidatat non proident, sunt in culpa qui officia deserunt mollit anim
-id est laborum.
-
-\begin{figure}[bht]
-\begin{center}
-{\resizebox{2in}{!}{\includegraphics{figures/drawing}}}
-%        {x-dim}{y-dim}
-% ! means proportional scaling
-\end{center}
-\caption{Caption of the figure.}
-\label{fig:figure}
-\end{figure}
-
 \begin{itemize}
-\item One
-\item Two
-\item There
+\item History of parallelism and java?
+\item Discuss embarresingly parallel (2 paragraphs)
+\item What we are going to do (1 page, one paragraph about problem)
+\item Summary of results
 \end{itemize}
 
-\begin{enumerate}
-\item One
-\item Two
-\item There
-\end{enumerate}
+\section{Background}
 
-\begin{description}
-\item[Item 1:] Ut enim ad minim veniam, quis nostrud exercitation ullamco
-laboris nisi ut aliquip ex ea commodo consequat.
-\item[Item 2:]  Duis aute irure dolor in reprehenderit in voluptate
-velit esse cillum dolore eu fugiat nulla pariatur.
-\item[Item 3:]  Excepteur sint occaecat cupidatat non proident, sunt in
-culpa qui officia deserunt mollit anim id est laborum.
-\end{description}
+What the problem was in depth
 
-\begin{table}[htdp]
-\caption{default}
-\begin{center}
-\begin{tabular}{|c|c|}
-\hline
-jljljljl&jkkjk\\
-\hline
-\end{tabular}
-\end{center}
-\label{default}
-\end{table}%
+what we decided to do
 
-\section{Experiment}
+improvmenets made, splitter merger etc
 
-The results of experiments are
+\section{Proposed Solution}
 
-$$\frac{3}{2}$$
+Break down the components. Have a UML diagram here first
 
-shown in Figure~\ref{fig:graph}.
+\section{Results}
 
-\begin{figure}[bht]
-\begin{center}
-%{\resizebox{3.4in}{!}{\includegraphics{experiment/plot}}}
-%        {x-dim}{y-dim}
-% ! means proportional scaling
-\end{center}
-\caption{Caption of the graph.}
-\label{fig:graph}
-\end{figure}
+Tables charts, etc
+
+\section{Conclusion}
+
+Future work \\
+if we had a do over\\
+
+current plans for improvement
 

### 2013-10-02 paper/paper.tex
WOrk on background of paper

@@
 \usepackage{graphics}
+\usepackage{setspace}
 
@@
 
+\doublespacing
 \begin{document}
@@
 
-What the problem was in depth
+BACKGROUND ON WORK WITH DAVE. INTRO TO KAKS
 
-what we decided to do
+Instead of attempting to rewrite the preexisting program, blah. Trying to
+parallelize the serial KaKs Calculator program would have presented several
+problems: introducing bugs, breaking the KaKs algorithm, and the learning curve
+of C++ threading. With such a short time before results were needed, a different
+approach was necessary. A simple Java program was written to break up the input
+and spawn threads that would run BLANKS's KaKs Calculator. When the input was
+calculated, the contents of the output files was concatenated together to
+produce a final input. MORE?
 
-improvmenets made, splitter merger etc
+The KaKs Calculator is not the only embarresingly parallel program that has the
+potential to take several days to run on a data set. In fact, there are several
+embarresingly parallel programs in the biological sciences. TALK ABOUT OTHER
+PROGRAMS HERE. With this multitude of applications that would benefit from
+parallelism, it was obvious that the wrapper program has potential outside of
+this project.
+
+TALK ABOUT PAPER HERE. AND MAYBE THE POWERPOINT TOO.
+
+The original wrapper was also written very quickly due to the impending
+deadline. In this version of the wrapper, several components are being added.
+First off, there is a wizard style menu that will allow the end-user to select
+not only the program that wish to use, but also to manage other settings for the
+run. A new IO class splits the input and merges the output more 
+efficiently. Lastly, in order to look at how well the wrapper performs, 
+the threads keep their own statstics. These statstics will not only be used to 
+find potential enhancements but also will help end-users of the wrapper
+determine whether their use of the wrapper is efficient.
 
@@
 Break down the components. Have a UML diagram here first
+
+splitter
+
+merger
+
+wizard
+
+Lastly, the worker threads will keep records during the execution of a set of 
+work. The threads records its uptime and the number of pieces of work it
+executes on. Also, the runtime for each piece of work is recorded. These will be
+used by the end user to determine if their run is ideal or if they may need to
+change some settings to make it work faster next time. The statistics can also
+give the developers of the wrapper an idea on what can be implemented in order
+make it as fast as possible for a user.
 

### 2013-10-05 paper/paper.tex
Worked more on paper

@@
 \begin{document}
-\title{A Java Wrapper For Embarresingly Parallel Programs}
+\title{A Java Wrapper For Embarresingly Parallel Problems}
 \author{Jacob Schwartz}
@@
 \begin{abstract}
-Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
-veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
-commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
-velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat
-cupidatat non proident, sunt in culpa qui officia deserunt mollit anim
-id est laborum.
+An embarresingly parallel, also called pleasing parallel, problem is one that 
+can easily be broken up into BLANK that do not need to know about one another.
+Several problems in the biological sciences are embarrsingly parallel but they
+are difficult to rewrite to use multithreading, because they are either poorly
+written or too complex. We have written a wrapper, implemented in Java, that
+will execute the serial program in several threads. RESULTS SENTENCE. More
+statistics, savable configurations and BLANK will be implemented next, in
+addition to BLANK.
 \end{abstract}
@@
 
-This is just a test. This is just a test (a line break follows)\\
-this is just a test.
+HISTORY OF PARALLELISM
 
-\begin{itemize}
-\item History of parallelism and java?
-\item Discuss embarresingly parallel (2 paragraphs)
-\item What we are going to do (1 page, one paragraph about problem)
-\item Summary of results
-\end{itemize}
+DISCUSS EMBARRESINGKLY PARALLEL (GET 3 LINKS BEFORE HAND)
+
+TALK ABOUT BIOLOGICAL SCIENCES AND KAKS?
+
+WHAT ARE WE GOING TO DO
+
+SUMMARY OF RESULTS
 
@@
 
-BACKGROUND ON WORK WITH DAVE. INTRO TO KAKS
+BACKGROUND ON WORK WITH DAVE. INTRO TO KAKS.
 
@@
 
-splitter
+The KaKs Calculator is not the only program to used the wrapper; there are
+various potential programs that the wrapper could support. SENTANCE. The wrapper
+needs to support various kinds of input files and be able to chunk up the work
+accordingly. The KaKs Calculator's input consists of a header and then two
+protein sequence lines followed by a blank line. The wrapper will use that blank
+line to know when one chunk of work has ended and another has begun. The user
+can input their own regular expression to determine what lines of input make up
+what chunks. This will occur in the ChunkManager class.
 
-merger
+The other purpose of the ChunkManager class is to combine the resulting chunks 
+back together when the worker threads have finished. MORE
 
-wizard
+As more features are added to the wrapper and as more programs start to use the
+wrapper, there are more choices for the end-user to make in regards to how they
+want their program to execute. The number of threads to use, various flags for
+the executable and blank are just a few choice they can make. A start-up wizard
+is displayed at runtime to systimatically allow the end-user to choose the
+settings for the run. The ConfigWizard class brings the user through this
+process and creates an instance of Configuration when it is completed to save
+the user's settings.
 
@@
 give the developers of the wrapper an idea on what can be implemented in order
-make it as fast as possible for a user.
+make it as fast as possible for a user. The statistics for each thread can be
+found in the Worker subclass and the individual Chunk classes will store their
+own statstics about runtime and size.
 
@@
 
-Future work \\
-if we had a do over\\
+Conclusions gathered from results.
 
-current plans for improvement
+There are several next steps in the pipeline. In addition to using the
+statistics to try to boost speed, adding savable configurations is at the top of
+the list. This will allow users to use the same configuration without having to
+go through the wizard if they need to redo a run. More extensive unit testing
+will be implemented. The ability to chunk multiple pieces of work may be
+implemented in order to avoid potential start up costs in the executable. 
+Finally, other  pleasing parallel problems will be executed by the wrapper so 
+that more potential features will be discovered. MORE
+
+Using Java was a good choice for implementation ease and future implementation
+extension by others, but it may not produce the fastest results. Other languages
+like Hadoop or blank may have been better due to their parallel nature. DO SOME
+RESEARCH. Another approach that could have been taken is one similar to the
+bitches in Washington: going to the cloud. WHY THEY WOULD BE BETTER. HOW IT
+COULD BE IMPLEMENTED.
 

### 2013-10-10 paper/paper.tex
More papaer

@@
 \usepackage{setspace}
+\usepackage{cite}
 
@@
 
-Instead of attempting to rewrite the preexisting program, blah. Trying to
-parallelize the serial KaKs Calculator program would have presented several
-problems: introducing bugs, breaking the KaKs algorithm, and the learning curve
-of C++ threading. With such a short time before results were needed, a different
-approach was necessary. A simple Java program was written to break up the input
-and spawn threads that would run BLANKS's KaKs Calculator. When the input was
-calculated, the contents of the output files was concatenated together to
-produce a final input. MORE?
+Instead of attempting to rewrite the preexisting program, we decided it would be
+better to look at other options. Trying to parallelize the serial KaKs 
+Calculator program could present several problems: introducing bugs, breaking 
+the KaKs algorithm, and the learning curve of C++ threading. We decided a 
+different approach was neccessary, mostly due to the short time table to produce
+results. A simple Java program was written to break up the input and spawn 
+threads that would run BLANKS's KaKs Calculator\cite{blah}. When the input was 
+calculated, the contents of the output files was concatenated together 
+to produce a final input.
 
@@
 embarresingly parallel programs in the biological sciences. TALK ABOUT OTHER
+
+BLAST, two other things are
+
 PROGRAMS HERE. With this multitude of applications that would benefit from
@@
 
-TALK ABOUT PAPER HERE. AND MAYBE THE POWERPOINT TOO.
+% TALK ABOUT PAPER HERE. AND MAYBE THE POWERPOINT TOO.
 
@@
 
-The KaKs Calculator is not the only program to used the wrapper; there are
-various potential programs that the wrapper could support. SENTANCE. The wrapper
-needs to support various kinds of input files and be able to chunk up the work
-accordingly. The KaKs Calculator's input consists of a header and then two
-protein sequence lines followed by a blank line. The wrapper will use that blank
-line to know when one chunk of work has ended and another has begun. The user
-can input their own regular expression to determine what lines of input make up
-what chunks. This will occur in the ChunkManager class.
+The KaKs Calculator is not the only program to use the wrapper; there are
+various potential programs that the wrapper could support. The only requirements
+for the this program are that it process the input in an embarresingly parallel
+manner and that the input comes from a file and the processed results are also
+writen to a file. The wrapper needs to support various kinds of input files and 
+be able to chunk up the work accordingly. The KaKs Calculator's input consists 
+of a header and then two protein sequence lines followed by a blank line. The 
+wrapper will use that blank line to know when one chunk of work has ended and 
+another has begun. The user can input their own regular expression to determine 
+what lines of input make up what chunks. This will occur in the ChunkManager 
+class.
 
 The other purpose of the ChunkManager class is to combine the resulting chunks 
-back together when the worker threads have finished. MORE
+back together when the worker threads have finished. Once the work has been
+down, all of the seperate results are spread across several files. The
+ChunkManager's second job is to retrieve those results and construct a real
+output file. The real output file must look the same as the output file would
+look if the program were run serially; the output must come in the same order as
+the inputs in the input file and headers must be added to the top, if
+applicable.
 

### 2013-10-11 paper/paper.tex
More papaer

@@
 An embarresingly parallel, also called pleasing parallel, problem is one that 
-can easily be broken up into BLANK that do not need to know about one another.
+can easily be broken up into work that does not need to know about one another.
 Several problems in the biological sciences are embarrsingly parallel but they
@@
 will execute the serial program in several threads. RESULTS SENTENCE. More
-statistics, savable configurations and BLANK will be implemented next, in
-addition to BLANK.
+statistics, savable configurations and more options will be implemented next, in
+addition to better testing and refactored.
 \end{abstract}
@@
 \section{Introduction}
-
-HISTORY OF PARALLELISM
 
@@
 
-WHAT ARE WE GOING TO DO
-
-SUMMARY OF RESULTS
+In this paper, I am going to propose a program that will call the serial
+programs on several Java threads. This program will act like the serial
+application, reading the input the same and creating the output in the same
+format. My wrapper program wraps any embarresingly parallel command line program
+that reads from a file, writes to a file and the input can be broken up into
+work units by a regular expression. SUMMARY OF RESULTS to end the paragraph.
 
@@
 potential to take several days to run on a data set. In fact, there are several
-embarresingly parallel programs in the biological sciences. TALK ABOUT OTHER
-
-BLAST, two other things are
-
-PROGRAMS HERE. With this multitude of applications that would benefit from
-parallelism, it was obvious that the wrapper program has potential outside of
-this project.
+embarresingly parallel programs in the biological sciences. The Basic Local
+Alignment Search Tool (BLAST) \cite{BLAST} is a common program used to find
+similarities between sequences and then compares them to databases to calculate
+the statistical significance. Another program we have been looking at is called
+Trinity. Trinity claims to be an efficient way to do de novo reconstruction of
+transcriptomes from mRNA sequence data. With this variety of applications that 
+would benefit from parallelism, it was obvious that the wrapper program has 
+potential outside of this project.
 
@@
 
-Break down the components. Have a UML diagram here first
+A UML Diagram will go here
 
@@
 Finally, other pleasing parallel problems will be executed by the wrapper so 
-that more potential features will be discovered. MORE
+that more potential features will be discovered.
 
 Using Java was a good choice for implementation ease and future implementation
-extension by others, but it may not produce the fastest results. Other languages
-like Hadoop or blank may have been better due to their parallel nature. DO SOME
-RESEARCH. Another approach that could have been taken is one similar to the
-bitches in Washington: going to the cloud. WHY THEY WOULD BE BETTER. HOW IT
-COULD BE IMPLEMENTED.
+extension by others, but it may not produce the fastest results. Languages
+like Hadoop, Clojure or other multithread oriented language may have been better
+due to their parallel nature. Another approach that could have been taken is one
+similar to the people in Washington: going to the cloud. Using a networked 
+solution like MPI or a cloud solution like Amazon instances. (More will go here
+when I added in more previous work from others)
 
 \begin{thebibliography}{1}
-
-\bibitem{aodv}
-C. Perkins,  E. Belding-Royer, and  S. Das, ``\emph{Ad hoc On-Demand
-Distance Vector (AODV) Routing},'' IETF RFC 3561, July 2003.
 

### 2013-10-11 paper/paper.tex
Fuinished RD of paper

@@
 
-DISCUSS EMBARRESINGKLY PARALLEL (GET 3 LINKS BEFORE HAND)
+The embarresingly parallel class of problems is defined as a problem when the
+computation graph is disconnected. The computation graph consists of nodes that
+represent the functions or processes and the data being passed from one process
+to another is displayed in the graph as edges. If the graph is disconnected, 
+none of the processes need to communicate to complete the computations. In a 
+practical situtation, there will be some internode communication to set up the 
+problem and then again to accumulate the results back together. Also known as
+pleasingly parallel problems, they can also easy be performed on a cluster of 
+servers or in any kind of distributed network, due to its lack of dependencies. 
+The term  embarresingly parallel was coined by Geoffrey Fox in his book, 
+\underline{Parallel Programming Works!} \cite{book}
 
-TALK ABOUT BIOLOGICAL SCIENCES AND KAKS?
+Programs in the field of Biology and Genetics often analyze long strings of
+characters, whether they are DNA, RNA or protein sequences. In addition to the
+large file sizes, there is a lot of processing that goes into comparing several
+characters. This time adds up when there are thousands of strings to process.
+However, these sequences often to not relate to each other and can be processed
+independently. Using the embarresingly parallel approach, the processing time
+for all of the sequences can be cut down exponentially with very minimal effort
+by the programmer.
 
@@
 
-BACKGROUND ON WORK WITH DAVE. INTRO TO KAKS.
+Originally, I was assisting with research into different forms of the species 
+\emph{Cicer arietinum}, the chikckpea. The two main forms, Kabuli and Desi, are
+very different in size and color but we mostly wanted to see why the Desi is
+more disease resistance and have more effective root nodule symbiosis and why
+the Kabuli has a large but soft shell. These two types are both cultivated and
+have been under human selection for several thousand years. We wanted to use a
+Ka/Ks equation to quantify the evelution and selection of these chickpeas. We
+found a Ka/Ks program writen by Zhang et al. from the Beijing Institute of 
+Genomics \cite{kaks} but had three varients that we wanted to be analyzed, each 
+with thousands of sequences to process. The Ka/Ks Calculator program takes
+somewhere from five to thirty seconds to process one pair of sequences.
 
 Instead of attempting to rewrite the preexisting program, we decided it would be
-better to look at other options. Trying to parallelize the serial KaKs 
-Calculator program could present several problems: introducing bugs, breaking 
-the KaKs algorithm, and the learning curve of C++ threading. We decided a 
-different approach was neccessary, mostly due to the short time table to produce
-results. A simple Java program was written to break up the input and spawn 
-threads that would run BLANKS's KaKs Calculator\cite{blah}. When the input was 
-calculated, the contents of the output files was concatenated together 
-to produce a final input.
+better to look at other options to process the sequences faster. Trying to 
+parallelize the serial Ka/Ks program could present several problems: introducing
+bugs, breaking the algorithm, dealing with the learning curve of C++ threading. 
+We decided a  different approach was neccessary, mostly due to the short time we
+had to produce results. A simple Java program was written to break up the input 
+and spawn  threads that would run the Ka/Ks Calculator process. When the input 
+was calculated, the contents of the output files was concatenated together to 
+produce a final input.
 
@@
 \begin{thebibliography}{1}
-
+\bibitem{book}
+Fox G., Williams R., and Messina G., ``\emph{Parallel Programming Works!},'', 
+Morgan Kaufmann, May 1994
+\bibitem{kaks}
+Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., ``\emph{KaKs Calculator: 
+calculating Ka and Ks through model selection and model averaging.},'',
+Genomics Proteomics Bioinformatics, November 2006.
+\bibitem{BLAST}
+http://blast.ncbi.nlm.nih.gov/Blast.cgii
 \end{thebibliography}

### 2013-10-31 examples/kaks/KaKs_Calculator1.2/src/KaKs.cpp
Various fixes so the KaKs example works

@@ -1,0 +1,619 @@
+/************************************************************
+* Copyright (C) 2005, BGI of Chinese Academy of Sciences
+* All rights reserved.
+ 
+* Filename: KaKs.cpp
+* Abstract: Declaration of KAKS class including several methods.
+
+* Version: 1.0
+* Author: Zhang Zhang (zhanghzhang@genomics.org.cn)
+* Date: Feb.2, 2005
+
+*************************************************************/
+
+#include "KaKs.h"
+
+KAKS::KAKS() {
+
+	string items[] = {"Sequence", "Method", "Ka", "Ks", "Ka/Ks", 
+		  			  "P-Value(Fisher)", "Length", "S-Sites", "N-Sites", "Fold-Sites(0:2:4)",
+					  "Substitutions", "S-Substitutions", "N-Substitutions", "Fold-S-Substitutions(0:2:4)", "Fold-N-Substitutions(0:2:4)", 
+					  "Divergence-Time", "Substitution-Rate-Ratio(rTC:rAG:rTA:rCG:rTG:rCA/rCA)", "GC(1:2:3)", "ML-Score", "AICc",
+					  "Akaike-Weight", "Model"};  //21 outputing items
+	
+	//Format of outputing parameters
+	int i;
+	for (i=0; i<sizeof(items)/sizeof(string); i++) titleInfo.push_back(items[i]);
+
+	//Load Methods' Names and References for -h in linux, also for windows' tool tip
+	method_name.push_back("NG");   method_ref.push_back("Nei, M. and Gojobori, T. (1986)");
+	method_name.push_back("LWL");  method_ref.push_back( "Li, W.H., Wu, C.I. and Luo, C.C. (1985)");
+	method_name.push_back("LPB");  method_ref.push_back("Li, W.H. (1993) and Pamilo, P. and Bianchi, N.O. (1993)");
+	method_name.push_back("MLWL"); method_ref.push_back("Tzeng, Y.H., Pan, R. and Li, W.H. (2004)");
+	method_name.push_back("MLPB"); method_ref.push_back("Tzeng, Y.H., Pan, R. and Li, W.H. (2004)");
+	method_name.push_back("GY");   method_ref.push_back("Goldman, N. and Yang, Z. (1994)");
+	method_name.push_back("YN");   method_ref.push_back("Yang, Z. and Nielsen, R. (2000)");
+	method_name.push_back("MYN");  method_ref.push_back("Zhang Z., Jun L. and Jun Y. (2006)");
[…]

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/Chunk.java

@@ -152,7 +152,7 @@ public final class Chunk implements Comparable<Chunk>
      */
     public String getInFileName()
     {
-        return this.directory.getAbsolutePath() + "in";
+        return this.directory.getAbsolutePath() + "/in";
     }
 
     /**
@@ -160,7 +160,16 @@ public final class Chunk implements Comparable<Chunk>
      */
     public String getOutFileName()
     {
-        return this.directory.getAbsolutePath() + "out";
+        return this.directory.getAbsolutePath() + "/out";
+    }
+
+    /**
+     * {@inheritDoc}
+     */
+    @Override 
+    public int hashCode() 
+    {
+        return this.content.hashCode();
     }
 
     /**

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/ParallelWrapper.java

@@ -55,8 +55,12 @@ final class ParallelWrapper
 
         final WorkerPool wp = new WorkerPool(config, chunks);
         wp.start();
-        manip.merge(config.getOutputDirectoryName());
-        manip.printStats(wp.getStats());
+        manip.merge(config.getOutputDirectory() + "/done.txt");
+        if (config.makeStats())
+        {
+            manip.printStats(wp.getStats(), config.getOutputDirectory());
+        }
+        manip.cleanUp();
     }
 
     /**
@@ -73,7 +77,7 @@ final class ParallelWrapper
             System.out.println("Opening Configuration Wizard");
             final Configuration config = 
                 ConfigWizard.getInstance().createConfiguration();
-            // start(config);
+            start(config);
         }
         // First command line arg is a configuration file
         // else if (args.length == 1)

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/config/Configuration.java

@@ -214,21 +214,33 @@ public final class Configuration
         return this.splitPattern;
     }
 
-    public String getOutputDirectoryName()
+    /**
+     * @return the directory for the final output
+     */
+    public String getOutputDirectory()
     {
         return this.outDirName;
     }
 
+    /**
+     * @return the path to the executable
+     */
     public String getExecutable()
     {
         return this.execPath;
     }
 
+    /**
+     * @return the flag used to mark the input file for the executable
+     */
     public String getInFlag()
     {
         return this.inFlag;
     }
 
+    /**
+     * @return the flag used to mark the output file for the executable
+     */
     public String getOutFlag()
     {
         return this.outFlag;
@@ -259,8 +271,20 @@ public final class Configuration
         execArgs.put(flag, value);
     }
 
+    /**
+     * @return the number of header lines to copy to the final output
+     */
     public int getNumHeaderLines()
     {
         return this.numberOfHeaderLines;
+    }
+
+    /**
+     * @return true iff the user wants a statistics file created after the
+     * workers have all finished
+     */
+    public boolean makeStats()
+    {
+        return this.makeStats;
     }
 }

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/config/JFileChooserButton.java

@@ -37,7 +37,7 @@ final class JFileChooserButton extends JButton implements CustomWizardComponent
     {
         super("...");
         this.dialog = new JDialog();
-        this.fc = new JFileChooser();
+        this.fc = new JFileChooser(".");
 
         if (directoriesOnly)
         {

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/io/Manipulator.java

@@ -110,6 +110,10 @@ public final class Manipulator
 
                 sb = new StringBuilder();
             }
+            else
+            {
+                sb.append("\n");
+            }
 
             line = reader.readLine();
         }
@@ -136,18 +140,20 @@ public final class Manipulator
            writer = new PrintWriter(fileName);
            for (final Chunk c : this.chunks)
            {
-               writer.println(c.getResult());
+               writer.print(c.getResult());
            }
         }
         catch (FileNotFoundException e)
         {
-            System.err.println("Could not create output file called " + 
-                fileName);
+            System.err.println(e.getMessage()); 
             return;
         }
         finally
         {
-            writer.close();
+            if (writer != null)
+            {
+                writer.close();
+            }
         }
     }
 
@@ -167,24 +173,23 @@ public final class Manipulator
      * <code>Chunk</code>s to a CSV file 'stats.csv' in the same output
      * directory as the program.
      * @param workerStats - the statstics of the Workers
+     * @param outDir - the directory to output the file to
      */
-    public void printStats(final String workerStats)
+    public void printStats(final String workerStats, final String outDir)
     {
-        // Open up the file to save to
-        // TODO: print to correct directory
         try
         {
             final String comma = ",";
-            final PrintWriter statsOut = new PrintWriter("stats.csv");
+            final PrintWriter statsOut = new PrintWriter(outDir + "/stats.csv");
             statsOut.println(workerStats);
 
-            statsOut.println("Chunk #,Runtime,Chunks Run,Avg Time Per Chunk");
+            statsOut.println("Chunk #,Length,Runtime(ms)");
             for (int i = 0; i < this.chunks.size(); i++)
             {
                 final Chunk c = this.chunks.get(i);
                 final StringBuilder sb = new StringBuilder();
                 sb.append(c.hashCode()).append(comma).append(c.length());
-                sb.append(comma).append(c.getRuntime());
+                sb.append(comma).append(c.getRuntime()).append('\n');
                 statsOut.println(sb.toString());
             }
 

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/worker/Worker.java

@@ -69,6 +69,7 @@ public final class Worker extends Thread
      */
     public static void setExecutable(final String exec)
     {
+        System.err.println(exec);
         EXEC = exec;
     }
     
@@ -119,7 +120,8 @@ public final class Worker extends Thread
                 final long end = System.currentTimeMillis();
                 c.setRuntime(end - start);
                 runTime += (end - start);
-                System.out.println("Finished chunk on thread " + this.idNum);
+                System.out.println("Finished chunk " + c.hashCode() + 
+                        " on thread " + this.idNum + " in " + (end - start));
             }
             catch (InterruptedException e)
             {
@@ -167,6 +169,12 @@ public final class Worker extends Thread
             commands.add(">");
         }
         commands.add(out);
+
+        for (String s : commands)
+        {
+            System.out.print(s + " ");
+        }
+        System.out.println();
  
         return new ProcessBuilder(commands);
     }

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/worker/WorkerPool.java

@@ -67,7 +67,7 @@ public final class WorkerPool
     {
         // Print the stats
         final StringBuilder sb = new StringBuilder();
-        sb.append("Thread #,Runtime,Chunks Run,Avg Time Per Chunk");
+        sb.append("Thread #,Runtime(ms),Chunks Run,Avg Time Per Chunk(ms)\n");
         final String comma = ",";
         for (int i = 0; i < workers.length; i++)
         {

### 2013-10-31 paper/paper.tex
Revisions

@@
 \begin{document}
-\title{A Java Wrapper For Embarresingly Parallel Problems}
+\title{A Java Wrapper For Embarrassingly Parallel Problems}
 \author{Jacob Schwartz}
@@
 \begin{abstract}
-An embarresingly parallel, also called pleasing parallel, problem is one that 
-can easily be broken up into work that does not need to know about one another.
-Several problems in the biological sciences are embarrsingly parallel but they
-are difficult to rewrite to use multithreading, because they are either poorly
-written or too complex. We have written a wrapper, implemented in Java, that
-will execute the serial program in several threads. RESULTS SENTENCE. More
+An embarrassingly parallel problem, also called pleasingly parallel, is one that 
+can easily be broken up into identital components that do not need to interact 
+to find the solution. Several problems in the biological sciences are 
+embarrsingly parallel but they are difficult to rewrite to use multithreading, 
+because they are either poorly written or too complex. We have written a 
+wrapper, implemented in Java, that will execute the serial program in several 
+threads. RESULTS SENTENCE. More
 statistics, savable configurations and more options will be implemented next, in
@@
 
-The embarresingly parallel class of problems is defined as a problem when the
-computation graph is disconnected. The computation graph consists of nodes that
-represent the functions or processes and the data being passed from one process
-to another is displayed in the graph as edges. If the graph is disconnected, 
-none of the processes need to communicate to complete the computations. In a 
-practical situtation, there will be some internode communication to set up the 
-problem and then again to accumulate the results back together. Also known as
-pleasingly parallel problems, they can also easy be performed on a cluster of 
-servers or in any kind of distributed network, due to its lack of dependencies. 
-The term  embarresingly parallel was coined by Geoffrey Fox in his book, 
-\underline{Parallel Programming Works!} \cite{book}
+A computation graph consists of nodes that represent the functions or processes 
+and the data being passed from one process to another is displayed in the graph 
+as edges. If the graph is disconnected, none of the processes need to 
+communicate to complete the computations. Such a computation is called
+"embarrassingly parallel." In a practical situation, there will be some 
+internode communication to set up the problem and then again to accumulate the 
+results back together. Also known as pleasingly parallel problems, they can 
+easily be performed on a cluster of servers or in any kind of distributed 
+network, due to its lack of dependencies. The term  embarrassingly parallel was 
+coined by FINISH THIS
 
@@
 characters, whether they are DNA, RNA or protein sequences. In addition to the
-large file sizes, there is a lot of processing that goes into comparing several
-characters. This time adds up when there are thousands of strings to process.
-However, these sequences often to not relate to each other and can be processed
-independently. Using the embarresingly parallel approach, the processing time
-for all of the sequences can be cut down exponentially with very minimal effort
-by the programmer.
+large file sizes, there is a lot of processing that goes into comparing and
+manipulating strings. This time adds up when there are thousands of strings to 
+process. However, these sequences often do not relate to each other and can be 
+processed independently. Using an embarrassingly parallel approach, the 
+processing time for all of the sequences can often be cut down exponentially 
+with very minimal effort by the programmer.
 
-In this paper, I am going to propose a program that will call the serial
-programs on several Java threads. This program will act like the serial
-application, reading the input the same and creating the output in the same
-format. My wrapper program wraps any embarresingly parallel command line program
-that reads from a file, writes to a file and the input can be broken up into
-work units by a regular expression. SUMMARY OF RESULTS to end the paragraph.
+The framework provides a "wrapper' for the original program that mimics the
+behavior of the original program. It calls the serial programs on multiple Java 
+threads. Each thread acts like the serial application, reading a subset of the 
+input the same and creating the output in the same format. This paper describes
+a framework a framework that makes it easy to parallelize an embarrassingly
+parallel program that reads from a file, writes to a file and whose input can be
+broken up into work units by a regular expression. 
+SUMMARY OF RESULTS to end the paragraph.
 
@@
 
-Originally, I was assisting with research into different forms of the species 
-\emph{Cicer arietinum}, the chikckpea. The two main forms, Kabuli and Desi, are
-very different in size and color but we mostly wanted to see why the Desi is
-more disease resistance and have more effective root nodule symbiosis and why
-the Kabuli has a large but soft shell. These two types are both cultivated and
-have been under human selection for several thousand years. We wanted to use a
-Ka/Ks equation to quantify the evelution and selection of these chickpeas. We
-found a Ka/Ks program writen by Zhang et al. from the Beijing Institute of 
-Genomics \cite{kaks} but had three varients that we wanted to be analyzed, each 
-with thousands of sequences to process. The Ka/Ks Calculator program takes
-somewhere from five to thirty seconds to process one pair of sequences.
+The motivation for this effort was with research into different forms of the 
+species \emph{Cicer arietinum}, the chikckpea. The two main forms, Kabuli and 
+Desi, are very different in size and color but we mostly wanted to see why the 
+Desi is more disease resistance and have more effective root nodule symbiosis 
+and why the Kabuli has a large but soft shell. These two types are both 
+cultivated and have been under human selection for several thousand years. We 
+wanted to use a Ka/Ks equation to quantify the evolution and selection of these 
+chickpeas. We found a Ka/Ks program writen by Zhang et al. \cite{kaks} but had 
+three variants that we wanted to be analyzed, each with thousands of sequences. 
+The Ka/Ks Calculator program takes somewhere from five to thirty seconds to 
+process one pair of sequences.
 
@@
 was calculated, the contents of the output files was concatenated together to 
-produce a final input.
+produce a final output that mnatches the format and order that would have been
+produces by Ka/Ks Calculator.
 
-The KaKs Calculator is not the only embarresingly parallel program that has the
+The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
 potential to take several days to run on a data set. In fact, there are several
-embarresingly parallel programs in the biological sciences. The Basic Local
+embarrassingly parallel programs in the biological sciences. The Basic Local
 Alignment Search Tool (BLAST) \cite{BLAST} is a common program used to find
@@
 transcriptomes from mRNA sequence data. With this variety of applications that 
-would benefit from parallelism, it was obvious that the wrapper program has 
-potential outside of this project.
+would benefit from parallelism, it was obvious it would be desirable to develop
+a framework for creating wrapper programs.
 
@@
 
-The original wrapper was also written very quickly due to the impending
-deadline. In this version of the wrapper, several components are being added.
-First off, there is a wizard style menu that will allow the end-user to select
-not only the program that wish to use, but also to manage other settings for the
-run. A new IO class splits the input and merges the output more 
-efficiently. Lastly, in order to look at how well the wrapper performs, 
-the threads keep their own statstics. These statstics will not only be used to 
-find potential enhancements but also will help end-users of the wrapper
-determine whether their use of the wrapper is efficient.
+In this version of the wrapper, several components are being added. First, there
+is a wizard style menu that will allow the end-user to select not only the 
+program that wish to use, but also to manage other settings for the run. A new 
+IO class splits the input and merges the output more efficiently. Lastly, in 
+order to look at how well the wrapper performs, the threads keep their own 
+statistics, which will be used to evaluate the effectiveness of the framework 
+and to find potential enhancements and help end-users determine whether their 
+use of the framework is efficient.
 
@@
 
-The KaKs Calculator is not the only program to use the wrapper; there are
-various potential programs that the wrapper could support. The only requirements
-for the this program are that it process the input in an embarresingly parallel
-manner and that the input comes from a file and the processed results are also
-writen to a file. The wrapper needs to support various kinds of input files and 
-be able to chunk up the work accordingly. The KaKs Calculator's input consists 
-of a header and then two protein sequence lines followed by a blank line. The 
-wrapper will use that blank line to know when one chunk of work has ended and 
-another has begun. The user can input their own regular expression to determine 
-what lines of input make up what chunks. This will occur in the ChunkManager 
-class.
+The KaKs Calculator is not the only program to use the framework; there are
+various potential programs that the framework could support. The only 
+requirements for the this program are that it process the input in an 
+embarrassingly parallel manner and that the input comes from a file and the 
+processed results are also writen to a file. The framework needs to support 
+various kinds of input files and be able to chunk up the work accordingly. The 
+Ka/Ks Calculator's input consists of a header and then two protein sequence 
+lines followed by a blank line. The framework uses that blank line to know when 
+one chunk of work has ended and another has begun. The user can input a regular 
+expression to define what lines of input make up what chunks. This occurs in 
+the ChunkManager class.
 
@@
 back together when the worker threads have finished. Once the work has been
-down, all of the seperate results are spread across several files. The
+done, all of the separate results are spread across several files. The
 ChunkManager's second job is to retrieve those results and construct a real
@@
 look if the program were run serially; the output must come in the same order as
-the inputs in the input file and headers must be added to the top, if
-applicable.
+the inputs in the input file and headers may need to be deleted from the
+separate files and added to the combined file.
 
-As more features are added to the wrapper and as more programs start to use the
-wrapper, there are more choices for the end-user to make in regards to how they
-want their program to execute. The number of threads to use, various flags for
-the executable and blank are just a few choice they can make. A start-up wizard
-is displayed at runtime to systimatically allow the end-user to choose the
-settings for the run. The ConfigWizard class brings the user through this
-process and creates an instance of Configuration when it is completed to save
-the user's settings.
+As more features are added to the framework and as more programs start to use 
+the framework, there are more choices for the end-user to make with regards to 
+how they want their program to execute. The number of threads to use, various 
+flags for the executable and the statstics output are just a few choice the 
+user can make. A start-up wizard is displayed at runtime to systematically allow
+the end-user to choose the settings for the run. The ConfigWizard class brings 
+the user through this process and creates an instance of Configuration when it 
+is completed to save the user's settings.
 
-Lastly, the worker threads will keep records during the execution of a set of 
-work. The threads records its uptime and the number of pieces of work it
-executes on. Also, the runtime for each piece of work is recorded. These will be
-used by the end user to determine if their run is ideal or if they may need to
-change some settings to make it work faster next time. The statistics can also
-give the developers of the wrapper an idea on what can be implemented in order
-make it as fast as possible for a user. The statistics for each thread can be
-found in the Worker subclass and the individual Chunk classes will store their
-own statstics about runtime and size.
+Lastly, the worker threads will keep records during execution. The threads 
+records their uptime and the number of pieces of work they execute. The runtime 
+for each piece of work is also recorded. This information will be used by us to
+evaluate the effectiveness of our approach, but can also provide useful
+information the can help a user tine a particular application on a particular
+type of input data. The statistics for each thread can be found in the Worker 
+subclass and the individual Chunk classes will store their own statstics about 
+runtime and size.
 
@@
 \begin{thebibliography}{1}
-\bibitem{book}
-Fox G., Williams R., and Messina G., ``\emph{Parallel Programming Works!},'', 
-Morgan Kaufmann, May 1994
 \bibitem{kaks}

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/Chunk.java
Merge now adds the header to the output

@@ -91,6 +91,38 @@ public final class Chunk implements Comparable<Chunk>
     }
 
     /**
+     * @return the header from the results of the processed chunk
+     */
+    public String getHeader()
+    {
+        final StringBuilder sb = new StringBuilder();
+        
+        try 
+        {
+            // Open out file
+            final BufferedReader br = 
+                new BufferedReader(new FileReader(getOutFileName()));
+
+            // Read the header lines
+            for (int i = 0; i < HEADER_LINES; i++)
+            {
+                sb.append(br.readLine()).append("\n");
+            }
+
+            // Close the file
+            br.close();
+            
+        }
+        catch (IOException e)
+        {
+            System.err.println(e.getMessage());
+        }
+        
+        return sb.toString();
+ 
+    }
+
+    /**
      * @return the result of the run on the chunk aka the content of the outfile
      */
     public String getResult()

### 2013-10-31 src/main/java/edu/unh/schwartz/parawrap/io/Manipulator.java

@@ -137,11 +137,13 @@ public final class Manipulator
         PrintWriter writer = null;
         try
         {
-           writer = new PrintWriter(fileName);
-           for (final Chunk c : this.chunks)
-           {
-               writer.print(c.getResult());
-           }
+            writer = new PrintWriter(fileName);
+            writer.print(this.chunks.get(0).getHeader());
+
+            for (final Chunk c : this.chunks)
+            {
+                writer.print(c.getResult());
+            }
         }
         catch (FileNotFoundException e)
         {

### 2013-11-01 paper/paper.tex
More paper work

@@
 because they are either poorly written or too complex. We have written a 
-wrapper, implemented in Java, that will execute the serial program in several 
-threads. RESULTS SENTENCE. More
-statistics, savable configurations and more options will be implemented next, in
-addition to better testing and refactored.
+framework, implemented in Java, that will execute the serial program in several 
+threads. These threads working together help cut down the total runtime
+exponentially. More statistics, savable configurations and more options will be 
+implemented next, in addition to better testing and refactored.
 \end{abstract}
@@
 parallel program that reads from a file, writes to a file and whose input can be
-broken up into work units by a regular expression. 
-SUMMARY OF RESULTS to end the paragraph.
+broken up into work units by a regular expression. SUMMARY OF RESULTS to end the
+paragraph.
 
@@
 
+REDO THIS PART
 The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
@@
 
-In this version of the wrapper, several components are being added. First, there
-is a wizard style menu that will allow the end-user to select not only the 
+In this version of the framework, several components are being added. First, 
+there is a wizard style menu that will allow the end-user to select not only the 
 program that wish to use, but also to manage other settings for the run. A new 
 IO class splits the input and merges the output more efficiently. Lastly, in 
-order to look at how well the wrapper performs, the threads keep their own 
+order to look at how well the framework performs, the threads keep their own 
 statistics, which will be used to evaluate the effectiveness of the framework 
@@
 
-Tables charts, etc
+Table and chart
+
+The Ka/Ks Calculator was run through the framework with ten different samples,
+each containing sixteen units of work. Each sample was run by the framework at 
+five different level of numbers of worker threads, starting at 1 and 
+increasing by powers of two until the 100\% CPU usage (16 processors). As the 
+numbers of threads increased, the time it took descreased exponentially.
 
@@
 
-Conclusions gathered from results.
+In a few cases, there was an increase in time when attempting to max out the CPU 
+usage. This occured because the framework had to wait until for the CPU to be 
+finished with its previous work before it was allowed to start work on what the 
+framework wanted it to do. In the cases when the framework executed faster while
+the CPU was maxed out, it was only faster a minute at the most. With such a
+small time gain with the CPU at 50\% versus the CPU at 100\%, running the
+framework at 50\% CPU is more efficient when the number of threads is on the
+same order as the number of units of work.
 

### 2013-11-02 paper/paper.tex
Graphs and table and more revisions

@@
 network, due to its lack of dependencies. The term embarrassingly parallel was 
-coined by FINISH THIS
+coined by Cleve Moler in his 1986 paper "Matrix Computation on Distributed
+Memory Multiprocessors." \cite{history}
 
@@
 parallel program that reads from a file, writes to a file and whose input can be
-broken up into work units by a regular expression. SUMMARY OF RESULTS to end the
-paragraph.
+broken up into work units by a regular expression. The framework gives an
+exponential decrease in runtime as more processor help in the computation. This
+decrease levels off between 50 and 100\% CPU usage due to the other tasks on the
+machine that take up memory.
 
@@
 potential to take several days to run on a data set. In fact, there are several
-embarrassingly parallel programs in the biological sciences. The Basic Local
-Alignment Search Tool (BLAST) \cite{BLAST} is a common program used to find
-similarities between sequences and then compares them to databases to calculate
-the statistical significance. Another program we have been looking at is called
-Trinity. Trinity claims to be an efficient way to do de novo reconstruction of
-transcriptomes from mRNA sequence data. With this variety of applications that 
-would benefit from parallelism, it was obvious it would be desirable to develop
-a framework for creating wrapper programs.
+embarrassingly parallel programs in the biological sciences. 
+TALK ABOUT CLUSTERING
+With several applications that 
+would benefit from parallelism in this field, it was obvious it would be 
+desirable to develop a framework for creating wrapper programs.
 
@@
 
-Table and chart
+To observe how the framework changes the runtime of sequential programs when
+using varying numbers of threads, I designed a simple experiment. The Ka/Ks 
+Calculator was run through the framework with ten different samples, each 
+containing sixteen units of work. Each sample was run by the framework at five 
+different level of numbers of worker threads, starting at 1 and increasing by 
+powers of two until the 100\% CPU usage (16 processors). These tests were run
+with minimal other activity on the server.
 
-The Ka/Ks Calculator was run through the framework with ten different samples,
-each containing sixteen units of work. Each sample was run by the framework at 
-five different level of numbers of worker threads, starting at 1 and 
-increasing by powers of two until the 100\% CPU usage (16 processors). As the 
-numbers of threads increased, the time it took descreased exponentially.
+\begin{figure}
+{{!}{\includegraphics{experiment/out.png}}}
+\caption{Runtimes for the Ka/Ks Calculator though the framework}
+\label{fig:graph}
+\end{figure}
 
@@
 
+As the numbers of threads increased, the time it took descreased exponentially. 
 In a few cases, there was an increase in time when attempting to max out the CPU 
@@
 like Hadoop, Clojure or other multithread oriented language may have been better
-due to their parallel nature. Another approach that could have been taken is one
-similar to the people in Washington: going to the cloud. Using a networked 
-solution like MPI or a cloud solution like Amazon instances. (More will go here
-when I added in more previous work from others)
+due to their parallel nature. In addition to a single machine working to process
+the data quickly, we can also look to the cloud for help by using a networked 
+solution like MPI or a cloud solution like Amazon instances. This would
+potentially allow for an even greater time decrease because the number of
+machines that could help is most likely larger than the number of processors on
+one machine.
 
 \begin{thebibliography}{1}
+\bibitem{history}
+Moler, Cleve. "Matrix Computation on Distributed Memory Multiprocessors."
+Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
+Hypercube Multiprocessors, Knoxville, Tennessee, August 24-27, 1985. By Michael
+T. Heath. Philadelphia: SIAM, 1986. N. pag. Print.
 \bibitem{kaks}
@@
 Genomics Proteomics Bioinformatics, November 2006.
-\bibitem{BLAST}
-http://blast.ncbi.nlm.nih.gov/Blast.cgii
 \end{thebibliography}

### 2013-11-03 paper/paper.tex
More paper

@@
 
-The framework provides a "wrapper' for the original program that mimics the
+The framework provides a "wrapper" for the original program that mimics the
 behavior of the original program. It calls the serial programs on multiple Java 
@@
 
-REDO THIS PART
 The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
@@
 \section{Proposed Solution}
-
-A UML Diagram will go here
-
+\begin{figure}
+{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
+\caption{UML for the embarrassingly parallel framework}
+\label{fig:uml}
+\end{figure}
 The KaKs Calculator is not the only program to use the framework; there are
@@
 \begin{figure}
-{{!}{\includegraphics{experiment/out.png}}}
+{\resizebox{5.2in}{!}{\includegraphics{experiment/out.png}}}
 \caption{Runtimes for the Ka/Ks Calculator though the framework}

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/Chunk.java
Renamed project

@@ -1,0 +1,224 @@
+package edu.unh.schwartz.epframework;
+
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileReader;
+import java.io.IOException;
+
+/**
+ * Piece of work to do be done by the <code>Worker</code>s. Also contains
+ * statstical information that can be used to get the ideal configuration.
+ */
+public final class Chunk implements Comparable<Chunk>
+{
+    /**
+     * The number of header lines used in the output file.
+     */
+    private static int HEADER_LINES;
+
+    /**
+     * The runtime of the chunk in millis.
+     */
+    private long runtime;
+    
+    /**
+     * The content of the chunk.
+     */
+    private String content;
+
+    /**
+     * The directory where the in and out files are saved.
+     */
+    private File directory;
+
+    /**
+     * Constructs a chunk based off some content.
+     * @param content - what the chunk represents
+     * @param directory - the directory for the chunk's IO
+     */
+    public Chunk(final String content, final File directory)
+    {
+        this.content = content;
+        this.directory = directory;
+    }
+
+    /**
+     * @return the length of the chunk's content
+     */
+    public int length()
+    {
+        return this.content.length();
+    }
+
+    /**
+     * @return the number of milliseconds taken to compute the chunk
+     */
+    public long getRuntime()
+    {
+        return this.runtime;
+    }
+
+    /**
+     * Set the runtime of the chunk.
+     * @param runtime - the runtime of the chunk in milliseconds
+     */
+    public void setRuntime(final long runtime)
+    {
+        this.runtime = runtime;
+    }
+
+    /**
+     * @return the directory where the content is saved
+     */
+    public File getDirectory()
+    {
+        return this.directory;
+    }
+
+    /**
+     * Deletes the directory and its files.
+     */
+    public void clean()
+    {
+        // Delete the files in the directories
+        for (final File f : this.directory.listFiles())
+        {
+            f.delete();
+        }
+        this.directory.delete();
+
+        this.runtime = 0;
+    }
+
+    /**
+     * @return the header from the results of the processed chunk
+     */
+    public String getHeader()
+    {
+        final StringBuilder sb = new StringBuilder();
+        
+        try 
+        {
+            // Open out file
+            final BufferedReader br = 
+                new BufferedReader(new FileReader(getOutFileName()));
+
+            // Read the header lines
+            for (int i = 0; i < HEADER_LINES; i++)
+            {
+                sb.append(br.readLine()).append("\n");
+            }
+
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/EPFramework.java

@@ -1,0 +1,103 @@
+package edu.unh.schwartz.epframework;
+
+import edu.unh.schwartz.epframework.config.Configuration;
+import edu.unh.schwartz.epframework.config.ConfigWizard;
+import edu.unh.schwartz.epframework.io.Manipulator;
+import edu.unh.schwartz.epframework.worker.WorkerPool;
+import java.io.IOException;
+import java.util.concurrent.PriorityBlockingQueue;
+
+/**
+ * Application class. Takes an optional command line parameter for the run
+ * configuration. If none is given, goes through the wizard to create one,
+ * which will then allow the user to save it for later runs. Calls the split
+ * operation, starts the workers, calls the move operation and then prints
+ * statistics about the run to 'stats.csv'.
+ *
+ * @author Jacob Schwartz
+ */
+final class EPFramework
+{
+    private EPFramework() 
+    {
+        // No-op
+    }
+
+    /**
+     * Starts the parallel wrapper based on the <code>Configuration</code>.
+     *
+     * @param config - the instructions for the wrapper
+     */
+    private static void start(final Configuration config)
+    {
+        Chunk.setHeaderLines(config.getNumHeaderLines());
+
+        // Read in the input file and get the chunks
+        final Manipulator manip = new Manipulator(config.getSplitPattern(), 
+            config.getNumHeaderLines());
+
+        try
+        {
+            manip.split(config.getInputFileName());
+        }
+        catch (IOException e)
+        {
+            System.err.print(e.getMessage());
+            return;
+        }
+
+        final PriorityBlockingQueue<Chunk> chunks = manip.getChunks();
+        if (chunks.size() == 0)
+        {
+            System.err.println("Incorrect chunk pattern or empty input file");
+            return;
+        }
+
+        final WorkerPool wp = new WorkerPool(config, chunks);
+        wp.start();
+        manip.merge(config.getOutputDirectory() + "/done.txt");
+        if (config.makeStats())
+        {
+            manip.printStats(wp.getStats(), config.getOutputDirectory());
+        }
+        manip.cleanUp();
+    }
+
+    /**
+     * Main method. Can be run with 0 or 1 cmd line args.
+     *
+     * @param args - Command line arguments
+     */
+    public static void main(final String[] args) 
+    {
+        // If there are no cmd line args, create a configuration file
+        if (args.length == 0)
+        {
+            // Allow the user to make a configuration file
+            System.out.println("Opening Configuration Wizard");
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java

@@ -1,0 +1,304 @@
+package edu.unh.schwartz.epframework.config;
+
+import java.awt.Dimension;
+import java.util.ArrayList;
+import java.util.List;
+// import javax.swing.border.EmptyBorder;
+import javax.swing.JCheckBox;
+import javax.swing.JDialog;
+import javax.swing.JLabel;
+import javax.swing.JTextField;
+import org.ciscavate.cjwizard.PageFactory;
+import org.ciscavate.cjwizard.pagetemplates.DefaultPageTemplate;
+import org.ciscavate.cjwizard.WizardContainer;
+import org.ciscavate.cjwizard.WizardListener;
+import org.ciscavate.cjwizard.WizardPage;
+import org.ciscavate.cjwizard.WizardSettings;
+
+/**
+ * GUI Wizard to help create configuration file.
+ */ 
+public final class ConfigWizard
+{
+    /**
+     * The instance.
+     */
+    private static ConfigWizard instance;
+
+    /**
+     * The last configuration created.
+     */ 
+    private Configuration config;
+
+    /**
+     * The window for the wizard.
+     */
+    private JDialog window;
+
+    /**
+     * Prevents instantiation.
+     */
+    private ConfigWizard()
+    {
+        window = new JDialog();
+
+        final WizardContainer wc = 
+            new WizardContainer(new ConfigPageFactory(),
+                    new DefaultPageTemplate());
+
+        wc.addWizardListener(new ConfigWizardListener());
+
+        window.setDefaultCloseOperation(JDialog.DISPOSE_ON_CLOSE);
+        window.getContentPane().add(wc);
+        window.setSize(375, 250);
+        window.setLocationRelativeTo(null);
+    }
+
+    /**
+     * @return the instance of the <code>ConfigWizard</code>
+     */
+    public static ConfigWizard getInstance()
+    {
+        if (instance == null)
+        {
+            instance = new ConfigWizard();
+        }
+        return instance;
+    }
+
+    /**
+     * Goes through the process of creating a configuration file. Saves it?
+     *
+     * @return the configuration created by the user
+     */
+    public Configuration createConfiguration()
+    {
+        this.window.setVisible(true);
+        synchronized(this)
+        {
+            try
+            {
+                this.wait();
+            }
+            catch (InterruptedException e)
+            {
+                System.err.println("Oh noes!");
+            }
+        }
+
+        return this.config;
+    }
+
+    /**
+     * Handles the callbacks from the wizard.
+     */
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -1,0 +1,290 @@
+package edu.unh.schwartz.epframework.config;
+
+// import com.fasterxml.jackson.core.JsonFactory;
+// import com.fasterxml.jackson.core.JsonParser;
+// import com.fasterxml.jackson.core.JsonToken;
+// import java.io.File;
+// import java.io.IOException;
+import java.util.HashMap;
+import java.util.Map;
+import java.util.Iterator;
+
+/**
+ * The settings for the current run of the application. 
+ *
+ * Talk about the various fields it contains
+ */
+public final class Configuration
+{
+    /**
+     * Key for in file setting.
+     */
+    public static final String IN_FILE_KEY = "inFile";
+
+    /**
+     * Key for split pattern setting.
+     */
+    public static final String SPLIT_PATTERN_KEY = "split";
+
+    /**
+     * Key for out file setting.
+     */
+    public static final String OUT_FILE_KEY = "outFile";
+
+    /**
+     * Key for executable location setting.
+     */
+    public static final String EXEC_LOC_KEY = "execLoc";
+
+    /**
+     * Key for in flag setting.
+     */
+    public static final String IN_FLAG_KEY = "inFlag";
+
+    /**
+     * Key for out flag setting.
+     */
+    public static final String OUT_FLAG_KEY = "outFlag";
+    
+    /**
+     * Key for threading setting.
+     */
+    public static final String NUM_PROCESSES_KEY = "numProcesses";
+
+    /**
+     * Key for stats setting.
+     */
+    public static final String STATS_KEY = "stats";
+
+    /**
+     * Key for output file header setting.
+     */
+    public static final String NUM_HEADER_KEY = "numHeaderLines";
+
+    /**
+     * The number of threads used.
+     */
+    private int numberOfThreads;
+    
+    /**
+     * The name of the input file.
+     */
+    private String inputFileName;
+    
+    /**
+     * The regex pattern to split the input file on.
+     */
+    private String splitPattern;
+
+    /**
+     * The directory where the output should go.
+     */
+    private String outDirName;
+
+    /**
+     * The path to the executable.
+     */
+    private String execPath;
+
+    /**
+     * The flags for the executable to show how to enter input and outfile.
+     */
+    private String inFlag;
+    private String outFlag;
+
+    /**
+     * The arguments for the execuatable.
+     */
+    private Map<String, String> execArgs;
+
+    /**
+     * Whether or not to make a stats file.
+     */
+    private boolean makeStats;
+
+    /**
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/config/JFileChooserButton.java

@@ -1,0 +1,89 @@
+package edu.unh.schwartz.epframework.config;
+
+import org.ciscavate.cjwizard.CustomWizardComponent;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+import java.io.File;
+import javax.swing.JButton;
+import javax.swing.JDialog;
+import javax.swing.JFileChooser;
+
+/**
+ * Clab.
+ */
+final class JFileChooserButton extends JButton implements CustomWizardComponent
+{
+    /**
+     * The dialog for the file choosers.
+     */
+    private JDialog dialog;
+    
+    /**
+     * The file chooser that appears when the button clicked.
+     */
+    private JFileChooser fc;
+    
+    /**
+     * The path of the file selected by the user.
+     */
+    private String path;
+
+    /**
+     * Constructs a new button.
+     * @param directoriesOnly - allow the user to select directories only iff
+     * true. otherwise, user can only select files
+     */
+    public JFileChooserButton(final boolean directoriesOnly)
+    {
+        super("...");
+        this.dialog = new JDialog();
+        this.fc = new JFileChooser(".");
+
+        if (directoriesOnly)
+        {
+            fc.setFileSelectionMode(JFileChooser.DIRECTORIES_ONLY);
+        }
+        else
+        {
+            fc.setFileSelectionMode(JFileChooser.FILES_ONLY);
+        }
+    
+        this.addActionListener(new ActionListener()
+        {
+            /**
+             * {@inheritDoc}
+             */
+            public void actionPerformed(final ActionEvent e)
+            {
+                final int returnVal = fc.showOpenDialog(dialog);
+                switch (returnVal)
+                {
+                    case JFileChooser.APPROVE_OPTION:
+                        final File f = fc.getSelectedFile();
+                        setValue(f.getPath());
+                        setText(f.getName());
+                        JFileChooserButton.this.dialog.dispose();
+                        break;
+                    default:
+                        break;
+                }
+            }
+        });
+    }
+
+    /**
+     * {@inheritDoc}
+     */               
+    public Object getValue()
+    {
+        return this.path;
+    }
+
+    /**
+     * {@inheritDoc}
+     */
+    public void setValue(final Object o)
+    {
+        this.path = (String) o;
+    }
+}

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/config/WizardSpinner.java

@@ -1,0 +1,22 @@
+package edu.unh.schwartz.epframework.config;
+
+import org.ciscavate.cjwizard.CustomWizardComponent;
+import java.util.List;
+import javax.swing.SpinnerListModel;
+import javax.swing.JSpinner;
+
+/**
+ * Clab.
+ */
+final class WizardSpinner extends JSpinner implements CustomWizardComponent
+{
+    /**
+     * Makes a new spinner with the provided options.
+     *
+     * @param options - the choices of the spinner
+     */
+    public WizardSpinner(final List<String> options)
+    {
+        super(new SpinnerListModel(options));
+    }
+}

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/config/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * blah blah blah.
+ */
+package edu.unh.schwartz.epframework.config;

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/io/Manipulator.java

@@ -1,0 +1,205 @@
+package edu.unh.schwartz.epframework.io;
+
+import edu.unh.schwartz.epframework.Chunk;
+import java.io.BufferedReader;
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.IOException;
+import java.io.PrintWriter;
+import java.util.ArrayList;
+import java.util.concurrent.PriorityBlockingQueue;
+import java.util.List;
+import java.util.regex.Pattern;
+
+/**
+ * Does all of the IO functions for the process. Can split an input file based
+ * on a pattern and merge it back together in the same order.
+ */
+public final class Manipulator
+{
+    /**
+     * The default pattern for a manipulator.
+     */
+    private static final String DEFAULT_PATTERN = "^.*$";
+
+    /**
+     * The pattern used to split the input file.
+     */
+    private Pattern pattern;
+    
+    /**
+     * The chunks for the current input file.
+     */
+    private List<Chunk> chunks;
+
+    /**
+     * The number of header lines to put in the final output file.
+     */
+    private int headerLines;
+
+    /**
+     * Constructs a manipulator with the default pattern and 0 header lines.
+     */
+    public Manipulator()
+    {
+        this(DEFAULT_PATTERN, 0);
+    }
+
+    /**
+     * Constructs a manipulator with the default pattern and some number of 
+     * header lines.
+     *
+     * @param headerLines - the number of header lines to take from output files
+     */
+    public Manipulator(final int headerLines)
+    {
+        this(DEFAULT_PATTERN, headerLines);
+    }
+
+    /**
+     * Constructs a manipulator with a custom pattern and some number of header
+     * lines.
+     *
+     * @param regex - Regular expression to split on
+     * @param headerLines - the number of header lines to take from output files
+     */
+    public Manipulator(final String regex, final int headerLines)
+    {
+        this.pattern = Pattern.compile(regex);
+        this.headerLines = headerLines;
+    }
+
+    /**
+     * Splits the file and creates chunks.
+     *
+     * @param fileName - the name of the file
+     * @throws IOException - when there is any kind of problem with the input
+     */
+    public void split(final String fileName) throws IOException 
+    {
+        this.chunks = new ArrayList<Chunk>();
+
+        StringBuilder sb = new StringBuilder();
+        
+        final File f = new File(fileName);
+        final BufferedReader reader = new BufferedReader(new FileReader(f));
+        String line = reader.readLine();
+        while (line != null)
+        {
+            sb.append(line);
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/io/package-info.java

@@ -1,0 +1,5 @@
+/**
+ * Provides classes that deal with file I/O of the chunks of work: spliting,
+ * merging, etc.
+ */
+package edu.unh.schwartz.epframework.io;

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/package-info.java

@@ -1,0 +1,4 @@
+/**
+ * Contains the application class and other classes used throughout the program.
+ */
+package edu.unh.schwartz.epframework;

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -1,0 +1,197 @@
+package edu.unh.schwartz.epframework.worker;
+
+import edu.unh.schwartz.epframework.Chunk;
+import java.io.IOException;
+import java.util.concurrent.PriorityBlockingQueue;
+import java.util.ArrayList;
+import java.util.List;
+
+/**
+ * Runs the process on the queued up input. Each worker has an id and keeps
+ * various statistical information to use later to determine if the
+ * configuration could be better.
+ */
+public final class Worker extends Thread
+{
+    /**
+     * The path to the executable.
+     */
+    private static String EXEC;
+
+    /**
+     * The in flag for the executable.
+     */
+    private static String IN_FLAG;
+
+    /**
+     * The out flag for the executable.
+     */
+    private static String OUT_FLAG;
+
+       /**
+     * The queue of pieces to do work on.
+     */
+    private PriorityBlockingQueue<Chunk> queue;
+    
+    /**
+     * The id number of this worker.
+     */
+    private int idNum;
+    
+    /**
+     * The sum of run times of executable.
+     */
+    private long runTime;
+
+    /**
+     * The number of chunks run by this worker.
+     */
+    private int chunksRun;
+
+    /**
+     * Creates a worker.
+     *
+     * @param idNum - the id number of this worker
+     * @param queue - the queue for the worker to take chunks from
+     */
+    public Worker(final int idNum, final PriorityBlockingQueue<Chunk> queue)
+    {
+        this.queue = queue;
+        this.idNum = idNum;
+        this.runTime = 0;
+        this.chunksRun = 0;
+    }
+
+    /**
+     * Set the path to the executable.
+     *
+     * @param exec - the path to the executable
+     */
+    public static void setExecutable(final String exec)
+    {
+        System.err.println(exec);
+        EXEC = exec;
+    }
+    
+    /**
+     * Set the flag to signify where the input goes for the executable.
+     *
+     * @param inFlag - the in flag used to signify the input file 
+     */
+    public static void setInFlag(final String inFlag)
+    {
+        IN_FLAG = inFlag;
+    }
+
+    /**
+     * Set the flag to signify where the output goes for the executable.
+     *
+     * @param outFlag - the flag used to signify the output file 
+     */
+    public static void setOutFlag(final String outFlag)
+    {
+        OUT_FLAG = outFlag;
+    }
+
+    /**
+     * {@inheritDoc}
+     */
+    @Override
+    public void run()
+    {
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/worker/WorkerPool.java

@@ -1,0 +1,83 @@
+package edu.unh.schwartz.epframework.worker;
+
+import edu.unh.schwartz.epframework.Chunk;
+import edu.unh.schwartz.epframework.config.Configuration;
+import java.util.concurrent.PriorityBlockingQueue;
+
+/**
+ * Creates and starts the <code>Worker</code>s.
+ */
+public final class WorkerPool
+{
+    /**
+     * The workers to be utilizated.
+     */
+    private Worker[] workers;
+
+    /**
+     * Constructs the workers.
+     *
+     * @param config - information for the run
+     * @param chunks - the work for the workers
+     */
+    public WorkerPool(final Configuration config, 
+        final PriorityBlockingQueue<Chunk> chunks)
+    {
+        // Set the executable information in the worker
+        Worker.setExecutable(config.getExecutable());
+        Worker.setInFlag(config.getInFlag());
+        Worker.setOutFlag(config.getOutFlag());
+
+        // Initialize the threads
+        workers = new Worker[config.getNumberOfThreads()];
+        for (int i = 0; i < workers.length; i++)
+        {
+            workers[i] = new Worker(i, chunks);
+        }
+    }
+
+    /**
+     * Start the workers.
+     */
+    public void start()
+    {
+        for (int i = 0; i < workers.length; i++)
+        {
+            workers[i].start();
+        }
+
+        try
+        {
+            for (int i = 0; i < workers.length; i++)
+            {
+                workers[i].join();
+            }
+        }
+        catch (InterruptedException e)
+        {
+            System.err.println("Thread interrupted");
+            System.exit(1);
+        }
+    }
+
+    /**
+     * @return the statistics for the <code>Worker</code> in a csv table
+     */
+    public String getStats()
+    {
+        // Print the stats
+        final StringBuilder sb = new StringBuilder();
+        sb.append("Thread #,Runtime(ms),Chunks Run,Avg Time Per Chunk(ms)\n");
+        final String comma = ",";
+        for (int i = 0; i < workers.length; i++)
+        {
+            final long runtime = workers[i].getRunTime();
+            final int chunks = workers[i].getChunksRun();
+            sb.append(i).append(comma).append(runtime).append(comma);
+            sb.append(chunks).append(comma).append(runtime / chunks);
+            sb.append('\n');
+        }
+        sb.append('\n');
+        return sb.toString();
+    }
+}

### 2013-11-06 src/main/java/edu/unh/schwartz/epframework/worker/package-info.java

@@ -1,0 +1,5 @@
+/**
+ * Classes to do the execution on the work and hold statistics about the
+ * runtimes and length of the work.
+ */
+ package edu.unh.schwartz.epframework.worker;

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/Chunk.java
Removed old files

@@ -1,224 +1,0 @@
-package edu.unh.schwartz.parawrap;
-
-import java.io.BufferedReader;
-import java.io.File;
-import java.io.FileReader;
-import java.io.IOException;
-
-/**
- * Piece of work to do be done by the <code>Worker</code>s. Also contains
- * statstical information that can be used to get the ideal configuration.
- */
-public final class Chunk implements Comparable<Chunk>
-{
-    /**
-     * The number of header lines used in the output file.
-     */
-    private static int HEADER_LINES;
-
-    /**
-     * The runtime of the chunk in millis.
-     */
-    private long runtime;
-    
-    /**
-     * The content of the chunk.
-     */
-    private String content;
-
-    /**
-     * The directory where the in and out files are saved.
-     */
-    private File directory;
-
-    /**
-     * Constructs a chunk based off some content.
-     * @param content - what the chunk represents
-     * @param directory - the directory for the chunk's IO
-     */
-    public Chunk(final String content, final File directory)
-    {
-        this.content = content;
-        this.directory = directory;
-    }
-
-    /**
-     * @return the length of the chunk's content
-     */
-    public int length()
-    {
-        return this.content.length();
-    }
-
-    /**
-     * @return the number of milliseconds taken to compute the chunk
-     */
-    public long getRuntime()
-    {
-        return this.runtime;
-    }
-
-    /**
-     * Set the runtime of the chunk.
-     * @param runtime - the runtime of the chunk in milliseconds
-     */
-    public void setRuntime(final long runtime)
-    {
-        this.runtime = runtime;
-    }
-
-    /**
-     * @return the directory where the content is saved
-     */
-    public File getDirectory()
-    {
-        return this.directory;
-    }
-
-    /**
-     * Deletes the directory and its files.
-     */
-    public void clean()
-    {
-        // Delete the files in the directories
-        for (final File f : this.directory.listFiles())
-        {
-            f.delete();
-        }
-        this.directory.delete();
-
-        this.runtime = 0;
-    }
-
-    /**
-     * @return the header from the results of the processed chunk
-     */
-    public String getHeader()
-    {
-        final StringBuilder sb = new StringBuilder();
-        
-        try 
-        {
-            // Open out file
-            final BufferedReader br = 
-                new BufferedReader(new FileReader(getOutFileName()));
-
-            // Read the header lines
-            for (int i = 0; i < HEADER_LINES; i++)
-            {
-                sb.append(br.readLine()).append("\n");
-            }
-
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/ParallelWrapper.java

@@ -1,103 +1,0 @@
-package edu.unh.schwartz.parawrap;
-
-import edu.unh.schwartz.parawrap.config.Configuration;
-import edu.unh.schwartz.parawrap.config.ConfigWizard;
-import edu.unh.schwartz.parawrap.io.Manipulator;
-import edu.unh.schwartz.parawrap.worker.WorkerPool;
-import java.io.IOException;
-import java.util.concurrent.PriorityBlockingQueue;
-
-/**
- * Application class. Takes an optional command line parameter for the run
- * configuration. If none is given, goes through the wizard to create one,
- * which will then allow the user to save it for later runs. Calls the split
- * operation, starts the workers, calls the move operation and then prints
- * statistics about the run to 'stats.csv'.
- *
- * @author Jacob Schwartz
- */
-final class ParallelWrapper
-{
-    private ParallelWrapper() 
-    {
-        // No-op
-    }
-
-    /**
-     * Starts the parallel wrapper based on the <code>Configuration</code>.
-     *
-     * @param config - the instructions for the wrapper
-     */
-    private static void start(final Configuration config)
-    {
-        Chunk.setHeaderLines(config.getNumHeaderLines());
-
-        // Read in the input file and get the chunks
-        final Manipulator manip = new Manipulator(config.getSplitPattern(), 
-            config.getNumHeaderLines());
-
-        try
-        {
-            manip.split(config.getInputFileName());
-        }
-        catch (IOException e)
-        {
-            System.err.print(e.getMessage());
-            return;
-        }
-
-        final PriorityBlockingQueue<Chunk> chunks = manip.getChunks();
-        if (chunks.size() == 0)
-        {
-            System.err.println("Incorrect chunk pattern or empty input file");
-            return;
-        }
-
-        final WorkerPool wp = new WorkerPool(config, chunks);
-        wp.start();
-        manip.merge(config.getOutputDirectory() + "/done.txt");
-        if (config.makeStats())
-        {
-            manip.printStats(wp.getStats(), config.getOutputDirectory());
-        }
-        manip.cleanUp();
-    }
-
-    /**
-     * Main method. Can be run with 0 or 1 cmd line args.
-     *
-     * @param args - Command line arguments
-     */
-    public static void main(final String[] args) 
-    {
-        // If there are no cmd line args, create a configuration file
-        if (args.length == 0)
-        {
-            // Allow the user to make a configuration file
-            System.out.println("Opening Configuration Wizard");
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/config/ConfigWizard.java

@@ -1,304 +1,0 @@
-package edu.unh.schwartz.parawrap.config;
-
-import java.awt.Dimension;
-import java.util.ArrayList;
-import java.util.List;
-// import javax.swing.border.EmptyBorder;
-import javax.swing.JCheckBox;
-import javax.swing.JDialog;
-import javax.swing.JLabel;
-import javax.swing.JTextField;
-import org.ciscavate.cjwizard.PageFactory;
-import org.ciscavate.cjwizard.pagetemplates.DefaultPageTemplate;
-import org.ciscavate.cjwizard.WizardContainer;
-import org.ciscavate.cjwizard.WizardListener;
-import org.ciscavate.cjwizard.WizardPage;
-import org.ciscavate.cjwizard.WizardSettings;
-
-/**
- * GUI Wizard to help create configuration file.
- */ 
-public final class ConfigWizard
-{
-    /**
-     * The instance.
-     */
-    private static ConfigWizard instance;
-
-    /**
-     * The last configuration created.
-     */ 
-    private Configuration config;
-
-    /**
-     * The window for the wizard.
-     */
-    private JDialog window;
-
-    /**
-     * Prevents instantiation.
-     */
-    private ConfigWizard()
-    {
-        window = new JDialog();
-
-        final WizardContainer wc = 
-            new WizardContainer(new ConfigPageFactory(),
-                    new DefaultPageTemplate());
-
-        wc.addWizardListener(new ConfigWizardListener());
-
-        window.setDefaultCloseOperation(JDialog.DISPOSE_ON_CLOSE);
-        window.getContentPane().add(wc);
-        window.setSize(375, 250);
-        window.setLocationRelativeTo(null);
-    }
-
-    /**
-     * @return the instance of the <code>ConfigWizard</code>
-     */
-    public static ConfigWizard getInstance()
-    {
-        if (instance == null)
-        {
-            instance = new ConfigWizard();
-        }
-        return instance;
-    }
-
-    /**
-     * Goes through the process of creating a configuration file. Saves it?
-     *
-     * @return the configuration created by the user
-     */
-    public Configuration createConfiguration()
-    {
-        this.window.setVisible(true);
-        synchronized(this)
-        {
-            try
-            {
-                this.wait();
-            }
-            catch (InterruptedException e)
-            {
-                System.err.println("Oh noes!");
-            }
-        }
-
-        return this.config;
-    }
-
-    /**
-     * Handles the callbacks from the wizard.
-     */
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/config/Configuration.java

@@ -1,290 +1,0 @@
-package edu.unh.schwartz.parawrap.config;
-
-// import com.fasterxml.jackson.core.JsonFactory;
-// import com.fasterxml.jackson.core.JsonParser;
-// import com.fasterxml.jackson.core.JsonToken;
-// import java.io.File;
-// import java.io.IOException;
-import java.util.HashMap;
-import java.util.Map;
-import java.util.Iterator;
-
-/**
- * The settings for the current run of the application. 
- *
- * Talk about the various fields it contains
- */
-public final class Configuration
-{
-    /**
-     * Key for in file setting.
-     */
-    public static final String IN_FILE_KEY = "inFile";
-
-    /**
-     * Key for split pattern setting.
-     */
-    public static final String SPLIT_PATTERN_KEY = "split";
-
-    /**
-     * Key for out file setting.
-     */
-    public static final String OUT_FILE_KEY = "outFile";
-
-    /**
-     * Key for executable location setting.
-     */
-    public static final String EXEC_LOC_KEY = "execLoc";
-
-    /**
-     * Key for in flag setting.
-     */
-    public static final String IN_FLAG_KEY = "inFlag";
-
-    /**
-     * Key for out flag setting.
-     */
-    public static final String OUT_FLAG_KEY = "outFlag";
-    
-    /**
-     * Key for threading setting.
-     */
-    public static final String NUM_PROCESSES_KEY = "numProcesses";
-
-    /**
-     * Key for stats setting.
-     */
-    public static final String STATS_KEY = "stats";
-
-    /**
-     * Key for output file header setting.
-     */
-    public static final String NUM_HEADER_KEY = "numHeaderLines";
-
-    /**
-     * The number of threads used.
-     */
-    private int numberOfThreads;
-    
-    /**
-     * The name of the input file.
-     */
-    private String inputFileName;
-    
-    /**
-     * The regex pattern to split the input file on.
-     */
-    private String splitPattern;
-
-    /**
-     * The directory where the output should go.
-     */
-    private String outDirName;
-
-    /**
-     * The path to the executable.
-     */
-    private String execPath;
-
-    /**
-     * The flags for the executable to show how to enter input and outfile.
-     */
-    private String inFlag;
-    private String outFlag;
-
-    /**
-     * The arguments for the execuatable.
-     */
-    private Map<String, String> execArgs;
-
-    /**
-     * Whether or not to make a stats file.
-     */
-    private boolean makeStats;
-
-    /**
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/config/JFileChooserButton.java

@@ -1,89 +1,0 @@
-package edu.unh.schwartz.parawrap.config;
-
-import org.ciscavate.cjwizard.CustomWizardComponent;
-import java.awt.event.ActionEvent;
-import java.awt.event.ActionListener;
-import java.io.File;
-import javax.swing.JButton;
-import javax.swing.JDialog;
-import javax.swing.JFileChooser;
-
-/**
- * Clab.
- */
-final class JFileChooserButton extends JButton implements CustomWizardComponent
-{
-    /**
-     * The dialog for the file choosers.
-     */
-    private JDialog dialog;
-    
-    /**
-     * The file chooser that appears when the button clicked.
-     */
-    private JFileChooser fc;
-    
-    /**
-     * The path of the file selected by the user.
-     */
-    private String path;
-
-    /**
-     * Constructs a new button.
-     * @param directoriesOnly - allow the user to select directories only iff
-     * true. otherwise, user can only select files
-     */
-    public JFileChooserButton(final boolean directoriesOnly)
-    {
-        super("...");
-        this.dialog = new JDialog();
-        this.fc = new JFileChooser(".");
-
-        if (directoriesOnly)
-        {
-            fc.setFileSelectionMode(JFileChooser.DIRECTORIES_ONLY);
-        }
-        else
-        {
-            fc.setFileSelectionMode(JFileChooser.FILES_ONLY);
-        }
-    
-        this.addActionListener(new ActionListener()
-        {
-            /**
-             * {@inheritDoc}
-             */
-            public void actionPerformed(final ActionEvent e)
-            {
-                final int returnVal = fc.showOpenDialog(dialog);
-                switch (returnVal)
-                {
-                    case JFileChooser.APPROVE_OPTION:
-                        final File f = fc.getSelectedFile();
-                        setValue(f.getPath());
-                        setText(f.getName());
-                        JFileChooserButton.this.dialog.dispose();
-                        break;
-                    default:
-                        break;
-                }
-            }
-        });
-    }
-
-    /**
-     * {@inheritDoc}
-     */               
-    public Object getValue()
-    {
-        return this.path;
-    }
-
-    /**
-     * {@inheritDoc}
-     */
-    public void setValue(final Object o)
-    {
-        this.path = (String) o;
-    }
-}

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/config/WizardSpinner.java

@@ -1,22 +1,0 @@
-package edu.unh.schwartz.parawrap.config;
-
-import org.ciscavate.cjwizard.CustomWizardComponent;
-import java.util.List;
-import javax.swing.SpinnerListModel;
-import javax.swing.JSpinner;
-
-/**
- * Clab.
- */
-final class WizardSpinner extends JSpinner implements CustomWizardComponent
-{
-    /**
-     * Makes a new spinner with the provided options.
-     *
-     * @param options - the choices of the spinner
-     */
-    public WizardSpinner(final List<String> options)
-    {
-        super(new SpinnerListModel(options));
-    }
-}

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/io/Manipulator.java

@@ -1,205 +1,0 @@
-package edu.unh.schwartz.parawrap.io;
-
-import edu.unh.schwartz.parawrap.Chunk;
-import java.io.BufferedReader;
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.FileReader;
-import java.io.IOException;
-import java.io.PrintWriter;
-import java.util.ArrayList;
-import java.util.concurrent.PriorityBlockingQueue;
-import java.util.List;
-import java.util.regex.Pattern;
-
-/**
- * Does all of the IO functions for the process. Can split an input file based
- * on a pattern and merge it back together in the same order.
- */
-public final class Manipulator
-{
-    /**
-     * The default pattern for a manipulator.
-     */
-    private static final String DEFAULT_PATTERN = "^.*$";
-
-    /**
-     * The pattern used to split the input file.
-     */
-    private Pattern pattern;
-    
-    /**
-     * The chunks for the current input file.
-     */
-    private List<Chunk> chunks;
-
-    /**
-     * The number of header lines to put in the final output file.
-     */
-    private int headerLines;
-
-    /**
-     * Constructs a manipulator with the default pattern and 0 header lines.
-     */
-    public Manipulator()
-    {
-        this(DEFAULT_PATTERN, 0);
-    }
-
-    /**
-     * Constructs a manipulator with the default pattern and some number of 
-     * header lines.
-     *
-     * @param headerLines - the number of header lines to take from output files
-     */
-    public Manipulator(final int headerLines)
-    {
-        this(DEFAULT_PATTERN, headerLines);
-    }
-
-    /**
-     * Constructs a manipulator with a custom pattern and some number of header
-     * lines.
-     *
-     * @param regex - Regular expression to split on
-     * @param headerLines - the number of header lines to take from output files
-     */
-    public Manipulator(final String regex, final int headerLines)
-    {
-        this.pattern = Pattern.compile(regex);
-        this.headerLines = headerLines;
-    }
-
-    /**
-     * Splits the file and creates chunks.
-     *
-     * @param fileName - the name of the file
-     * @throws IOException - when there is any kind of problem with the input
-     */
-    public void split(final String fileName) throws IOException 
-    {
-        this.chunks = new ArrayList<Chunk>();
-
-        StringBuilder sb = new StringBuilder();
-        
-        final File f = new File(fileName);
-        final BufferedReader reader = new BufferedReader(new FileReader(f));
-        String line = reader.readLine();
-        while (line != null)
-        {
-            sb.append(line);
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/io/package-info.java

@@ -1,5 +1,0 @@
-/**
- * Provides classes that deal with file I/O of the chunks of work: spliting,
- * merging, etc.
- */
-package edu.unh.schwartz.parawrap.io;

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/package-info.java

@@ -1,4 +1,0 @@
-/**
- * Contains the application class and other classes used throughout the program.
- */
-package edu.unh.schwartz.parawrap;

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/worker/Worker.java

@@ -1,197 +1,0 @@
-package edu.unh.schwartz.parawrap.worker;
-
-import edu.unh.schwartz.parawrap.Chunk;
-import java.io.IOException;
-import java.util.concurrent.PriorityBlockingQueue;
-import java.util.ArrayList;
-import java.util.List;
-
-/**
- * Runs the process on the queued up input. Each worker has an id and keeps
- * various statistical information to use later to determine if the
- * configuration could be better.
- */
-public final class Worker extends Thread
-{
-    /**
-     * The path to the executable.
-     */
-    private static String EXEC;
-
-    /**
-     * The in flag for the executable.
-     */
-    private static String IN_FLAG;
-
-    /**
-     * The out flag for the executable.
-     */
-    private static String OUT_FLAG;
-
-       /**
-     * The queue of pieces to do work on.
-     */
-    private PriorityBlockingQueue<Chunk> queue;
-    
-    /**
-     * The id number of this worker.
-     */
-    private int idNum;
-    
-    /**
-     * The sum of run times of executable.
-     */
-    private long runTime;
-
-    /**
-     * The number of chunks run by this worker.
-     */
-    private int chunksRun;
-
-    /**
-     * Creates a worker.
-     *
-     * @param idNum - the id number of this worker
-     * @param queue - the queue for the worker to take chunks from
-     */
-    public Worker(final int idNum, final PriorityBlockingQueue<Chunk> queue)
-    {
-        this.queue = queue;
-        this.idNum = idNum;
-        this.runTime = 0;
-        this.chunksRun = 0;
-    }
-
-    /**
-     * Set the path to the executable.
-     *
-     * @param exec - the path to the executable
-     */
-    public static void setExecutable(final String exec)
-    {
-        System.err.println(exec);
-        EXEC = exec;
-    }
-    
-    /**
-     * Set the flag to signify where the input goes for the executable.
-     *
-     * @param inFlag - the in flag used to signify the input file 
-     */
-    public static void setInFlag(final String inFlag)
-    {
-        IN_FLAG = inFlag;
-    }
-
-    /**
-     * Set the flag to signify where the output goes for the executable.
-     *
-     * @param outFlag - the flag used to signify the output file 
-     */
-    public static void setOutFlag(final String outFlag)
-    {
-        OUT_FLAG = outFlag;
-    }
-
-    /**
-     * {@inheritDoc}
-     */
-    @Override
-    public void run()
-    {
-        // Until we run out of chunks
[…]

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/worker/WorkerPool.java

@@ -1,83 +1,0 @@
-package edu.unh.schwartz.parawrap.worker;
-
-import edu.unh.schwartz.parawrap.Chunk;
-import edu.unh.schwartz.parawrap.config.Configuration;
-import java.util.concurrent.PriorityBlockingQueue;
-
-/**
- * Creates and starts the <code>Worker</code>s.
- */
-public final class WorkerPool
-{
-    /**
-     * The workers to be utilizated.
-     */
-    private Worker[] workers;
-
-    /**
-     * Constructs the workers.
-     *
-     * @param config - information for the run
-     * @param chunks - the work for the workers
-     */
-    public WorkerPool(final Configuration config, 
-        final PriorityBlockingQueue<Chunk> chunks)
-    {
-        // Set the executable information in the worker
-        Worker.setExecutable(config.getExecutable());
-        Worker.setInFlag(config.getInFlag());
-        Worker.setOutFlag(config.getOutFlag());
-
-        // Initialize the threads
-        workers = new Worker[config.getNumberOfThreads()];
-        for (int i = 0; i < workers.length; i++)
-        {
-            workers[i] = new Worker(i, chunks);
-        }
-    }
-
-    /**
-     * Start the workers.
-     */
-    public void start()
-    {
-        for (int i = 0; i < workers.length; i++)
-        {
-            workers[i].start();
-        }
-
-        try
-        {
-            for (int i = 0; i < workers.length; i++)
-            {
-                workers[i].join();
-            }
-        }
-        catch (InterruptedException e)
-        {
-            System.err.println("Thread interrupted");
-            System.exit(1);
-        }
-    }
-
-    /**
-     * @return the statistics for the <code>Worker</code> in a csv table
-     */
-    public String getStats()
-    {
-        // Print the stats
-        final StringBuilder sb = new StringBuilder();
-        sb.append("Thread #,Runtime(ms),Chunks Run,Avg Time Per Chunk(ms)\n");
-        final String comma = ",";
-        for (int i = 0; i < workers.length; i++)
-        {
-            final long runtime = workers[i].getRunTime();
-            final int chunks = workers[i].getChunksRun();
-            sb.append(i).append(comma).append(runtime).append(comma);
-            sb.append(chunks).append(comma).append(runtime / chunks);
-            sb.append('\n');
-        }
-        sb.append('\n');
-        return sb.toString();
-    }
-}

### 2013-11-06 src/main/java/edu/unh/schwartz/parawrap/worker/package-info.java

@@ -1,5 +1,0 @@
-/**
- * Classes to do the execution on the work and hold statistics about the
- * runtimes and length of the work.
- */
- package edu.unh.schwartz.parawrap.worker;

### 2013-11-08 examples/octupus/octu3.pl
Begininng of Octupu examples

@@ -1,0 +1,2007 @@
+#!/usr/bin/perl
+#---  octu3.pl  - rdb derived from octu2.pl on 4/27/12
+#                 besides preserving existing code to simplify later 
+#                 (possibly extensive) comparisons. 
+#                 Goal of this version is to get all satisfactory hits
+#                 and pick the one with the longest match region -- or 
+#                 possibly other criteria.
+#
+# Way Sung 10/2008
+# Edited by Dan Bergeron March/April 2012
+#
+# rdb: This version is an attempt to reduce the i/o. It maintains all 
+#      octu information in hash tables, so it never needs to re-read it; it
+#      still needs to append to the octulist file when a new octu is created
+#      and re-write it whenever an octu's consensus is changed.
+#---------------------------------------------------------------------
+#    This file is part of OCTUPUS.
+
+#    OCTUPUS is free software: you can redistribute it and/or modify
+#    it under the terms of the GNU General Public License as published by
+#    the Free Software Foundation, either version 3 of the License, or
+#    (at your option) any later version.
+
+#    OCTUPUS is distributed in the hope that it will be useful,
+#    but WITHOUT ANY WARRANTY; without even the implied warranty of
+#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
+#    GNU General Public License for more details.
+
+#    You should have received a copy of the GNU General Public License
+#    along with OCTUPUS.  If not, see <http://www.gnu.org/licenses/>.
+#
+# History as of 03/29/2012 rdb
+#----------------- octu2.pl -----------------------------------------------
+# 03/29-4/5/2012 rdb
+#    Functional changes
+#    1. revised finishing code that used "sed"; it didn't work on Mac OS X
+#    2. changed command line parameter conventions and checking
+#          -test for non-numeric and invalid % and length
+#          -changed default directory to one composed of fasta file name, 
+#           % and min length such as: harvardSite_95_100. To use cwd, use "."
+#    3. Found bug in test for recomputing consensus; code tested exactMatchCount
+#       for the octu (%matchNum) rather than the octu count (%octuCount). This
+#       should actually give better results (for more time) since it was
+#       essentially nearly always recomputing the consensus.
+#       For a 500 sequence test, the matchNum version is about 50% slower than
+#       the octuCount version (32 secs vs 22 secs on macbook air). The octu
+#       result differences were very small; it looks like all the octus were
[…]

### 2013-11-10 paper/paper.tex
Paper revision #2 completed

@@
 potential to take several days to run on a data set. In fact, there are several
-embarrassingly parallel programs in the biological sciences. 
-TALK ABOUT CLUSTERING
-With several applications that 
-would benefit from parallelism in this field, it was obvious it would be 
-desirable to develop a framework for creating wrapper programs.
+embarrassingly parallel programs in the biological sciences. To deal with large
+amounts of data, the best method is often to group them into clusters. 
+Hierarchical clustering algorthms take the data and then organize into
+hierarchical structure, usually a dendrogram, based on a priority matric. There 
+are hierarchical clustering algorithms that can be implemented in parallel using
+an embarrassingly parallel approach.  With several applications that would 
+benefit from parallelism in this field, it was obvious it would be desirable to 
+develop a framework for creating wrapper programs. \cite{cluster}
 
@@
 \bibitem{history}
-Moler, Cleve. "Matrix Computation on Distributed Memory Multiprocessors."
-Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
+Moler, Cleve. ``\emph{Matrix Computation on Distributed Memory Multiprocessors."
+}, Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
 Hypercube Multiprocessors, Knoxville, Tennessee, August 24-27, 1985. By Michael
@@
 \bibitem{kaks}
-Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., ``\emph{KaKs Calculator: 
-calculating Ka and Ks through model selection and model averaging.},'',
+Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{KaKs Calculator: 
+calculating Ka and Ks through model selection and model averaging},
 Genomics Proteomics Bioinformatics, November 2006.
+\bibitem{cluster}
+Rua, Xu, Wunsch, Donald II, \emph{Survey of Clustering Algorithms},
+IEEE Transactions on Neural Networks VOL. 16, NO. 3, MAY 2005
 \end{thebibliography}

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/Chunk.java
Configuration saving and beginning of directory input

@@ -4,6 +4,7 @@ import java.io.BufferedReader;
 import java.io.File;
 import java.io.FileReader;
 import java.io.IOException;
+import java.nio.file.Files;
 import org.apache.commons.logging.Log;
 import org.apache.commons.logging.LogFactory;
 
@@ -19,7 +20,7 @@ public final class Chunk implements Comparable<Chunk>
     private static int headerLines;
 
     /**
-     * the log.
+     * The log.
      */
     private static final Log LOG = LogFactory.getLog(Chunk.class);
 
@@ -47,6 +48,35 @@ public final class Chunk implements Comparable<Chunk>
     {
         this.content = content;
         this.directory = directory;
+    }
+
+    /**
+     * Constructs a chunk based off a file and the directory for the chunk.
+     * @param inFile - the file that contains the chunk's content
+     * @param directory - the directory for the chunk's IO
+     * @throws IOException is there is problem copying the file to the directory
+     * or reading the content
+     */
+    public Chunk(final File inFile, final File directory) throws IOException
+    {
+        this.directory = directory;
+
+        final StringBuilder sb = new StringBuilder();
+        final BufferedReader br = new BufferedReader(new FileReader(inFile));
+        String line = br.readLine();
+        while (line != null) 
+        {
+            sb.append(line);
+            sb.append('\n');
+            line = br.readLine();
+        }
+        br.close();
+
+        this.content = sb.toString();
+
+        // Write the content to a file in the directory
+        Files.copy(inFile.toPath(), 
+            new File("tmp" + inFile.getName()).toPath());
     }
 
     /**

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/EPFramework.java

@@ -20,16 +20,12 @@ import org.apache.commons.logging.LogFactory;
  */
 final class EPFramework
 {
-<<<<<<< HEAD:src/main/java/edu/unh/schwartz/parawrap/ParallelWrapper.java
     /**
      * The Log.
      */
-    private static Log LOG = LogFactory.getLog(ParallelWrapper.class);
+    private static Log LOG = LogFactory.getLog(EPFramework.class);
 
-    private ParallelWrapper() 
-=======
     private EPFramework() 
->>>>>>> d0b9a24644e979bcd84a296ab9f48a3ad1dfed4b:src/main/java/edu/unh/schwartz/epframework/EPFramework.java
     {
         // No-op
     }
@@ -43,13 +39,23 @@ final class EPFramework
     {
         Chunk.setHeaderLines(config.getNumHeaderLines());
 
-        // Read in the input file and get the chunks
-        final Manipulator manip = new Manipulator(config.getSplitPattern(), 
-            config.getNumHeaderLines());
-
+        Manipulator manip = null;
         try
         {
-            manip.split(config.getInputFileName());
+            if (config.getInputFile() == null)
+            {
+                // Make a chunk for each presplit file
+                manip = new Manipulator(config.getNumHeaderLines());
+                manip.splitFiles(config.getInputDirectory());
+            }
+            else
+            {
+                // Read in the input file and get the chunks
+                manip = new Manipulator(config.getSplitPattern(), 
+                        config.getNumHeaderLines());
+
+                manip.split(config.getInputFile());
+            }
         }
         catch (IOException e)
         {
@@ -57,6 +63,7 @@ final class EPFramework
             return;
         }
 
+        // Get the chunks made my the manipulator
         final PriorityBlockingQueue<Chunk> chunks = manip.getChunks();
         if (chunks.size() == 0)
         {
@@ -64,9 +71,14 @@ final class EPFramework
             return;
         }
 
+        // Start the workers
         final WorkerPool wp = new WorkerPool(config, chunks);
         wp.start();
+
+        // Merge the results back together
         manip.merge(config.getOutputDirectory() + "/done.txt");
+
+        // Make stats if instructed to 
         if (config.makeStats())
         {
             manip.printStats(wp.getStats(), config.getOutputDirectory());

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -1,10 +1,12 @@
 package edu.unh.schwartz.epframework.config;
 
-// import com.fasterxml.jackson.core.JsonFactory;
-// import com.fasterxml.jackson.core.JsonParser;
-// import com.fasterxml.jackson.core.JsonToken;
-// import java.io.File;
-// import java.io.IOException;
+import com.fasterxml.jackson.core.JsonEncoding;
+import com.fasterxml.jackson.core.JsonFactory;
+import com.fasterxml.jackson.core.JsonGenerator;
+import com.fasterxml.jackson.core.JsonParser;
+import com.fasterxml.jackson.core.JsonToken;
+import java.io.File;
+import java.io.IOException;
 import java.util.HashMap;
 import java.util.Map;
 import java.util.Iterator;
@@ -22,6 +24,11 @@ public final class Configuration
      * Key for in file setting.
      */
     public static final String IN_FILE_KEY = "inFile";
+
+    /**
+     * Key for in file directory setting.
+     */
+    public static final String IN_FILE_DIR_KEY = "inFileDir";
 
     /**
      * Key for split pattern setting.
@@ -77,7 +84,12 @@ public final class Configuration
      * The name of the input file.
      */
     private String inputFileName;
-    
+     
+    /**
+     * The name of the input directory file.
+     */
+    private String inputFileDirName;
+
     /**
      * The regex pattern to split the input file on.
      */
@@ -132,6 +144,9 @@ public final class Configuration
                  case IN_FILE_KEY:
                     this.inputFileName = (String) val;
                     break;
+                case IN_FILE_DIR_KEY:
+                    this.inputFileDirName = (String) val;
+                    break;
                  case SPLIT_PATTERN_KEY:
                     this.splitPattern = (String) val;
                     break;
@@ -165,37 +180,59 @@ public final class Configuration
     }
 
     /**
-     * Constructs a configuration file from a saved copy.
-     * @param jsonFile - the file holding the saved configuration file
-     */
-    // public Configuration(final File jsonFile)
-    // {
-
-    // }
-
-    /**
      * Constructs a configuration file from a past configuration file that was
      * saved to the disk.
      *
      * @param fileName - the path to the file on disk
      * @throws IOException - if there is any problem reading the file
      */
-    // public Configuration(final String fileName) throws IOException
-    // {
-        // final JsonFactory jf = new JsonFactory();
-        // final JsonParser jp = jf.createJsonParser(new File(fileName));
[…]

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/io/Manipulator.java

@@ -104,10 +104,6 @@ public final class Manipulator
                 final File dir = new File("/tmp/" + content.hashCode());
                 dir.mkdir();
 
-                // Make the new file
-                // final File in = new File(dir.getName() + "/in");
-                // in.createNewFile();
-
                 // Write the content to a file
                 final PrintWriter inWriter = new PrintWriter(dir.getAbsolutePath() + "/in");
                 inWriter.println(content);
@@ -123,6 +119,24 @@ public final class Manipulator
             }
 
             line = reader.readLine();
+        }
+    }
+
+    /**
+     * Make chunks for the pre-split input files.
+     * @param dir - the directory of pre-split files
+     * @throws IOException if there is any problem with the files in the
+     * directory
+     */
+    public void splitFiles(final String dir) throws IOException
+    {
+        this.chunks = new ArrayList<Chunk>();
+
+        final File directory = new File(dir);
+        for (File i : directory.listFiles())
+        {
+            final File d = new File("tmp/" + i.getName().hashCode());
+            this.chunks.add(new Chunk(i , d));
         }
     }
     

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/EPFramework.java
Loading configuration files and seperators in wizard

@@ -106,24 +106,25 @@ final class EPFramework
             }
         }
         // First command line arg is a configuration file
-        // else if (args.length == 1)
-        // {
-            // try
-            // {
-                // final Configuration config = new Configuration(args[0]);
-                // start(config);
-            // }
-            // catch (IOException e)
-            // {
-                // System.err.println("Problem reading configuation file: " + 
-                        // e.getMessage());
-            // }
-        // }
-        // else
-        // {
-            // System.err.print("Usage:\n\tTakes only one option args:\n\t\t");
-            // System.err.print("- The configuration file's location\n\n");
-            // System.err.println("No arguments will bring up the wizard");
-        // }
+        else if (args.length == 1)
+        {
+            try
+            {
+                LOG.debug("Loading configuration file");
+                final Configuration config = new Configuration(args[0]);
+                start(config);
+            }
+            catch (IOException e)
+            {
+
+                LOG.fatal("Problem loading config file: " + e.getMessage());
+            }
+        }
+        else
+        {
+            System.err.print("Usage:\n\tTakes only one option args:\n\t\t");
+            System.err.print("- The configuration file's location\n\n");
+            System.err.println("No arguments will bring up the wizard");
+        }
     }
 }

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java

@@ -33,6 +33,11 @@ public final class ConfigWizard
     private static final Log LOG = LogFactory.getLog(ConfigWizard.class);
 
     /**
+     * Seperator string.
+     */
+    private static final String SEP = "---------------------------------------"; 
+
+    /**
      * The last configuration created.
      */ 
     private Configuration config;
@@ -168,20 +173,6 @@ public final class ConfigWizard
         }
     }
 
-    /**
-     * Border for all components.
-     */
-    // private static final EmptyBorder BORDER = new EmptyBorder(0, 0, 40, 0);
-
-    // private class Seperator extends JLabel
-    // {
-        // private Seperator()
-        // {
-            // super(" ");
-            // setBorder(BORDER);
-        // }
-    // }
-
     private final class IOPage extends WizardPage
     {
         private IOPage()
@@ -201,6 +192,16 @@ public final class ConfigWizard
             add(new JLabel("Pattern used to split input: "));
             add(splitField);
             add(new JLabel("(Leave blank to use every new line)"));
+
+            add((new JLabel("--------------- OR ---------------")));
+
+            // Settings for the input directory
+            final JFileChooserButton inDirChooser = new JFileChooserButton(true);
+            inDirChooser.setName(Configuration.IN_FILE_DIR_KEY);
+            add((new JLabel("Select the input directory: ")));
+            add(inDirChooser);
+
+            add(new JLabel(SEP));
 
             // Settings for the output location
             final JFileChooserButton outChooser = new JFileChooserButton(true);
@@ -222,6 +223,7 @@ public final class ConfigWizard
             execChooser.setName(Configuration.EXEC_LOC_KEY);
             add((new JLabel("Select the executable: ")));
             add(execChooser);
+            add(new JLabel(SEP));
 
             // Name for input and output flags
             // Setting for the split pattern
@@ -231,6 +233,7 @@ public final class ConfigWizard
             add(new JLabel("Flag for executable to define input file"));
             add(inFlagField);
             add(new JLabel("(Leave blank to use stdin)"));
+            add(new JLabel(SEP));
 
             // Setting for the split pattern
             final JTextField outFlagField = new JTextField();
@@ -255,18 +258,20 @@ public final class ConfigWizard
             while (i <= max)
             {
                 options.add(Integer.toString(i));
-                i *= 2;
+                i++;
             }
 
             final WizardSpinner spinner = new WizardSpinner(options);
[…]

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -71,6 +71,11 @@ public final class Configuration
     public static final String NUM_HEADER_KEY = "numHeaderLines";
 
     /**
+     * Key for setting whether or not to save the file.
+     */
+    public static final String SAVE_KEY = "save";
+
+    /**
      * The Log.
      */
     private static final Log LOG = LogFactory.getLog(Configuration.class);
@@ -142,19 +147,19 @@ public final class Configuration
              switch(key)
              {
                  case IN_FILE_KEY:
-                    this.inputFileName = (String) val;
-                    break;
-                case IN_FILE_DIR_KEY:
-                    this.inputFileDirName = (String) val;
-                    break;
+                     this.inputFileName = (String) val;
+                     break;
+                 case IN_FILE_DIR_KEY:
+                     this.inputFileDirName = (String) val;
+                     break;
                  case SPLIT_PATTERN_KEY:
-                    this.splitPattern = (String) val;
-                    break;
+                     this.splitPattern = (String) val;
+                     break;
                  case OUT_FILE_KEY:
-                    this.outDirName = (String) val;
-                    break;
+                     this.outDirName = (String) val;
+                     break;
                  case EXEC_LOC_KEY:
-                    this.execPath = (String) val;
+                     this.execPath = (String) val;
                      break;
                  case IN_FLAG_KEY: 
                      this.inFlag = (String) val;
@@ -170,6 +175,12 @@ public final class Configuration
                      break;
                  case NUM_HEADER_KEY:
                      this.numberOfHeaderLines = Integer.valueOf((String) val);
+                     break;
+                 case SAVE_KEY:
+                     if ((boolean) val)
+                     {
+                         saveConfig();
+                     }
                      break;
                  default:
                      assert(false);

### 2013-11-12 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java
Start of review page code

@@ -3,7 +3,6 @@ package edu.unh.schwartz.epframework.config;
 import java.awt.Dimension;
 import java.util.ArrayList;
 import java.util.List;
-// import javax.swing.border.EmptyBorder;
 import javax.swing.JCheckBox;
 import javax.swing.JDialog;
 import javax.swing.JLabel;
@@ -292,9 +291,18 @@ public final class ConfigWizard
             box.setName(Configuration.SAVE_KEY);
             add(new JLabel("Save Configuration File?"));
             add(box);
-            add(new JLabel(SEP));
+            // add(new JLabel(SEP));
 
-            add(new JLabel("This will eventually work"));
+            //TODO: Review entered values
+            // add(new JLabel("Confirm String:"));
+            // for(String key : settings.keySet())
+            // {
+                // Object val = settings.get(key);
+                // if (val != null && !val.equals(""))
+                // {
+                    // add(new JLabel(key + " : " + val + "\n"));
+                // }
+            // }
         }
 
         /**

### 2013-11-18 src/main/java/edu/unh/schwartz/epframework/io/Manipulator.java
external merge code

@@ -37,6 +37,12 @@ public final class Manipulator
      */
     private static final String DEFAULT_PATTERN = "^.*$";
 
+   /**
+     * The file name for the executable that will do an external merge if that
+     * configuration was chosen.
+     */
+    private static final String EXTERNAL_MERGE_EXEC_NAME = "./merger";
+
     /**
      * The pattern used to split the input file.
      */
@@ -202,12 +208,35 @@ public final class Manipulator
         CustomMerge.merge(fileName, this.chunks);
     }
 
-    private void externalMerge(final String fileName)
+    private void externalMerge(final String fileName) 
     {
-        // Use the code to open an executable with the command line arguments
-        // being
-    }
+        // Prepare the args
+        final List<String> commands = new ArrayList<String>();
+        commands.add(EXTERNAL_MERGE_EXEC_NAME);
+        for (final Chunk c : this.chunks)
+        {
+            commands.add(c.getDirectory().getAbsolutePath());
+        }
 
+        try
+        {
+            // Create the process builder
+            final ProcessBuilder pb = new ProcessBuilder(commands);
+            pb.redirectErrorStream(true);
+            pb.redirectOutput(new File(fileName));
+
+            // Start the work and capture the time it takes to run
+            LOG.info("Starting external merge");
+            final Process proc = pb.start();
+            proc.waitFor();
+            LOG.info("Finished external merge");
+        }
+        catch (IOException|InterruptedException e)
+        {
+            LOG.fatal("externalMerge: " + e.getMessage());
+        }
+    }
+    
     /**
      * Cleans up the chunks and temp out files and directories.
      */

### 2013-11-20 paper/paper.tex
Renamed Manipulator and did some work on paper and readme

@@
 threads. These threads working together help cut down the total runtime
-exponentially. More statistics, savable configurations and more options will be 
-implemented next, in addition to better testing and refactored.
+exponentially. The next step is to seperate the framework into a front-end that
+will run locally and the back-end which recieves blocks of work and does the
+computations. This back-end should be running in the cloud, on a machine who is
+dedicated to running embarrassingly parallel tasks only.
 \end{abstract}
@@
 input the same and creating the output in the same format. This paper describes
-a framework a framework that makes it easy to parallelize an embarrassingly
+a framework that makes it easy to parallelize an potentially embarrassingly
 parallel program that reads from a file, writes to a file and whose input can be
@@
 The motivation for this effort was with research into different forms of the 
-species \emph{Cicer arietinum}, the chikckpea. The two main forms, Kabuli and 
+species \emph{Cicer arietinum}, the chickpea. The two main forms, Kabuli and 
 Desi, are very different in size and color but we mostly wanted to see why the 
@@
 
+%TODO: get a better source? Talk about UCLUST and octupus
 The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
@@
 
-% TALK ABOUT PAPER HERE. AND MAYBE THE POWERPOINT TOO.
-
-In this version of the framework, several components are being added. First, 
-there is a wizard style menu that will allow the end-user to select not only the 
-program that wish to use, but also to manage other settings for the run. A new 
-IO class splits the input and merges the output more efficiently. Lastly, in 
-order to look at how well the framework performs, the threads keep their own 
-statistics, which will be used to evaluate the effectiveness of the framework 
-and to find potential enhancements and help end-users determine whether their 
-use of the framework is efficient.
+%TODO: TALK ABOUT CLOUD PAPER HERE. AND MAYBE THE POWERPOINT TOO.
 
@@
 \end{figure}
-The KaKs Calculator is not the only program to use the framework; there are
-various potential programs that the framework could support. The only 
-requirements for the this program are that it process the input in an 
-embarrassingly parallel manner and that the input comes from a file and the 
-processed results are also writen to a file. The framework needs to support 
-various kinds of input files and be able to chunk up the work accordingly. The 
-Ka/Ks Calculator's input consists of a header and then two protein sequence 
-lines followed by a blank line. The framework uses that blank line to know when 
-one chunk of work has ended and another has begun. The user can input a regular 
-expression to define what lines of input make up what chunks. This occurs in 
-the ChunkManager class.
+The only requirements for a program to be wrapped by framework are that it 
+process the input in an embarrassingly parallel manner and that the input comes 
+from a file. The processed results are must also written to a file. The 
+framework supports two forms of input: a directory of files that contain that 
+each contain one unit of work, which is represented by the Chunk class, or a 
+single file that the framework can break up into Chunks. For example, the Ka/Ks 
+Calculator's input consists of a header and then two protein sequence lines 
+followed by a blank line. The framework uses that blank line to know when one 
+Chunk of work has ended and another has begun. The user can input a regular 
+expression to define when lines of input are seperated into Chunks. This occurs 
+in the ChunkManager class.
 
-The other purpose of the ChunkManager class is to combine the resulting chunks 
+The other purpose of the ChunkManager class is to combine the resulting Chunks 
 back together when the worker threads have finished. Once the work has been
@@
 the inputs in the input file and headers may need to be deleted from the
-separate files and added to the combined file.
+separate files and added to the combined file. There are two other options if
+the end-user does not want this behavior. They can choose to write their own
+merger in Java, using the CustomMerge class, or write their own script to do the
+merging.
 
@@
 type of input data. The statistics for each thread can be found in the Worker 
-subclass and the individual Chunk classes will store their own statstics about 
+subclass and the individual Chunk objects will store their own statstics about 
 runtime and size.
@@
 To observe how the framework changes the runtime of sequential programs when
-using varying numbers of threads, I designed a simple experiment. The Ka/Ks 
+using varying numbers of threads, we designed a simple experiment. The Ka/Ks 
 Calculator was run through the framework with ten different samples, each 
@@
 
+%TODO: Rewrite with new next steps
 There are several next steps in the pipeline. In addition to using the
@@
 
+%TODO: Does this still make sense
 Using Java was a good choice for implementation ease and future implementation
@@
 \bibitem{kaks}
-Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{KaKs Calculator: 
+Zhang Z, Li J, Zhao XQ, Wang J, Wong GK, Yu J., \emph{Ka/Ks Calculator: 
 calculating Ka and Ks through model selection and model averaging},

### 2013-11-20 src/main/java/edu/unh/schwartz/epframework/ChunkManager.java

@@ -1,6 +1,5 @@
-package edu.unh.schwartz.epframework.io;
+package edu.unh.schwartz.epframework;
 
-import edu.unh.schwartz.epframework.Chunk;
 import java.io.BufferedReader;
 import java.io.File;
 import java.io.FileNotFoundException;
@@ -18,7 +17,7 @@ import org.apache.commons.logging.LogFactory;
  * Does all of the IO functions for the process. Can split an input file based
  * on a pattern and merge it back together in the same order.
  */
-public final class Manipulator
+public final class ChunkManager
 {
     private enum MergeMethod
     {
@@ -30,7 +29,7 @@ public final class Manipulator
     /**
      * The Log.
      */
-    private static final Log LOG = LogFactory.getLog(Manipulator.class);
+    private static final Log LOG = LogFactory.getLog(ChunkManager.class);
 
    /**
      * The default pattern for a manipulator.
@@ -61,7 +60,7 @@ public final class Manipulator
     /**
      * Constructs a manipulator with the default pattern and 0 header lines.
      */
-    public Manipulator()
+    public ChunkManager()
     {
         this(DEFAULT_PATTERN, 0);
     }
@@ -72,7 +71,7 @@ public final class Manipulator
      *
      * @param headerLines - the number of header lines to take from output files
      */
-    public Manipulator(final int headerLines)
+    public ChunkManager(final int headerLines)
     {
         this(DEFAULT_PATTERN, headerLines);
     }
@@ -84,7 +83,7 @@ public final class Manipulator
      * @param regex - Regular expression to split on
      * @param headerLines - the number of header lines to take from output files
      */
-    public Manipulator(final String regex, final int headerLines)
+    public ChunkManager(final String regex, final int headerLines)
     {
         this.pattern = Pattern.compile(regex);
         this.headerLines = headerLines;

### 2013-11-20 src/main/java/edu/unh/schwartz/epframework/CustomMerge.java

@@ -1,6 +1,5 @@
-package edu.unh.schwartz.epframework.io;
+package edu.unh.schwartz.epframework;
 
-import edu.unh.schwartz.epframework.Chunk;
 import java.util.List;
 
 /**

### 2013-11-20 src/main/java/edu/unh/schwartz/epframework/EPFramework.java

@@ -2,7 +2,6 @@ package edu.unh.schwartz.epframework;
 
 import edu.unh.schwartz.epframework.config.Configuration;
 import edu.unh.schwartz.epframework.config.ConfigWizard;
-import edu.unh.schwartz.epframework.io.Manipulator;
 import edu.unh.schwartz.epframework.worker.WorkerPool;
 import java.io.IOException;
 import java.util.concurrent.PriorityBlockingQueue;
@@ -39,22 +38,22 @@ final class EPFramework
     {
         Chunk.setHeaderLines(config.getNumHeaderLines());
 
-        Manipulator manip = null;
+        ChunkManager cm = null;
         try
         {
             if (config.getInputFile() == null)
             {
                 // Make a chunk for each presplit file
-                manip = new Manipulator(config.getNumHeaderLines());
-                manip.splitFiles(config.getInputDirectory());
+                cm = new ChunkManager(config.getNumHeaderLines());
+                cm.splitFiles(config.getInputDirectory());
             }
             else
             {
                 // Read in the input file and get the chunks
-                manip = new Manipulator(config.getSplitPattern(), 
+                cm = new ChunkManager(config.getSplitPattern(), 
                         config.getNumHeaderLines());
 
-                manip.split(config.getInputFile());
+                cm.split(config.getInputFile());
             }
         }
         catch (IOException e)
@@ -63,8 +62,8 @@ final class EPFramework
             return;
         }
 
-        // Get the chunks made my the manipulator
-        final PriorityBlockingQueue<Chunk> chunks = manip.getChunks();
+        // Get the chunks made my the chunkmanager
+        final PriorityBlockingQueue<Chunk> chunks = cm.getChunks();
         if (chunks.size() == 0)
         {
             LOG.fatal("Incorrect chunk pattern or empty input file");
@@ -76,15 +75,15 @@ final class EPFramework
         wp.start();
 
         // Merge the results back together
-        manip.merge(config.getOutputDirectory() + "/done.txt", 
+        cm.merge(config.getOutputDirectory() + "/done.txt", 
             config.getMergeMethod());
 
         // Make stats if instructed to 
         if (config.makeStats())
         {
-            manip.printStats(wp.getStats(), config.getOutputDirectory());
+            cm.printStats(wp.getStats(), config.getOutputDirectory());
         }
-        manip.cleanUp();
+        cm.cleanUp();
     }
 
     /**

### 2013-11-20 src/main/java/edu/unh/schwartz/epframework/io/package-info.java

@@ -1,5 +1,0 @@
-/**
- * Provides classes that deal with file I/O of the chunks of work: spliting,
- * merging, etc.
- */
-package edu.unh.schwartz.epframework.io;

### 2013-11-21 paper/paper.tex
Wills paper revisions

@@
 An embarrassingly parallel problem, also called pleasingly parallel, is one that 
-can easily be broken up into identital components that do not need to interact 
+can be easily broken up into identital components that do not need to interact 
 to find the solution. Several problems in the biological sciences are 
@@
 framework, implemented in Java, that will execute the serial program in several 
-threads. These threads working together help cut down the total runtime
-exponentially. The next step is to seperate the framework into a front-end that
-will run locally and the back-end which recieves blocks of work and does the
-computations. This back-end should be running in the cloud, on a machine who is
-dedicated to running embarrassingly parallel tasks only.
+threads. These threads working together help cut down the total runtime of the
+program exponentially. The next step is to seperate the framework into a 
+front-end that will run locally and a back-end which recieves blocks of work and 
+does the computations. This back-end should run in the cloud, on a machine that 
+is dedicated to running embarrassingly parallel tasks only.
 \end{abstract}
@@
 
-A computation graph consists of nodes that represent the functions or processes 
-and the data being passed from one process to another is displayed in the graph 
-as edges. If the graph is disconnected, none of the processes need to 
-communicate to complete the computations. Such a computation is called
-"embarrassingly parallel." In a practical situation, there will be some 
-internode communication to set up the problem and then again to accumulate the 
-results back together. Also known as pleasingly parallel problems, they can 
-easily be performed on a cluster of servers or in any kind of distributed 
-network, due to its lack of dependencies. The term embarrassingly parallel was 
-coined by Cleve Moler in his 1986 paper "Matrix Computation on Distributed
-Memory Multiprocessors." \cite{history}
+A computation graph consists of nodes that represent the functions or processes. 
+The edges of the graph show data being passed from one process to another. If 
+the graph is disconnected, none of the processes need to communicate to complete
+the computations. Such a computation is called "embarrassingly parallel." In a 
+practical situation, there will be some internode communication to set up the 
+problem, and then again to accumulate the results. Embarrassingly parallel 
+problems can be easily performed on a cluster of servers or in any kind of 
+distributed network, due to its lack of dependencies. The term embarrassingly 
+parallel was coined by Cleve Moler in his 1986 paper "Matrix Computation on 
+Distributed Memory Multiprocessors." \cite{history}
 
 Programs in the field of Biology and Genetics often analyze long strings of
-characters, whether they are DNA, RNA or protein sequences. In addition to the
-large file sizes, there is a lot of processing that goes into comparing and
-manipulating strings. This time adds up when there are thousands of strings to 
-process. However, these sequences often do not relate to each other and can be 
-processed independently. Using an embarrassingly parallel approach, the 
+characters, whether they are DNA, RNA or protein sequences. In addition to
+handling large file sizes, there is a lot of processing that goes into comparing
+and manipulating strings. This time adds up when there are thousands of strings 
+to process. However, these sequences often do not relate to each other and can 
+be processed independently. Using an embarrassingly parallel approach, the 
 processing time for all of the sequences can often be cut down exponentially 
@@
 
-The motivation for this effort was with research into different forms of the 
+The motivation for this effort was research into different forms of the 
 species \emph{Cicer arietinum}, the chickpea. The two main forms, Kabuli and 
-Desi, are very different in size and color but we mostly wanted to see why the 
-Desi is more disease resistance and have more effective root nodule symbiosis 
-and why the Kabuli has a large but soft shell. These two types are both 
-cultivated and have been under human selection for several thousand years. We 
-wanted to use a Ka/Ks equation to quantify the evolution and selection of these 
-chickpeas. We found a Ka/Ks program writen by Zhang et al. \cite{kaks} but had 
-three variants that we wanted to be analyzed, each with thousands of sequences. 
-The Ka/Ks Calculator program takes somewhere from five to thirty seconds to 
-process one pair of sequences.
+Desi, are very different in size and color. The Desi is also more resistant to 
+diseases and are more effective at root nodule symbiosis. The Kabuli has a large 
+but soft shell, which make it at better food source for humans. These two types 
+are both cultivated and have been under human selection for several thousand 
+years. We wanted to use a Ka/Ks equation to quantify the evolution and selection 
+of these chickpeas. We found a Ka/Ks program written by Zhang et al. \cite{kaks}
+but had three variants that we wanted to analyze, each with thousands of 
+sequences. The Ka/Ks Calculator program takes somewhere from five to thirty 
+seconds to process one pair of sequences.
 
@@
 bugs, breaking the algorithm, dealing with the learning curve of C++ threading. 
-We decided a  different approach was neccessary, mostly due to the short time we
-had to produce results. A simple Java program was written to break up the input 
-and spawn  threads that would run the Ka/Ks Calculator process. When the input 
-was calculated, the contents of the output files was concatenated together to 
-produce a final output that mnatches the format and order that would have been
-produces by Ka/Ks Calculator.
+We decided that a  different approach was neccessary, mostly due to the short 
+time given to produce results. A simple Java program was written to break up the
+input and spawn threads that would run the Ka/Ks Calculator process. When the 
+input was calculated, the contents of the output files were concatenated 
+together to produce a final output that matches the format and order that would 
+have been produced by the Ka/Ks Calculator program.
 
@@
 process the input in an embarrassingly parallel manner and that the input comes 
-from a file. The processed results are must also written to a file. The 
-framework supports two forms of input: a directory of files that contain that 
-each contain one unit of work, which is represented by the Chunk class, or a 
-single file that the framework can break up into Chunks. For example, the Ka/Ks 
-Calculator's input consists of a header and then two protein sequence lines 
-followed by a blank line. The framework uses that blank line to know when one 
-Chunk of work has ended and another has begun. The user can input a regular 
-expression to define when lines of input are seperated into Chunks. This occurs 
-in the ChunkManager class.
+from a file. The processed results must also written to a file. The framework 
+supports two forms of input: a directory of files that contain that each contain
+one unit of work, which is represented by the Chunk class, or a single file that
+the framework can break up into Chunks. For example, the Ka/Ks Calculator's 
+input consists of a header and then two protein sequence lines followed by a 
+blank line. The framework uses that blank line to know when one Chunk of work 
+has ended and another has begun. The user can input a regular expression to 
+define when lines of input are seperated into Chunks. This occurs in the 
+ChunkManager class.
 
@@
 back together when the worker threads have finished. Once the work has been
-done, all of the separate results are spread across several files. The
-ChunkManager's second job is to retrieve those results and construct a real
-output file. The real output file must look the same as the output file would
-look if the program were run serially; the output must come in the same order as
-the inputs in the input file and headers may need to be deleted from the
-separate files and added to the combined file. There are two other options if
-the end-user does not want this behavior. They can choose to write their own
-merger in Java, using the CustomMerge class, or write their own script to do the
-merging.
+done, all of the separate results are spread across several files. Those results 
+must be retrieved and combined to construct the final output file. This output 
+file must look the same as the output file would look if the program were run 
+serially; the output must come in the same order as the inputs in the input file
+and headers may need to be deleted from the separate files and added to the 
+combined file. There are two other options if the end-user does not want this 
+behavior. They can choose to write their own merger in Java, using the 
+CustomMerge class, or write their own script to do the merging.
 
@@
 
-To observe how the framework changes the runtime of sequential programs when
-using varying numbers of threads, we designed a simple experiment. The Ka/Ks 
-Calculator was run through the framework with ten different samples, each 
+In order to observe how the framework changes the runtime of sequential programs 
+when using varying numbers of threads, we designed a simple experiment. The 
+Ka/Ks Calculator was run through the framework with ten different samples, each 
 containing sixteen units of work. Each sample was run by the framework at five 
@@
 
-As the numbers of threads increased, the time it took descreased exponentially. 
-In a few cases, there was an increase in time when attempting to max out the CPU 
-usage. This occured because the framework had to wait until for the CPU to be 
-finished with its previous work before it was allowed to start work on what the 
-framework wanted it to do. In the cases when the framework executed faster while
-the CPU was maxed out, it was only faster a minute at the most. With such a
-small time gain with the CPU at 50\% versus the CPU at 100\%, running the
-framework at 50\% CPU is more efficient when the number of threads is on the
-same order as the number of units of work.
+As the numbers of threads increased, the runtime of the program descreased 
+exponentially. In a few cases, there was an increase in time when attempting to 
+max out the CPU usage. This occured because the framework had to wait for the 
+CPU to be finished with its previous work before it was allowed to start any 
+further jobs. In the cases when the framework executed faster while the CPU was 
+maxed out, it was only faster a minute at the most. However, running the 
+framework at 50\% of the CPU is more efficient than running using 100\% of the 
+CPU. The runtime drop achieved when using 100\% of the CPU versus 50\% is not 
+large enough to warrant using all of the machine's power.
 
-%TODO: Rewrite with new next steps
-There are several next steps in the pipeline. In addition to using the
-statistics to try to boost speed, adding savable configurations is at the top of
-the list. This will allow users to use the same configuration without having to
-go through the wizard if they need to redo a run. More extensive unit testing
-will be implemented. The ability to chunk multiple pieces of work may be
-implemented in order to avoid potential start up costs in the executable. 
-Finally, other pleasing parallel problems will be executed by the wrapper so 
-that more potential features will be discovered.
-
-%TODO: Does this still make sense
 Using Java was a good choice for implementation ease and future implementation
 extension by others, but it may not produce the fastest results. Languages
-like Hadoop, Clojure or other multithread oriented language may have been better
-due to their parallel nature. In addition to a single machine working to process
-the data quickly, we can also look to the cloud for help by using a networked 
-solution like MPI or a cloud solution like Amazon instances. This would
-potentially allow for an even greater time decrease because the number of
-machines that could help is most likely larger than the number of processors on
-one machine.
+like Hadoop, Clojure or other multithread oriented language may have been a
+better choice due to their parallel nature. In addition to a single machine 
+working to process the data quickly, we can also look to the cloud for help by 
+using a networked solution like MPI or a cloud solution like Amazon instances. 
+In the future, we would like to see this work be split into a local front-end
+and a cloud back-end. This would potentially allow for an even greater time 
+decrease because the number of machines that could help is much larger than the 
+number of processors on one machine. Spliting the framework would also allow for
+better testing of cloud environments, where the cloud environment itself could
+be a configurable option for end users.
 

### 2013-11-24 paper/paper.tex
Spell check and more readme stuff

@@
 An embarrassingly parallel problem, also called pleasingly parallel, is one that 
-can be easily broken up into identital components that do not need to interact 
+can be easily broken up into identical components that do not need to interact 
 to find the solution. Several problems in the biological sciences are 
-embarrsingly parallel but they are difficult to rewrite to use multithreading, 
+embarrassingly parallel but they are difficult to rewrite to use multithreading, 
 because they are either poorly written or too complex. We have written a 
@@
 threads. These threads working together help cut down the total runtime of the
-program exponentially. The next step is to seperate the framework into a 
-front-end that will run locally and a back-end which recieves blocks of work and 
+program exponentially. The next step is to separate the framework into a 
+front-end that will run locally and a back-end which receives blocks of work and 
 does the computations. This back-end should run in the cloud, on a machine that 
@@
 the computations. Such a computation is called "embarrassingly parallel." In a 
-practical situation, there will be some internode communication to set up the 
+practical situation, there will be some inter-node communication to set up the 
 problem, and then again to accumulate the results. Embarrassingly parallel 
@@
 bugs, breaking the algorithm, dealing with the learning curve of C++ threading. 
-We decided that a  different approach was neccessary, mostly due to the short 
+We decided that a  different approach was necessary, mostly due to the short 
 time given to produce results. A simple Java program was written to break up the
@@
 amounts of data, the best method is often to group them into clusters. 
-Hierarchical clustering algorthms take the data and then organize into
-hierarchical structure, usually a dendrogram, based on a priority matric. There 
+Hierarchical clustering algorithms take the data and then organize into
+hierarchical structure, usually a dendrogram, based on a priority matrix. There 
 are hierarchical clustering algorithms that can be implemented in parallel using
@@
 
-%TODO: TALK ABOUT CLOUD PAPER HERE. AND MAYBE THE POWERPOINT TOO.
+%TODO: TALK ABOUT CLOUD PAPER HERE.
+Segue. Gunarathne et al.\cite{cloud} have investigated running much larger
+embarrassingly parallel biological problems using various cloud services. These
+services offer on-demand computational power with MORE.
+These services also have built in hooks to various distributed services, such as
+storage and databases. One of these technologies is the MapReduce framework,
+which allows user to perform distributed computation similar to this framework.
+As seen in figure X, Apache Hadoop, an open-source implementation of MapReduce,
+breaks down the input data into parts, runs them in parallel with the 'Map'
+function and then combines the results with the 'Reduce' function. TWO MORE
+SENTENCES.
 
@@
 has ended and another has begun. The user can input a regular expression to 
-define when lines of input are seperated into Chunks. This occurs in the 
+define when lines of input are separated into Chunks. This occurs in the 
 ChunkManager class.
@@
 how they want their program to execute. The number of threads to use, various 
-flags for the executable and the statstics output are just a few choice the 
+flags for the executable and the statistics output are just a few choice the 
 user can make. A start-up wizard is displayed at runtime to systematically allow
@@
 type of input data. The statistics for each thread can be found in the Worker 
-subclass and the individual Chunk objects will store their own statstics about 
+subclass and the individual Chunk objects will store their own statistics about 
 runtime and size.
@@
 
-As the numbers of threads increased, the runtime of the program descreased 
+As the numbers of threads increased, the runtime of the program decreased 
 exponentially. In a few cases, there was an increase in time when attempting to 
-max out the CPU usage. This occured because the framework had to wait for the 
+max out the CPU usage. This occurred because the framework had to wait for the 
 CPU to be finished with its previous work before it was allowed to start any 
@@
 using a networked solution like MPI or a cloud solution like Amazon instances. 
-In the future, we would like to see this work be split into a local front-end
-and a cloud back-end. This would potentially allow for an even greater time 
-decrease because the number of machines that could help is much larger than the 
-number of processors on one machine. Spliting the framework would also allow for
-better testing of cloud environments, where the cloud environment itself could
-be a configurable option for end users.
+The MapReduce framework works similarly to our framework, there is a step that
+splits the data, the Map function is the user's executable and the merge step is
+the Reduce function in the framework. In the future, we would like to see this 
+work be split into a local front-end and a cloud back-end. This allows for an 
+even greater runtime decrease because the number of compute nodes available is 
+larger than the number of processors on most machines. Splitting the framework 
+also allows for better testing of cloud environments, where the cloud 
+environment itself could be a configurable option for end users.
 
@@
 IEEE Transactions on Neural Networks VOL. 16, NO. 3, MAY 2005
+\bibitem{cloud}
+Crap, crap and Crap
 \end{thebibliography}

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/EPFramework.java
Jar build changes

@@ -117,7 +117,7 @@ final class EPFramework
             catch (IOException e)
             {
 
-                LOG.fatal("Problem loading config file: " + e.getMessage());
+                LOG.fatal("Invalid Configuration File");
             }
         }
         else

### 2013-11-24 paper/paper.tex
Coding work, log messages, config saving doesnt work still

@@
 the user through this process and creates an instance of Configuration when it 
-is completed to save the user's settings.
+is completed to save the user's settings, allowing the user to rerun with the
+same settings without having to go through the ConfigWizard.
 

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/ChunkManager.java

@@ -180,13 +180,14 @@ public final class ChunkManager
                 externalMerge(fileName);
                 break;
             default:
-                LOG.fatal("Illegal mergeMethod");
+                LOG.fatal("Illegal Merge Method");
                 assert(false);
         }
     }
 
     private void defaultMerge(final String fileName)
     {
+        LOG.info("Using Default Merge");
         try(final PrintWriter writer = new PrintWriter(fileName))
         {
             writer.print(this.chunks.get(0).getHeader());
@@ -204,11 +205,14 @@ public final class ChunkManager
 
     private void customMerge(final String fileName)
     {
+        LOG.info("Using Custom Merge");
         CustomMerge.merge(fileName, this.chunks);
     }
 
     private void externalMerge(final String fileName) 
     {
+        LOG.info("Using External Merge");
+
         // Prepare the args
         final List<String> commands = new ArrayList<String>();
         commands.add(EXTERNAL_MERGE_EXEC_NAME);
@@ -260,7 +264,7 @@ public final class ChunkManager
         {
             final String comma = ",";
             final String header = "Chunk #,Length,Runtime(ms)";
-            statsOut.println(workerStats);
+            statsOut.print(workerStats);
             LOG.debug(workerStats);
 
             statsOut.println(header);
@@ -270,7 +274,7 @@ public final class ChunkManager
                 final Chunk c = this.chunks.get(i);
                 final StringBuilder sb = new StringBuilder();
                 sb.append(c.hashCode()).append(comma).append(c.length());
-                sb.append(comma).append(c.getRuntime()).append('\n');
+                sb.append(comma).append(c.getRuntime());
                 statsOut.println(sb.toString());
                 LOG.debug(sb.toString());
             }

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/EPFramework.java

@@ -75,14 +75,16 @@ final class EPFramework
         wp.start();
 
         // Merge the results back together
-        cm.merge(config.getOutputDirectory() + "/done.txt", 
+        cm.merge(config.getOutputDirectory() + "/finalOutput", 
             config.getMergeMethod());
 
         // Make stats if instructed to 
         if (config.makeStats())
         {
+            LOG.info("Printing stats");
             cm.printStats(wp.getStats(), config.getOutputDirectory());
         }
+        LOG.info("Cleaning up");
         cm.cleanUp();
     }
 

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java

@@ -61,7 +61,7 @@ public final class ConfigWizard
 
         window.setDefaultCloseOperation(JDialog.DISPOSE_ON_CLOSE);
         window.getContentPane().add(wc);
-        window.setSize(375, 250);
+        window.setSize(380, 290);
         window.setLocationRelativeTo(null);
     }
 
@@ -192,7 +192,7 @@ public final class ConfigWizard
             add(splitField);
             add(new JLabel("(Leave blank to use every new line)"));
 
-            add((new JLabel("--------------- OR ---------------")));
+            add((new JLabel("               ------ OR ------               ")));
 
             // Settings for the input directory
             final JFileChooserButton inDirChooser = new JFileChooserButton(true);
@@ -278,6 +278,12 @@ public final class ConfigWizard
             headerField.setPreferredSize(new Dimension(50, 20));
             add(new JLabel("Number of header lines in output files: "));
             add(headerField);
+            add(new JLabel(SEP));
+ 
+            final JCheckBox savebox = new JCheckBox();
+            savebox.setName(Configuration.SAVE_KEY);
+            add(new JLabel("Save Configuration File?"));
+            add(savebox);
         }
     }
 
@@ -287,11 +293,7 @@ public final class ConfigWizard
         {
             super("Confirmation", "Confirmation Page");
 
-            final JCheckBox box = new JCheckBox();
-            box.setName(Configuration.SAVE_KEY);
-            add(new JLabel("Save Configuration File?"));
-            add(box);
-            // add(new JLabel(SEP));
+            add(new JLabel("TODO"));
 
             //TODO: Review entered values
             // add(new JLabel("Confirm String:"));

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -140,6 +140,11 @@ public final class Configuration
      * The method used to merge the results.
      */
     private int mergeMethod;
+
+    /**
+     * Whether or not to save the config file.
+     */
+    private boolean save;
     
     /**
      * Constructs a configuration file from a map.
@@ -186,10 +191,7 @@ public final class Configuration
                      this.numberOfHeaderLines = Integer.valueOf((String) val);
                      break;
                  case SAVE_KEY:
-                     if ((boolean) val)
-                     {
-                         saveConfig();
-                     }
+                     this.save = (boolean) val;
                      break;
                  case MERGE_METHOD_KEY:
                      this.mergeMethod = Integer.valueOf((String) val);
@@ -199,7 +201,32 @@ public final class Configuration
              }
          }
 
-         // TODO: Assertions here
+         // Check to make sure necessary fields were filled
+         boolean crash = false;
+         if (this.inputFileDirName == null && this.inputFileName == null)
+         {
+             LOG.fatal("An input file or directory must be selected");
+             crash = true;
+         }
+         else if (this.outDirName == null)
+         {
+             LOG.fatal("An output directory must be selected");
+             crash = true;
+         }
+         else if (this.execPath == null)
+         {
+             crash = true;
+             LOG.fatal("An executable must be selected");
+         }
+
+         if (crash)
+         {
+             System.exit(1);
+         }
+         else if (this.save)
+         {
+             saveConfig();
+         }
     }
 
     /**
@@ -383,6 +410,7 @@ public final class Configuration
         final JsonFactory jsonFactory = new JsonFactory(); 
         try
         {
+            LOG.info("Saving configuration in " + this.outDirName);
             final File file = new File(this.outDirName + "/config.txt");
             final JsonGenerator jg = jsonFactory.createGenerator(file, 
                     JsonEncoding.UTF8);
@@ -396,6 +424,7 @@ public final class Configuration
                 jg.writeStringField(IN_FILE_DIR_KEY, this.inputFileDirName);
             }
 
+            LOG.info("Made it");
             jg.writeStringField(OUT_FILE_KEY, this.outDirName);
             jg.writeStringField(EXEC_LOC_KEY, this.execPath);
             jg.writeStringField(IN_FLAG_KEY, this.inFlag);
@@ -404,6 +433,7 @@ public final class Configuration
             jg.writeBooleanField(STATS_KEY, this.makeStats);
[…]

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -120,15 +120,15 @@ public final class Worker extends Thread
                 pb.redirectErrorStream(true);
 
                 // Start the work and capture the time it takes to run
-                LOG.info("Starting chunk on thread " + this.idNum);
+                LOG.info("Starting chunk on Worker " + this.idNum);
                 final long start = System.currentTimeMillis();
                 final Process proc = pb.start();
                 proc.waitFor();
                 final long end = System.currentTimeMillis();
                 c.setRuntime(end - start);
                 runTime += (end - start);
-                LOG.info("Finished chunk " + c.hashCode() + " on thread " + 
-                        this.idNum + " in " + (end - start));
+                LOG.info("Finished chunk on Worker " + this.idNum + " in " + 
+                        (end - start));
             }
             catch (InterruptedException|IOException e)
             {
@@ -137,6 +137,7 @@ public final class Worker extends Thread
 
             this.chunksRun++;
         }
+        LOG.info("Worker " + this.idNum + " has finished");
     }
     
     /**

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/worker/WorkerPool.java

@@ -65,6 +65,8 @@ public final class WorkerPool
             LOG.fatal("Worker interrupted: " + e.getMessage());
             System.exit(1);
         }
+
+        LOG.info("Workers finished");
     }
 
     /**

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/EPFramework.java
Configurations save and load

@@ -75,7 +75,7 @@ final class EPFramework
         wp.start();
 
         // Merge the results back together
-        cm.merge(config.getOutputDirectory() + "/finalOutput", 
+        cm.merge(config.getOutputDirectory() + "/output", 
             config.getMergeMethod());
 
         // Make stats if instructed to 

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -240,6 +240,7 @@ public final class Configuration
     {
         final JsonFactory jf = new JsonFactory();
         final JsonParser jp = jf.createParser(new File(fileName));
+        jp.nextToken();
 
         while (jp.nextToken() != JsonToken.END_OBJECT)
         {
@@ -414,6 +415,7 @@ public final class Configuration
             final File file = new File(this.outDirName + "/config.txt");
             final JsonGenerator jg = jsonFactory.createGenerator(file, 
                     JsonEncoding.UTF8);
+            jg.writeStartObject();
             if (this.inputFileName != null)
             {
                 jg.writeStringField(IN_FILE_KEY, this.inputFileName);
@@ -424,7 +426,6 @@ public final class Configuration
                 jg.writeStringField(IN_FILE_DIR_KEY, this.inputFileDirName);
             }
 
-            LOG.info("Made it");
             jg.writeStringField(OUT_FILE_KEY, this.outDirName);
             jg.writeStringField(EXEC_LOC_KEY, this.execPath);
             jg.writeStringField(IN_FLAG_KEY, this.inFlag);
@@ -432,6 +433,7 @@ public final class Configuration
             jg.writeNumberField(NUM_PROCESSES_KEY, this.numberOfThreads);
             jg.writeBooleanField(STATS_KEY, this.makeStats);
             jg.writeNumberField(NUM_HEADER_KEY, this.numberOfHeaderLines);
+            jg.writeEndObject();
             jg.close();
             LOG.info("Configuration saved");
         }

### 2013-11-24 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java
Working on confirmation area, leving Kingsbury

@@ -6,6 +6,7 @@ import java.util.List;
 import javax.swing.JCheckBox;
 import javax.swing.JDialog;
 import javax.swing.JLabel;
+import javax.swing.JScrollPane;
 import javax.swing.JTextField;
 import org.apache.commons.logging.Log;
 import org.apache.commons.logging.LogFactory;
@@ -34,7 +35,7 @@ public final class ConfigWizard
     /**
      * Seperator string.
      */
-    private static final String SEP = "---------------------------------------"; 
+    private static final String SEP = "======================================="; 
 
     /**
      * The last configuration created.
@@ -191,8 +192,7 @@ public final class ConfigWizard
             add(new JLabel("Pattern used to split input: "));
             add(splitField);
             add(new JLabel("(Leave blank to use every new line)"));
-
-            add((new JLabel("               ------ OR ------               ")));
+            add((new JLabel("               ====== OR ======               ")));
 
             // Settings for the input directory
             final JFileChooserButton inDirChooser = new JFileChooserButton(true);
@@ -293,18 +293,21 @@ public final class ConfigWizard
         {
             super("Confirmation", "Confirmation Page");
 
-            add(new JLabel("TODO"));
-
-            //TODO: Review entered values
-            // add(new JLabel("Confirm String:"));
-            // for(String key : settings.keySet())
-            // {
-                // Object val = settings.get(key);
-                // if (val != null && !val.equals(""))
-                // {
-                    // add(new JLabel(key + " : " + val + "\n"));
-                // }
-            // }
+            add(new JLabel("Configuration Settings:"));
+            
+            // Get the settings
+            final JTextArea label = new JTextArea(5, 20);
+            for(final String key : settings.keySet())
+            {
+                final Object val = settings.get(key);
+                if (val != null && !val.equals(""))
+                {
+                    label.append(key).append(": ").append(val).append("\n");
+                }
+            }
+            label.setEditable(false);
+            
+            add(new JScrollPane(label));
         }
 
         /**

### 2013-11-25 paper/paper.tex
Beginning of Dan's paper revisions

--- 2013-11-24 paper/paper.tex
@@
 The edges of the graph show data being passed from one process to another. If
-the graph is disconnected, none of the processes need to communicate to complete
-the computations. Such a computation is called "embarrassingly parallel." In a 
-practical situation, there will be some inter-node communication to set up the 
+the graph is fully disconnected, none of the processes need to communicate to
+complete the computations. Such a computation is called embarrassingly
+parallel.\footnote{The term embarrassingly parallel was coined by Cleve Moler in
+his 1986 paper ``Matrix Computation on Distributed Memory Multiprocessors.''} In
+a practical situation, there will be some inter-node communication to set up the
 problem, and then again to accumulate the results.  Embarrassingly parallel
 problems can be easily performed on a cluster of servers or in any kind of
-distributed network, due to its lack of dependencies. The term embarrassingly 
-parallel was coined by Cleve Moler in his 1986 paper "Matrix Computation on 
-Distributed Memory Multiprocessors." \cite{history}
+distributed network, due to its lack of dependencies.
 
@@
 handling large file sizes, there is a lot of processing that goes into comparing
-and manipulating strings. This time adds up when there are thousands of strings 
-to process. However, these sequences often do not relate to each other and can 
-be processed independently. Using an embarrassingly parallel approach, the 
-processing time for all of the sequences can often be cut down exponentially 
-with very minimal effort by the programmer.
+and manipulating strings. This time adds up when there are hundreds of thousands
+of strings to process. However, these sequences often do not relate to each
+other and can be processed independently. Using an embarrassingly parallel
+approach, the processing time for all of the sequences can often be cut down
+exponentially with very minimal effort by the programmer.
 
-The framework provides a "wrapper" for the original program that mimics the
+This paper describes a framework that makes it easy to parallelize a potentially
+embarrassingly parallel program that reads from a file, writes to a file and
+whose input can be broken up into work units in an easily identifiable manner.
+The framework provides a ``wrapper'' for the original program that mimics the
 behavior of the original program. It calls the serial programs on multiple Java
-threads. Each thread acts like the serial application, reading a subset of the 
-input the same and creating the output in the same format. This paper describes
-a framework that makes it easy to parallelize an potentially embarrassingly
-parallel program that reads from a file, writes to a file and whose input can be
-broken up into work units by a regular expression. The framework gives an
-exponential decrease in runtime as more processor help in the computation. This
-decrease levels off between 50 and 100\% CPU usage due to the other tasks on the
-machine that take up memory.
+threads, such that each thread acts like the serial application, reading a
+subset of the input in the same manner and creating the output in the same
+format. The framework can result in a significant exponential decrease with very
+little programmer effort.
 
@@
 
-The motivation for this effort was research into different forms of the 
+TODO: Arrows?
+The motivation for this effort was based on research into different forms of the
 species \emph{Cicer arietinum}, the chickpea. The two main forms, Kabuli and
@@
 diseases and are more effective at root nodule symbiosis. The Kabuli has a large
-but soft shell, which make it at better food source for humans. These two types 
-are both cultivated and have been under human selection for several thousand 
-years. We wanted to use a Ka/Ks equation to quantify the evolution and selection 
-of these chickpeas. We found a Ka/Ks program written by Zhang et al. \cite{kaks}
-but had three variants that we wanted to analyze, each with thousands of 
-sequences. The Ka/Ks Calculator program takes somewhere from five to thirty 
-seconds to process one pair of sequences.
+but soft shell, which make it at better food source for humans. Both forms are
+cultivated and have been under human selection for several thousand years. We
+wanted to use an existing Ka/Ks program (Zhang et al. \cite{kaks}) to quantify
+the evolution and selection of these chickpeas. We needed to analyze three
+variants, each with thousands of sequences. The Ka/Ks Calculator program took
+between five to thirty seconds to process one pair of sequences on a commodity
+desktop.
 
-Instead of attempting to rewrite the preexisting program, we decided it would be
-better to look at other options to process the sequences faster. Trying to 
-parallelize the serial Ka/Ks program could present several problems: introducing
-bugs, breaking the algorithm, dealing with the learning curve of C++ threading. 
-We decided that a  different approach was necessary, mostly due to the short 
-time given to produce results. A simple Java program was written to break up the
-input and spawn threads that would run the Ka/Ks Calculator process. When the 
-input was calculated, the contents of the output files were concatenated 
-together to produce a final output that matches the format and order that would 
-have been produced by the Ka/Ks Calculator program.
+At this rate, we predicted it would take ten days of constant computation to
+complete the processing we needed. We neither had the time nor the expertise to
+develop a new parallel Ka/Ks program. We were also reluctant to revise the
+existing code to to implement the parallel computation because of the danger of
+introducing bugs into unfamiliar code and because of the learning curve required
+for C++ threading. Instead we wrote, a simple Java program to break up the input
+and spawn threads that would run the Ka/Ks Calculator process without having to
+make any changes to the code. When al of the threads ended, the contents of the
+output files were concatenated together to produce a final output that matches
+the format and order that would have been produced by a single invocation of the
+Ka/Ks Calculator program.
 
 %TODO: get a better source? Talk about UCLUST and octupus
-The Ka/Ks Calculator is not the only embarrassingly parallel program that has the
+Ka/Ks Calculator is not the only embarrassingly parallel program that has the
 potential to take several days to run on a data set. In fact, there are several
@@
 benefit from parallelism in this field, it was obvious it would be desirable to
-develop a framework for creating wrapper programs. \cite{cluster}
+develop a framework for the  parallelization task. \cite{cluster}
 
@@
 file must look the same as the output file would look if the program were run
-serially; the output must come in the same order as the inputs in the input file
-and headers may need to be deleted from the separate files and added to the 
-combined file. There are two other options if the end-user does not want this 
-behavior. They can choose to write their own merger in Java, using the 
-CustomMerge class, or write their own script to do the merging.
+serially; the output may need to come in the same order as the inputs in the
+input file and headers may need to be deleted from the separate files and added
+to the combined file. End-users can also choose to write their own merge code in
+Java, using the CustomMerge class, or write their own independent merge script.
 
-As more features are added to the framework and as more programs start to use 
-the framework, there are more choices for the end-user to make with regards to 
-how they want their program to execute. The number of threads to use, various 
-flags for the executable and the statistics output are just a few choice the 
-user can make. A start-up wizard is displayed at runtime to systematically allow
-the end-user to choose the settings for the run. The ConfigWizard class brings 
-the user through this process and creates an instance of Configuration when it 
-is completed to save the user's settings.
+The end-user can control many aspects of the parallelization of the code,
+including the number of threads to use, various flags for the executable and the
+statistics output.  A start-up wizard allows the end-user to choose the settings
+for the run and creates an instance of Configuration when it is completed to
+save the user's settings, allowing the user to rerun with the same settings
+without having to go through the wizard again.
 
-Lastly, the worker threads will keep records during execution. The threads 
-records their uptime and the number of pieces of work they execute. The runtime 
-for each piece of work is also recorded. This information will be used by us to
-evaluate the effectiveness of our approach, but can also provide useful
-information the can help a user tine a particular application on a particular
-type of input data. The statistics for each thread can be found in the Worker 
-subclass and the individual Chunk objects will store their own statistics about 
-runtime and size.
+Lastly, the worker threads keep records during execution. The threads record
+their total uptime and the number of Chunks they execute, and the runtime for
+each piece of work. This information will be used to evaluate the effectiveness
+of the approach, but can also provide useful information the can help a user
+tine a particular application on a particular type of input data. The statistics
+for each thread can be found in the Worker subclass and the individual Chunk
+objects will store their own statistics about runtime and size.
 
@@
 
-In order to observe how the framework changes the runtime of sequential programs 
-when using varying numbers of threads, we designed a simple experiment. The 
+We evaluated the convenience and performace of the framework on two different
+applications: the Ka/Ks Calculator and two different sequence clustering
+algorithms. In all cases, we compared the framework based application with the
+original using different data partitions and different thread counts.
+
+\subsection{Ka/Ks Calculator}
 Ka/Ks Calculator was run through the framework with ten different samples, each 
-containing sixteen units of work. Each sample was run by the framework at five 
-different level of numbers of worker threads, starting at 1 and increasing by 
-powers of two until the 100\% CPU usage (16 processors). These tests were run
+containing sixteen units of work. Each sample was run by the framework thread
+counts, starting at 1 and increasing by 
+powers of two until the 100\% processor usage (16 processors). These tests were run
 with minimal other activity on the server.
@@
 
-\section{Conclusion}
+Figure 2 summarized the results; each line shows the time taken for each chunk
+of the data.
+As the numbers of threads increases, the runtime of the program decreases 
+exponentially. In a few cases, there was an increase in time when attempting to 
+max out the CPU usage. This occurs because the framework has to wait for the 
+CPU to be finished with its previous work before it can start any 
+further jobs.
 
-As the numbers of threads increased, the runtime of the program decreased 
-exponentially. In a few cases, there was an increase in time when attempting to 
-max out the CPU usage. This occurred because the framework had to wait for the 
-CPU to be finished with its previous work before it was allowed to start any 
-further jobs. In the cases when the framework executed faster while the CPU was 
+TODO(Keep?): In the cases when the framework executed faster while the CPU was 
 maxed out, it was only faster a minute at the most. However, running the 
@@
 
+\subsection{uClust}
+
+Place holder text
+
+\subsection{Octupus}
+
+Place holder text
+
+\section{Conclusion}
+
+TODO: First paragrpah should summarize performce: its clear that framework
+provices simple and effective module for adding parallelism to a class of
+file-oriented EP apps. More self praise.
+
 Using Java was a good choice for implementation ease and future implementation
-extension by others, but it may not produce the fastest results. Languages
-like Hadoop, Clojure or other multithread oriented language may have been a
-better choice due to their parallel nature. In addition to a single machine 
-working to process the data quickly, we can also look to the cloud for help by 
-using a networked solution like MPI or a cloud solution like Amazon instances. 
-The MapReduce framework works similarly to our framework, there is a step that
-splits the data, the Map function is the user's executable and the merge step is
-the Reduce function in the framework. In the future, we would like to see this 
-work be split into a local front-end and a cloud back-end. This allows for an 
-even greater runtime decrease because the number of compute nodes available is 
-larger than the number of processors on most machines. Splitting the framework 
-also allows for better testing of cloud environments, where the cloud 
-environment itself could be a configurable option for end users.
+extension by others, but it may not produce the fastest results. Languages like
+Hadoop, Clojure or other multithread oriented language may have been a better
+choice due to their inherit parallel nature. In addition to a single machine
+working to process the data quickly, we can also look at distributed solutions
+by using MPI or a cloud solution like Amazon instances. The MapReduce framework
+works similarly to our framework, there is a step that splits the data, the Map
+function is the user's executable and the merge step is the Reduce function in
+the framework.
+
+In the future, we would like to see this work be split into a
+local front-end and a cloud back-end. This allows for an even greater runtime
+decrease because the number of compute nodes available is larger than the number
+of processors on most machines. Splitting the framework also allows for better
+testing of cloud environments, where the cloud environment itself could be a
+configurable option for end users.
+TODO: MORE
 

### 2013-11-26 paper/paper.tex
More paper revisions

@@
 can be easily broken up into identical components that do not need to interact
-to find the solution. Several problems in the biological sciences are
-embarrassingly parallel but they are difficult to rewrite to use multithreading,
-because they are either poorly written or too complex. We have written a
-framework, implemented in Java, that will execute the serial program in several
-threads. These threads working together help cut down the total runtime of the
-program exponentially. The next step is to separate the framework into a
-front-end that will run locally and a back-end which receives blocks of work and
-does the computations. This back-end should run in the cloud, on a machine that
-is dedicated to running embarrassingly parallel tasks only.
+to find the solution. Many problems in the biological sciences are 
+embarrassingly parallel but ofter their authors do not have the expertise to
+implement a parallel solution. We have written a framework, implemented in Java,
+that will execute the serial program in several threads. These threads working
+together help cut down the total runtime of the program significantly. The next
+step is to separate the framework into a front-end that will run locally and a
+back-end which receives blocks of work and does the computations. This back-end
+should run in the cloud, on a machine that is dedicated to running
+embarrassingly parallel tasks only.
 \end{abstract}
@@
 A computation graph consists of nodes that represent the functions or processes.
-The edges of the graph show data being passed from one process to another. If
-the graph is fully disconnected, none of the processes need to communicate to
-complete the computations. Such a computation is called embarrassingly
-parallel.\footnote{The term embarrassingly parallel was coined by Cleve Moler in
-his 1986 paper ``Matrix Computation on Distributed Memory Multiprocessors.''} In
-a practical situation, there will be some inter-node communication to set up the
-problem, and then again to accumulate the results.  Embarrassingly parallel
-problems can be easily performed on a cluster of servers or in any kind of
-distributed network, due to its lack of dependencies.
+and edges that represent data being passed. If the graph is fully disconnected,
+none of the processes need to communicate to complete the computations. Such a
+computation is called embarrassingly parallel\footnote{The term embarrassingly
+parallel was coined by Cleve Moler in his 1986 paper ``Matrix Computation on
+Distributed Memory Multiprocessors.''}. In a practical situation, there will be
+some inter-node communication to set up the problem, and then again to
+accumulate the results.  Embarrassingly parallel problems can be easily
+performed on a cluster of servers or in any kind of distributed network, due to
+the lack of dependencies.
 
@@
 
+%TODO: Embarrassingly parallel diagram
+\begin{figure}
+{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
+\caption{UML for the embarrassingly parallel framework}
+\label{fig:uml}
+\end{figure}
+
 \section{Background}
 
-TODO: Arrows?
+% TODO: Arrows?
 The motivation for this effort was based on research into different forms of the
@@
 variants, each with thousands of sequences. The Ka/Ks Calculator program took
-between five to thirty seconds to process one pair of sequences on a commodity
-desktop.
+between five to thirty seconds to process one pair of sequences on a ordinary
+machine.
 
-At this rate, we predicted it would take ten days of constant computation to
-complete the processing we needed. We neither had the time nor the expertise to
-develop a new parallel Ka/Ks program. We were also reluctant to revise the
-existing code to to implement the parallel computation because of the danger of
-introducing bugs into unfamiliar code and because of the learning curve required
-for C++ threading. Instead we wrote, a simple Java program to break up the input
-and spawn threads that would run the Ka/Ks Calculator process without having to
-make any changes to the code. When al of the threads ended, the contents of the
-output files were concatenated together to produce a final output that matches
-the format and order that would have been produced by a single invocation of the
-Ka/Ks Calculator program.
+At this rate, we predicted it would take upwards of ten days of constant
+computation to complete the processing we needed. We neither had the time nor
+the expertise to develop a new parallel Ka/Ks program. We were also reluctant to
+revise the existing code to to implement the parallel computation because of the
+danger of introducing bugs into unfamiliar code and because of the learning
+curve required for C++ threading. Instead we wrote, a simple Java program to
+break up the input and spawn threads that would run the Ka/Ks Calculator process
+without having to make any changes to the code. When al of the threads ended,
+the contents of the output files were concatenated together to produce a final
+output that matches the format and order that would have been produced by a
+single invocation of the Ka/Ks Calculator program.
 
 %TODO: get a better source? Talk about UCLUST and octupus
+% Talk about uclust and octupus and blast, even though there are parallelize
+% versions. Rewrite to not go into details about the programs but to talk about
+% that there are many programs.
 Ka/Ks Calculator is not the only embarrassingly parallel program that has the
@@
 
-%TODO: TALK ABOUT CLOUD PAPER HERE.
-Segue. Gunarathne et al.\cite{cloud} have investigated running much larger
-embarrassingly parallel biological problems using various cloud services. These
-services offer on-demand computational power with MORE.
-These services also have built in hooks to various distributed services, such as
-storage and databases. One of these technologies is the MapReduce framework,
-which allows user to perform distributed computation similar to this framework.
-As seen in figure X, Apache Hadoop, an open-source implementation of MapReduce,
-breaks down the input data into parts, runs them in parallel with the 'Map'
-function and then combines the results with the 'Reduce' function. TWO MORE
-SENTENCES.
+%TODO: Footnotes for days
+This framework is designed to run locally but there are other options when more
+power is needed. Gunarathne et al.\cite{cloud} have investigated running much
+larger embarrassingly parallel biological application using various cloud
+services. These services offer on-demand computational power with flexibility.
+These services have built in hooks to various distributed services, such as
+storage and databases. Amazon has a set of cloud computing services called
+Amazon Web Services(AWS) and Microsoft has a similar service named Microsoft
+Azure. AWS and Azure are esentially virtual instances run on machines in the
+cloud that can be spun up for extra computing power and shut down when not
+needed.
+
+Amazon also offers another service called Amazon Elastic MapReduce. This
+combines its virtual instance framework with Apache Hadoop. As seen
+in figure X, Hadoop breaks down the input data into parts, runs them in parallel
+with the 'Map' function and then combines the results with the 'Reduce'
+function. Dryad is a framework developed released by Microsoft Research that
+allows the end-user to create directed acyclic computation graphs that run on
+Windows High Performance Computer(HPC) clusters. Gunarathne et al. compared
+the services using several applications to analyze performance, cost and
+usability..
+
+%TODO: Hadoop figure
+\begin{figure}
+{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
+\caption{UML for the embarrassingly parallel framework}
+\label{fig:uml}
+\end{figure}
 
@@
 Figure 2 summarized the results; each line shows the time taken for each chunk
-of the data.
-As the numbers of threads increases, the runtime of the program decreases 
-exponentially. In a few cases, there was an increase in time when attempting to 
-max out the CPU usage. This occurs because the framework has to wait for the 
-CPU to be finished with its previous work before it can start any 
+of the data. As the numbers of threads increases, the runtime of the program
+decreases exponentially. In a few cases, there was an increase in time when
+attempting to max out the CPU usage. This occurs because the framework has to
+wait for the CPU to be finished with its previous work before it can start any
 further jobs.

### 2013-11-26 paper/paper.tex
New figures

@@
 \usepackage{cite}
+\usepackage{wrapfig}
 
@@
 
-%TODO: Embarrassingly parallel diagram
-\begin{figure}
-{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
-\caption{UML for the embarrassingly parallel framework}
-\label{fig:uml}
-\end{figure}
+\begin{wrapfigure}{R}{0.5\textwidth}
+    \begin{center}
+        \includegraphics{figures/ep.jpg}
+    \end{center}
+    \caption{Embarrassingly Parallel Model}
+    \label{fig:ep}
+\end{wrapfigure}
 
@@
 combines its virtual instance framework with Apache Hadoop. As seen
-in figure X, Hadoop breaks down the input data into parts, runs them in parallel
+in figure \ref{fig:map}, Hadoop breaks down the input data into parts, runs them in parallel
 with the 'Map' function and then combines the results with the 'Reduce'
@@
 the services using several applications to analyze performance, cost and
-usability..
+usability.
 
-%TODO: Hadoop figure
-\begin{figure}
-{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
-\caption{UML for the embarrassingly parallel framework}
-\label{fig:uml}
-\end{figure}
+\begin{wrapfigure}{L}{0.5\textwidth}
+    \begin{center}
+        \includegraphics{figures/MapReduce.jpg}
+    \end{center}
+    \caption{MapReduce Model}
+    \label{fig:map}
+\end{wrapfigure}
 
@@
 \caption{Runtimes for the Ka/Ks Calculator though the framework}
-\label{fig:graph}
+\label{fig:kaksgraph}
 \end{figure}
 
-Figure 2 summarized the results; each line shows the time taken for each chunk
+Figure \ref{fig:kaksgraph} summarized the results; each line shows the time taken for each chunk
 of the data. As the numbers of threads increases, the runtime of the program

### 2013-11-29 paper/paper.tex
More paper work

@@
 \begin{document}
-\title{A Java Wrapper For Embarrassingly Parallel Problems}
+\title{A Java Framework For Embarrassingly Parallel Problems}
 \author{Jacob Schwartz}
@@
 
-% TODO: Arrows?
 The motivation for this effort was based on research into different forms of the
@@
 Desi, are very different in size and color. The Desi is also more resistant to
-diseases and are more effective at root nodule symbiosis. The Kabuli has a large
-but soft shell, which make it at better food source for humans. Both forms are
+diseases and is more effective at root nodule symbiosis. The Kabuli has a large
+but soft shell, which makes it a better food source for humans. Both forms are
 cultivated and have been under human selection for several thousand years. We
@@
 
-%TODO: get a better source? Talk about UCLUST and octupus
-% Talk about uclust and octupus and blast, even though there are parallelize
-% versions. Rewrite to not go into details about the programs but to talk about
-% that there are many programs.
 Ka/Ks Calculator is not the only embarrassingly parallel program that has the
 potential to take several days to run on a data set. In fact, there are several
-embarrassingly parallel programs in the biological sciences. To deal with large
-amounts of data, the best method is often to group them into clusters.
-Hierarchical clustering algorithms take the data and then organize into
-hierarchical structure, usually a dendrogram, based on a priority matrix. There
-are hierarchical clustering algorithms that can be implemented in parallel using
-an embarrassingly parallel approach.  With several applications that would
-benefit from parallelism in this field, it was obvious it would be desirable to
-develop a framework for the parallelization task. \cite{cluster}
+embarrassingly parallel programs in the biological sciences. Basic Local
+Alignment Search Tool, or BLAST\fotenote{blast.ncbi.nlm.nih.gov}, is an
+algorithm that compares many aspects of DNA sequences, like the nucleotides or
+amino acid sequences. In addition, the user can also compare to the sequences to
+a database of sequences to identity known subsequences. There are many
+implementations of BLAST, some of them already have parallel implementations.
+Many applications however do not have parallel processing capabilities. A class
+of problems that organize large amounts of data into similar groups called
+clusters. Two applications, octupus\footnote{octupus.sourceforge.com} and
+USEARCH\footnote{https://www.drive5.com/usearch}, are examples of programs in
+this class that do not have parallel versions. With several applications that
+would benefit from parallelism in this field, it was obvious it would be
+desirable to develop a framework for the parallelization task.
 
-%TODO: Footnotes for days
 This framework is designed to run locally but there are other options when more
@@
 storage and databases. Amazon has a set of cloud computing services called
-Amazon Web Services(AWS) and Microsoft has a similar service named Microsoft
-Azure. AWS and Azure are esentially virtual instances run on machines in the
-cloud that can be spun up for extra computing power and shut down when not
-needed.
+Amazon Web Services(AWS)\footnote{https://aws.amazon.com} and Microsoft has a
+similar service named Microsoft Azure\footnote{https://www.windowsazure.com}.
+AWS and Azure are esentially virtual instances run on machines in the cloud that
+can be spun up for extra computing power and shut down when not needed.
 
-Amazon also offers another service called Amazon Elastic MapReduce. This
-combines its virtual instance framework with Apache Hadoop. As seen
-in figure \ref{fig:map}, Hadoop breaks down the input data into parts, runs them in parallel
-with the 'Map' function and then combines the results with the 'Reduce'
-function. Dryad is a framework developed released by Microsoft Research that
-allows the end-user to create directed acyclic computation graphs that run on
-Windows High Performance Computer(HPC) clusters. Gunarathne et al. compared
-the services using several applications to analyze performance, cost and
-usability.
+Amazon also offers another service called Amazon Elastic
+MapReduce\footnote{https://aws.amazon.com/elasticmapreduce}. This combines its
+virtual instance framework with Apache
+Hadoop\footnote{https://hadoop.apache.org}. As seen in figure \ref{fig:map},
+Hadoop breaks down the input data into parts, runs them in parallel with the
+'Map' function and then combines the results with the 'Reduce' function.
+DryadLINQ\footnote{https://research.microsoft.com/apps/mobile/showpage.aspx?page=/en-us/projects/draydlinq}
+is a framework developed released by Microsoft Research that allows the end-user
+to create directed acyclic computation graphs that run on Windows High
+Performance Computer(HPC)\footnote{https://www.microsoft.com/hpc} clusters.
+Gunarathne et al. compared the services using several applications to analyze
+performance, cost and usability.
 
@@
 applications: the Ka/Ks Calculator and two different sequence clustering
-algorithms. In all cases, we compared the framework based application with the
-original using different data partitions and different thread counts.
+algorithms, USEARCH and ocutupus. In all cases, we compared the framework based
+application with the original using different data partitions and different
+thread counts.
 
 \subsection{Ka/Ks Calculator}
+TODO: Reword when redone
 Ka/Ks Calculator was run through the framework with ten different samples, each
 containing sixteen units of work. Each sample was run by the framework thread
-counts, starting at 1 and increasing by 
-powers of two until the 100\% processor usage (16 processors). These tests were run
-with minimal other activity on the server.
+counts, starting at 1 and increasing by powers of two until the 100\% processor
+usage (16 processors). These tests were run with minimal other activity on the
+server.
 
@@
 
-In the future, we would like to see this work be split into a
-local front-end and a cloud back-end. This allows for an even greater runtime
-decrease because the number of compute nodes available is larger than the number
-of processors on most machines. Splitting the framework also allows for better
-testing of cloud environments, where the cloud environment itself could be a
-configurable option for end users.
-TODO: MORE
+In the future, we would like to see this work be split into a local front-end
+and a cloud back-end. The configuration set-up process will run locally. The
+split and merge steps depend on the cloud service chosen, but data processing
+will always occur in the cloud. Splitting the framework will give performance
+improvements, because the number of compute nodes can be much larger than the
+number of processors on an average machine. More customization options would be
+available to the end-user, such as choice of environment. This provides ultimate
+control for the group to pick the best enviroment to suit its computational and
+financial needs.
 

### 2013-11-30 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java
Paper mods and command line argument change

@@ -225,23 +225,15 @@ public final class ConfigWizard
             add(execChooser);
             add(new JLabel(SEP));
 
-            // Name for input and output flags
-            // Setting for the split pattern
-            final JTextField inFlagField = new JTextField();
-            inFlagField.setName(Configuration.IN_FLAG_KEY);
-            inFlagField.setPreferredSize(new Dimension(50, 20));
-            add(new JLabel("Flag for executable to define input file"));
-            add(inFlagField);
-            add(new JLabel("(Leave blank to use stdin)"));
+            // Arguments for executable
+            final JTextField argumentField = new JTextField();
+            argumentField.setName(Configuration.ARGUMENT_KEY);
+            argumentField.setPreferredSize(new Dimension(50, 200));
+            add(new JLabel("Enter in the arguments for the executable"));
+            add(argumentField);
+            add(new JLabel("   Use @ to replace the input file"));
+            add(new JLabel("   Use $ to replace the output file"));
             add(new JLabel(SEP));
-
-            // Setting for the split pattern
-            final JTextField outFlagField = new JTextField();
-            outFlagField.setName(Configuration.OUT_FLAG_KEY);
-            outFlagField.setPreferredSize(new Dimension(50, 20));
-            add(new JLabel("Flag for executable to define output dir"));
-            add(outFlagField);
-            add(new JLabel("(Leave blank to use stdout)"));
         }
     }
 

### 2013-11-30 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -7,7 +7,6 @@ import com.fasterxml.jackson.core.JsonParser;
 import com.fasterxml.jackson.core.JsonToken;
 import java.io.File;
 import java.io.IOException;
-import java.util.HashMap;
 import java.util.Map;
 import java.util.Iterator;
 import org.apache.commons.logging.Log;
@@ -46,16 +45,6 @@ public final class Configuration
     public static final String EXEC_LOC_KEY = "execLoc";
 
     /**
-     * Key for in flag setting.
-     */
-    public static final String IN_FLAG_KEY = "inFlag";
-
-    /**
-     * Key for out flag setting.
-     */
-    public static final String OUT_FLAG_KEY = "outFlag";
-    
-    /**
      * Key for threading setting.
      */
     public static final String NUM_PROCESSES_KEY = "numProcesses";
@@ -79,6 +68,11 @@ public final class Configuration
      * Key for setting the merge method.
      */
     public static final String MERGE_METHOD_KEY = "mergeMethod";
+
+    /**
+     * Key for setting the command line argument.
+     */
+    public static final String ARGUMENT_KEY = "argument";
 
     /**
      * The Log.
@@ -116,17 +110,6 @@ public final class Configuration
     private String execPath;
 
     /**
-     * The flags for the executable to show how to enter input and outfile.
-     */
-    private String inFlag;
-    private String outFlag;
-
-    /**
-     * The arguments for the execuatable.
-     */
-    private Map<String, String> execArgs;
-
-    /**
      * Whether or not to make a stats file.
      */
     private boolean makeStats;
@@ -145,6 +128,11 @@ public final class Configuration
      * Whether or not to save the config file.
      */
     private boolean save;
+
+    /**
+     * The arguments for the command line.
+     */
+    private String argument;
     
     /**
      * Constructs a configuration file from a map.
@@ -174,12 +162,6 @@ public final class Configuration
                      break;
                  case EXEC_LOC_KEY:
                      this.execPath = (String) val;
-                     break;
-                 case IN_FLAG_KEY: 
-                     this.inFlag = (String) val;
-                     break;
-                 case OUT_FLAG_KEY:
-                     this.outFlag = (String) val;
                      break;
                  case NUM_PROCESSES_KEY:
                      this.numberOfThreads = Integer.valueOf((String) val);
@@ -264,12 +246,6 @@ public final class Configuration
                 case EXEC_LOC_KEY:
[…]

### 2013-11-30 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -21,14 +21,9 @@ public final class Worker extends Thread
     private static String exec;
 
     /**
-     * The in flag for the executable.
+     * The arguments for the executable.
      */
-    private static String inFlag;
-
-    /**
-     * The out flag for the executable.
-     */
-    private static String outFlag;
+    private static String[] arguments;
 
     /**
      * The Log.
@@ -81,23 +76,14 @@ public final class Worker extends Thread
     }
     
     /**
-     * Set the flag to signify where the input goes for the executable.
+     * Set the arguments for executable.
      *
-     * @param in - the in flag used to signify the input file 
+     * @param argument - the command line argument string
      */
-    public static void setInFlag(final String in)
+    public static void setArguments(final String argument)
     {
-        inFlag = in;
-    }
-
-    /**
-     * Set the flag to signify where the output goes for the executable.
-     *
-     * @param out - the flag used to signify the output file 
-     */
-    public static void setOutFlag(final String out)
-    {
-        outFlag = out;
+        LOG.debug("setArgument: " + argument);
+        arguments = argument.split("\\w");
     }
 
     /**
@@ -153,26 +139,23 @@ public final class Worker extends Thread
         // Create the executable
         final List<String> commands = new ArrayList<String>();
         commands.add(exec);
-
-        if (inFlag != null)
+        
+        // Add the arguments in
+        for (String a : arguments)
         {
-            commands.add(inFlag);
+            if (a.equals("@"))
+            {
+                commands.add(in);
+            }
+            else if (a.equals("$"))
+            {
+                commands.add(out);
+            }
+            else
+            {
+                commands.add(a);
+            }
         }
-        else
-        {
-            commands.add("<");
-        }
-        commands.add(in);
-
-        if (outFlag != null)
-        {
-            commands.add(outFlag);
-        }
-        else
-        {
-            commands.add(">");
-        }
-        commands.add(out);
 
         return new ProcessBuilder(commands);
     }

### 2013-11-30 src/main/java/edu/unh/schwartz/epframework/worker/WorkerPool.java

@@ -32,8 +32,7 @@ public final class WorkerPool
     {
         // Set the executable information in the worker
         Worker.setExecutable(config.getExecutable());
-        Worker.setInFlag(config.getInFlag());
-        Worker.setOutFlag(config.getOutFlag());
+        Worker.setArguments(config.getArguments());
 
         // Initialize the threads
         workers = new Worker[config.getNumberOfThreads()];

### 2013-11-30 paper/paper.tex
Paper mods and command line argument change
Spell checked

@@
 to find the solution. Many problems in the biological sciences are 
-embarrassingly parallel but ofter their authors do not have the expertise to
+embarrassingly parallel but often their authors do not have the expertise to
 implement a parallel solution. We have written a framework, implemented in Java,
@@
 amino acid sequences. In addition, the user can also compare to the sequences to
-a database of sequences to identity known subsequences. There are many
+a database of sequences to identity known subservience's. There are many
 implementations of BLAST, some of them already have parallel implementations.
@@
 similar service named Microsoft Azure\footnote{https://www.windowsazure.com}.
-AWS and Azure are esentially virtual instances run on machines in the cloud that
+AWS and Azure are essentially virtual instances run on machines in the cloud that
 can be spun up for extra computing power and shut down when not needed.
@@
 
-We evaluated the convenience and performace of the framework on two different
+We evaluated the convenience and performance of the framework on two different
 applications: the Ka/Ks Calculator and two different sequence clustering
@@
 
-Place holder text
+TODO: Place holder text
 
@@
 
-TODO: First paragrpah should summarize performce: its clear that framework
-provices simple and effective module for adding parallelism to a class of
+TODO: First paragraph should summarize performance: its clear that framework
+provides simple and effective module for adding parallelism to a class of
 file-oriented EP apps. More self praise.
@@
 available to the end-user, such as choice of environment. This provides ultimate
-control for the group to pick the best enviroment to suit its computational and
+control for the group to pick the best environment to suit its computational and
 financial needs.

### 2013-11-30 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java
Merge method stuff

@@ -3,9 +3,11 @@ package edu.unh.schwartz.epframework.config;
 import java.awt.Dimension;
 import java.util.ArrayList;
 import java.util.List;
+import javax.swing.ButtonGroup;
 import javax.swing.JCheckBox;
 import javax.swing.JDialog;
 import javax.swing.JLabel;
+import javax.swing.JRadioButton;
 import javax.swing.JScrollPane;
 import javax.swing.JTextArea;
 import javax.swing.JTextField;
@@ -200,7 +202,6 @@ public final class ConfigWizard
             inDirChooser.setName(Configuration.IN_FILE_DIR_KEY);
             add((new JLabel("Select the input directory: ")));
             add(inDirChooser);
-
             add(new JLabel(SEP));
 
             // Settings for the output location
@@ -234,6 +235,24 @@ public final class ConfigWizard
             add(new JLabel("   Use @ to replace the input file"));
             add(new JLabel("   Use $ to replace the output file"));
             add(new JLabel(SEP));
+
+            final JRadioButton jRadioDefault = new JRadioButton("Default");
+            final JRadioButton jRadioCustom = new JRadioButton("Custom");
+            final JRadioButton jRadioExternal = new JRadioButton("External");
+
+            jRadioDefault.setName(Configuration.DEFAULT_MERGE_KEY);
+            jRadioDefault.setName(Configuration.CUSTOM_MERGE_KEY);
+            jRadioDefault.setName(Configuration.EXTERNAL_MERGE_KEY);
+
+            final ButtonGroup group = new ButtonGroup();
+            group.add(jRadioDefault);
+            group.add(jRadioCustom);
+            group.add(jRadioExternal);
+
+            add(new JLabel("Select the merge method"));
+            add(jRadioDefault);
+            add(jRadioCustom);
+            add(jRadioExternal);
         }
     }
 

### 2013-11-30 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -67,7 +67,17 @@ public final class Configuration
     /**
      * Key for setting the merge method.
      */
-    public static final String MERGE_METHOD_KEY = "mergeMethod";
+    public static final String EXTERNAL_MERGE_KEY = "externalMerge";
+
+    /**
+     * Key for setting the merge method.
+     */
+    public static final String CUSTOM_MERGE_KEY = "customMerge";
+
+    /**
+     * Key for setting the merge method.
+     */
+    public static final String DEFAULT_MERGE_KEY = "defaultMerge";
 
     /**
      * Key for setting the command line argument.
@@ -122,7 +132,7 @@ public final class Configuration
     /**
      * The method used to merge the results.
      */
-    private int mergeMethod;
+    private int mergeMethod = -1;
 
     /**
      * Whether or not to save the config file.
@@ -140,76 +150,40 @@ public final class Configuration
      */
     public Configuration(final Map<String, Object> map)
     {
-         final Iterator<String> it = map.keySet().iterator();
-         while (it.hasNext()) 
-         {
-             final String key = it.next();
-             final Object val = map.get(key);
-             LOG.debug(key  + " => " + val);
-             switch(key)
-             {
-                 case IN_FILE_KEY:
-                     this.inputFileName = (String) val;
-                     break;
-                 case IN_FILE_DIR_KEY:
-                     this.inputFileDirName = (String) val;
-                     break;
-                 case SPLIT_PATTERN_KEY:
-                     this.splitPattern = (String) val;
-                     break;
-                 case OUT_FILE_KEY:
-                     this.outDirName = (String) val;
-                     break;
-                 case EXEC_LOC_KEY:
-                     this.execPath = (String) val;
-                     break;
-                 case NUM_PROCESSES_KEY:
-                     this.numberOfThreads = Integer.valueOf((String) val);
-                     break;
-                 case STATS_KEY:
-                     this.makeStats = (boolean) val;
-                     break;
-                 case NUM_HEADER_KEY:
-                     this.numberOfHeaderLines = Integer.valueOf((String) val);
-                     break;
-                 case SAVE_KEY:
-                     this.save = (boolean) val;
-                     break;
-                 case MERGE_METHOD_KEY:
-                     this.mergeMethod = Integer.valueOf((String) val);
-                     break;
-                 default:
-                     assert(false);
-             }
-         }
+        loadConfig(map);
 
-         // Check to make sure necessary fields were filled
-         boolean crash = false;
-         if ((this.inputFileDirName == null && this.inputFileName == null) || 
[…]

### 2013-12-02 examples/kaks/KaKs_Calculator1.2/src/KaKs.cpp
Removed Kaks calc from version control

@@ -1,619 +1,0 @@
-/************************************************************
-* Copyright (C) 2005, BGI of Chinese Academy of Sciences
-* All rights reserved.
- 
-* Filename: KaKs.cpp
-* Abstract: Declaration of KAKS class including several methods.
-
-* Version: 1.0
-* Author: Zhang Zhang (zhanghzhang@genomics.org.cn)
-* Date: Feb.2, 2005
-
-*************************************************************/
-
-#include "KaKs.h"
-
-KAKS::KAKS() {
-
-	string items[] = {"Sequence", "Method", "Ka", "Ks", "Ka/Ks", 
-		  			  "P-Value(Fisher)", "Length", "S-Sites", "N-Sites", "Fold-Sites(0:2:4)",
-					  "Substitutions", "S-Substitutions", "N-Substitutions", "Fold-S-Substitutions(0:2:4)", "Fold-N-Substitutions(0:2:4)", 
-					  "Divergence-Time", "Substitution-Rate-Ratio(rTC:rAG:rTA:rCG:rTG:rCA/rCA)", "GC(1:2:3)", "ML-Score", "AICc",
-					  "Akaike-Weight", "Model"};  //21 outputing items
-	
-	//Format of outputing parameters
-	int i;
-	for (i=0; i<sizeof(items)/sizeof(string); i++) titleInfo.push_back(items[i]);
-
-	//Load Methods' Names and References for -h in linux, also for windows' tool tip
-	method_name.push_back("NG");   method_ref.push_back("Nei, M. and Gojobori, T. (1986)");
-	method_name.push_back("LWL");  method_ref.push_back( "Li, W.H., Wu, C.I. and Luo, C.C. (1985)");
-	method_name.push_back("LPB");  method_ref.push_back("Li, W.H. (1993) and Pamilo, P. and Bianchi, N.O. (1993)");
-	method_name.push_back("MLWL"); method_ref.push_back("Tzeng, Y.H., Pan, R. and Li, W.H. (2004)");
-	method_name.push_back("MLPB"); method_ref.push_back("Tzeng, Y.H., Pan, R. and Li, W.H. (2004)");
-	method_name.push_back("GY");   method_ref.push_back("Goldman, N. and Yang, Z. (1994)");
-	method_name.push_back("YN");   method_ref.push_back("Yang, Z. and Nielsen, R. (2000)");
-	method_name.push_back("MYN");  method_ref.push_back("Zhang Z., Jun L. and Jun Y. (2006)");
[…]

### 2013-12-09 src/main/java/edu/unh/schwartz/epframework/Chunk.java
1.0 changes and kaks data

@@ -75,8 +75,10 @@ public final class Chunk implements Comparable<Chunk>
         this.content = sb.toString();
 
         // Write the content to a file in the directory
-        Files.copy(inFile.toPath(), 
-            new File("tmp" + inFile.getName()).toPath());
+        final File d = 
+            new File(directory.getAbsolutePath() + "/" + inFile.getName());
+        Files.copy(inFile.toPath(), d.toPath()); 
+
     }
 
     /**

### 2013-12-09 src/main/java/edu/unh/schwartz/epframework/ChunkManager.java

@@ -42,6 +42,8 @@ public final class ChunkManager
      */
     private static final String EXTERNAL_MERGE_EXEC_NAME = "./merger";
 
+    private final String rootDir = "/tmp/";
+
     /**
      * The pattern used to split the input file.
      */
@@ -113,11 +115,12 @@ public final class ChunkManager
                 final String content = sb.toString();
 
                 // Make a directory for that file
-                final File dir = new File("/tmp/" + content.hashCode());
+                final File dir = new File(rootDir + content.hashCode());
                 dir.mkdir();
 
                 // Write the content to a file
-                final PrintWriter inWriter = new PrintWriter(dir.getAbsolutePath() + "/in");
+                final PrintWriter inWriter = 
+                    new PrintWriter(dir.getAbsolutePath() + "/in");
                 inWriter.println(content);
                 inWriter.close();
 
@@ -147,7 +150,8 @@ public final class ChunkManager
         final File directory = new File(dir);
         for (File i : directory.listFiles())
         {
-            final File d = new File("tmp/" + i.getName().hashCode());
+            final File d = new File(rootDir + i.getName().hashCode());
+            d.mkdir();
             this.chunks.add(new Chunk(i , d));
         }
     }

### 2013-12-09 src/main/java/edu/unh/schwartz/epframework/EPFramework.java

@@ -34,7 +34,7 @@ final class EPFramework
      *
      * @param config - the instructions for the wrapper
      */
-    private static void start(final Configuration config)
+    private static void run(final Configuration config)
     {
         Chunk.setHeaderLines(config.getNumHeaderLines());
 
@@ -44,12 +44,14 @@ final class EPFramework
             if (config.getInputFile() == null)
             {
                 // Make a chunk for each presplit file
+                LOG.info("Loading chunks from directory");
                 cm = new ChunkManager(config.getNumHeaderLines());
                 cm.splitFiles(config.getInputDirectory());
             }
             else
             {
                 // Read in the input file and get the chunks
+                LOG.info("Reading chunks from input file");
                 cm = new ChunkManager(config.getSplitPattern(), 
                         config.getNumHeaderLines());
 
@@ -104,7 +106,7 @@ final class EPFramework
                 ConfigWizard.getInstance().createConfiguration();
             if (config != null)
             {
-                start(config);
+                run(config);
             }
         }
         // First command line arg is a configuration file
@@ -114,7 +116,7 @@ final class EPFramework
             {
                 LOG.debug("Loading configuration file");
                 final Configuration config = new Configuration(args[0]);
-                start(config);
+                run(config);
             }
             catch (IOException e)
             {

### 2013-12-09 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -158,7 +158,7 @@ public final class Configuration
         // Check to make sure necessary fields were filled
         boolean crash = false;
         if ((this.inputFileDirName == null && this.inputFileName == null) || 
-                (this.inputFileName != null && this.inputFileName != null))
+                (this.inputFileDirName != null && this.inputFileName != null))
         {
             LOG.fatal("An input file OR directory must be selected");
             crash = true;
@@ -231,6 +231,9 @@ public final class Configuration
                     break;
                 case NUM_HEADER_KEY:
                     this.numberOfHeaderLines = jp.getIntValue();
+                    break;
+                case ARGUMENT_KEY:
+                    this.argument = jp.getText();
                     break;
                 case DEFAULT_MERGE_KEY:
                     if (jp.getBooleanValue())
@@ -311,6 +314,9 @@ public final class Configuration
                      {
                          this.mergeMethod = 2;
                      }
+                     break;
+                 case ARGUMENT_KEY:
+                     this.argument = (String) val;
                      break;
                  default:
                      assert(false);
@@ -436,7 +442,11 @@ public final class Configuration
             jg.writeStringField(EXEC_LOC_KEY, this.execPath);
             jg.writeNumberField(NUM_PROCESSES_KEY, this.numberOfThreads);
             jg.writeBooleanField(STATS_KEY, this.makeStats);
+            jg.writeStringField(ARGUMENT_KEY, this.argument);
             jg.writeNumberField(NUM_HEADER_KEY, this.numberOfHeaderLines);
+            jg.writeBooleanField(EXTERNAL_MERGE_KEY, this.mergeMethod == 2);
+            jg.writeBooleanField(CUSTOM_MERGE_KEY, this.mergeMethod == 1);
+            jg.writeBooleanField(DEFAULT_MERGE_KEY, this.mergeMethod == 0);
             jg.writeEndObject();
             jg.close();
             LOG.info("Configuration saved");

### 2013-12-09 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -83,7 +83,7 @@ public final class Worker extends Thread
     public static void setArguments(final String argument)
     {
         LOG.debug("setArgument: " + argument);
-        arguments = argument.split("\\w");
+        arguments = argument.split("\\s");
     }
 
     /**
@@ -156,6 +156,14 @@ public final class Worker extends Thread
                 commands.add(a);
             }
         }
+
+        // System.out.println("\n\n\n");
+        // for(String co : commands)
+        // {
+            // System.out.print(co);
+            // System.out.print(" ");
+        // }
+        // System.out.println();
 
         return new ProcessBuilder(commands);
     }

### 2013-12-10 paper/paper.tex
directory output

@@
 We evaluated the convenience and performance of the framework on two different
-applications: the Ka/Ks Calculator and two different sequence clustering
-algorithms, USEARCH and ocutupus. In all cases, we compared the framework based
-application with the original using different data partitions and different
-thread counts.
+applications: the Ka/Ks Calculator and a sequence clustering algorithms,
+ocutupus. In all cases, we compared the framework based application with the
+original using different data partitions and different thread counts.
 
 \subsection{Ka/Ks Calculator}
-TODO: Reword when redone
-Ka/Ks Calculator was run through the framework with ten different samples, each
+Ka/Ks Calculator was run through the framework with five different samples, each
 containing sixteen units of work. Each sample was run by the framework thread
-counts, starting at 1 and increasing by powers of two until the 100\% processor
-usage (16 processors). These tests were run with minimal other activity on the
-server.
+counts, starting at 1 and increasing by multiple of two until the runtimes
+leveled off. The samples were then all run again at 100\% processor usage (16
+processors). These tests were run with minimal other activity on the server.
 
@@
 
-Figure \ref{fig:kaksgraph} summarized the results; each line shows the time taken for each chunk
-of the data. As the numbers of threads increases, the runtime of the program
-decreases exponentially. In a few cases, there was an increase in time when
-attempting to max out the CPU usage. This occurs because the framework has to
-wait for the CPU to be finished with its previous work before it can start any
-further jobs.
+Figure \ref{fig:kaksgraph} summarized the results; each line shows the time
+taken for each chunk of the data. As the numbers of threads increases, the
+runtime of the program decreases exponentially. In a few cases, there was an
+increase in time when attempting to max out the CPU usage. This occurs because
+the framework has to wait for the CPU to be finished with its previous work
+before it can start any further jobs.
 
@@
 
-\subsection{uClust}
-
-TODO: Place holder text
-
 \subsection{Octupus}
 
-TODO: Place holder text
+A version of octupus was also run through the framework and was tested against
+two different sized data sets. Both sets were first clustered at 90\% similarity
+and the resulting clusters were used as the input for the framework's run, which
+is for 97\% similarity. The framework in this case was just run at four and
+eight threads and Figure \ref{fig:octugraph} shows that the running the
+framework once again provides a benefit for the user.
+
+\begin{figure}
+{\resizebox{5.2in}{!}{\includegraphics{experiment/outoctu.png}}}
+\caption{Runtimes for the Ka/Ks Calculator though the framework}
+\label{fig:octugraph}
+\end{figure}
 
@@
 
-TODO: First paragraph should summarize performance: its clear that framework
-provides simple and effective module for adding parallelism to a class of
-file-oriented EP apps. More self praise.
+It is clear that the framework provides an effective yet simple to use module to
+add parallelism to a specific class of file-oriented embarrassingly parallel
+problems. Two sentences with specifics from the graphs. More self-praise
 
@@
 \begin{thebibliography}{1}
-\bibitem{history}
-Moler, Cleve. ``\emph{Matrix Computation on Distributed Memory Multiprocessors."
-}, Hypercube Multiprocessors, 1986: Proceedings of the First Conference on
-Hypercube Multiprocessors, Knoxville, Tennessee, August 24-27, 1985. By Michael
-T. Heath. Philadelphia: SIAM, 1986. N. pag. Print.
 \bibitem{kaks}
@@
 Genomics Proteomics Bioinformatics, November 2006.
-\bibitem{cluster}
-Rua, Xu, Wunsch, Donald II, \emph{Survey of Clustering Algorithms},
-IEEE Transactions on Neural Networks VOL. 16, NO. 3, MAY 2005
 \bibitem{cloud}

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/Chunk.java

@@ -75,9 +75,7 @@ public final class Chunk implements Comparable<Chunk>
         this.content = sb.toString();
 
         // Write the content to a file in the directory
-        final File d = 
-            new File(directory.getAbsolutePath() + "/" + inFile.getName());
-        Files.copy(inFile.toPath(), d.toPath()); 
+        Files.copy(inFile.toPath(), new File(getInFileName()).toPath()); 
 
     }
 
@@ -189,14 +187,23 @@ public final class Chunk implements Comparable<Chunk>
 
     /**
      * Creates the output file for use my the worker.
+     *
+     * @param dir - true iff the output file should be a directory
      */
-    public void createOutFile()
+    public void createOutFile(final boolean dir)
     {
         final String outName = getOutFileName();
         final File out = new File(outName);
         try
         {
-            out.createNewFile();
+            if (dir)
+            {
+                out.mkdir(); 
+            }
+            else
+            {
+                out.createNewFile();
+            }
         }
         catch (IOException e)
         {

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/EPFramework.java

@@ -86,8 +86,8 @@ final class EPFramework
             LOG.info("Printing stats");
             cm.printStats(wp.getStats(), config.getOutputDirectory());
         }
-        LOG.info("Cleaning up");
-        cm.cleanUp();
+        // LOG.info("Cleaning up");
+        // cm.cleanUp();
     }
 
     /**

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/config/ConfigWizard.java

@@ -277,20 +277,24 @@ public final class ConfigWizard
             add(spinner);
             add(new JLabel(SEP));
 
+            final JCheckBox fmtbox = new JCheckBox();
+            fmtbox.setName(Configuration.OUTPUT_FMT_KEY);
+            add(new JLabel("Does the exec output directories?"));
+            add(fmtbox);
+            add(new JLabel(SEP));
+           
             final JCheckBox box = new JCheckBox();
             box.setName(Configuration.STATS_KEY);
             add(new JLabel("Create stats file?"));
             add(box);
             add(new JLabel(SEP));
 
-            final JTextField headerField = new JTextField();
-            headerField.setName(Configuration.NUM_HEADER_KEY);
-            headerField.setText("0");
-            headerField.setPreferredSize(new Dimension(50, 20));
+            final WizardSpinner spinner2 = new WizardSpinner(options);
+            spinner2.setName(Configuration.NUM_HEADER_KEY);
             add(new JLabel("Number of header lines in output files: "));
-            add(headerField);
+            add(spinner2);
             add(new JLabel(SEP));
- 
+
             final JCheckBox savebox = new JCheckBox();
             savebox.setName(Configuration.SAVE_KEY);
             add(new JLabel("Save Configuration File?"));

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/config/Configuration.java

@@ -88,6 +88,11 @@ public final class Configuration
     public static final String ARGUMENT_KEY = "argument";
 
     /**
+     * Key for output format argument.
+     */
+    public static final String OUTPUT_FMT_KEY = "outputFmt";
+
+    /**
      * The Log.
      */
     private static final Log LOG = LogFactory.getLog(Configuration.class);
@@ -146,6 +151,11 @@ public final class Configuration
      * The arguments for the command line.
      */
     private String argument;
+
+    /**
+     * The output format: true for directories or false for files.
+     */
+    private boolean outputFmt;
     
     /**
      * Constructs a configuration file from a map.
@@ -232,9 +242,6 @@ public final class Configuration
                 case NUM_HEADER_KEY:
                     this.numberOfHeaderLines = jp.getIntValue();
                     break;
-                case ARGUMENT_KEY:
-                    this.argument = jp.getText();
-                    break;
                 case DEFAULT_MERGE_KEY:
                     if (jp.getBooleanValue())
                     {
@@ -252,6 +259,12 @@ public final class Configuration
                     {
                         this.mergeMethod = 2;
                     }
+                    break;
+                case ARGUMENT_KEY:
+                    this.argument = jp.getText();
+                    break;
+                case OUTPUT_FMT_KEY:
+                    this.outputFmt = jp.getBooleanValue();
                     break;
                  default:
                     assert(false);
@@ -317,6 +330,9 @@ public final class Configuration
                      break;
                  case ARGUMENT_KEY:
                      this.argument = (String) val;
+                     break;
+                 case OUTPUT_FMT_KEY:
+                     this.outputFmt = (boolean) val;
                      break;
                  default:
                      assert(false);
@@ -409,6 +425,14 @@ public final class Configuration
     }
 
     /**
+     * @return true iff the output should be in directories
+     */
+    public boolean getOutputSetting()
+    {
+        return this.outputFmt;
+    }
+
+    /**
      * Saves the configuration in a file so it can be loaded if the user wants
      * to use the configuration again.
      */
@@ -447,6 +471,7 @@ public final class Configuration
             jg.writeBooleanField(EXTERNAL_MERGE_KEY, this.mergeMethod == 2);
             jg.writeBooleanField(CUSTOM_MERGE_KEY, this.mergeMethod == 1);
             jg.writeBooleanField(DEFAULT_MERGE_KEY, this.mergeMethod == 0);
[…]

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -26,6 +26,11 @@ public final class Worker extends Thread
     private static String[] arguments;
 
     /**
+     * Whether the Chunks need output files or output directories.
+     */
+    private static boolean outputDirs;
+
+    /**
      * The Log.
      */
     private static final Log LOG = LogFactory.getLog(Worker.class);
@@ -87,6 +92,16 @@ public final class Worker extends Thread
     }
 
     /**
+     * Set the output file/directory setting.
+     *
+     * @param dirs - true iff output directories are supposed to be used
+     */
+    public static void setOutputDirs(final boolean dirs)
+    {
+        outputDirs = dirs;
+    }
+
+    /**
      * {@inheritDoc}
      */
     @Override
@@ -97,7 +112,7 @@ public final class Worker extends Thread
         {
             // Grab a chunk and get it ready for output
             final Chunk c = this.queue.poll();
-            c.createOutFile();
+            c.createOutFile(outputDirs);
 
             try
             {

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/worker/WorkerPool.java

@@ -33,6 +33,7 @@ public final class WorkerPool
         // Set the executable information in the worker
         Worker.setExecutable(config.getExecutable());
         Worker.setArguments(config.getArguments());
+        Worker.setOutputDirs(config.getOutputSetting());
 
         // Initialize the threads
         workers = new Worker[config.getNumberOfThreads()];

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/Chunk.java
More changes for files

@@ -117,14 +117,26 @@ public final class Chunk implements Comparable<Chunk>
      */
     public void clean()
     {
-        // Delete the files in the directories
-        for (final File f : this.directory.listFiles())
-        {
-            f.delete();
-        }
-        this.directory.delete();
-
+        delete(this.directory);
         this.runtime = 0;
+    }
+
+    /**
+     * Recursively deletes file system rooted at file.
+     *
+     * @param file - the file to delete
+     */
+    private void delete(final File file)
+    {
+        if (file.isDirectory())
+        {
+            for (final File f : file.listFiles())
+            {
+                delete(f);
+            }
+        }
+
+        file.delete();
     }
 
     /**

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/ChunkManager.java

@@ -152,7 +152,7 @@ public final class ChunkManager
         {
             final File d = new File(rootDir + i.getName().hashCode());
             d.mkdir();
-            this.chunks.add(new Chunk(i , d));
+            this.chunks.add(new Chunk(i, d));
         }
     }
     

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -121,7 +121,7 @@ public final class Worker extends Thread
                 pb.redirectErrorStream(true);
 
                 // Start the work and capture the time it takes to run
-                LOG.info("Starting chunk on Worker " + this.idNum);
+                LOG.info("Starting chunk " + c.hashCode() + " on Worker " + this.idNum);
                 final long start = System.currentTimeMillis();
                 final Process proc = pb.start();
                 proc.waitFor();

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/ChunkManager.java
Trying to fix split file naming weirdness

@@ -150,7 +150,7 @@ public final class ChunkManager
         final File directory = new File(dir);
         for (File i : directory.listFiles())
         {
-            final File d = new File(rootDir + i.getName().hashCode());
+            final File d = new File(rootDir + i.hashCode());
             d.mkdir();
             this.chunks.add(new Chunk(i, d));
         }

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/Chunk.java
Fixed code changes regarding filed input

@@ -1,9 +1,9 @@
 package edu.unh.schwartz.epframework;
 
 import java.io.BufferedReader;
+import java.io.IOException;
 import java.io.File;
 import java.io.FileReader;
-import java.io.IOException;
 import java.nio.file.Files;
 import org.apache.commons.logging.Log;
 import org.apache.commons.logging.LogFactory;
@@ -30,9 +30,9 @@ public final class Chunk implements Comparable<Chunk>
     private long runtime;
     
     /**
-     * The content of the chunk.
+     * The name of the chunk.
      */
-    private String content;
+    private String name;
 
     /**
      * The directory where the in and out files are saved.
@@ -40,13 +40,13 @@ public final class Chunk implements Comparable<Chunk>
     private File directory;
 
     /**
-     * Constructs a chunk based off some content.
-     * @param content - what the chunk represents
+     * Constructs a chunk.
+     * @param name - the name of the chunk
      * @param directory - the directory for the chunk's IO
      */
-    public Chunk(final String content, final File directory)
+    public Chunk(final String name, final File directory)
     {
-        this.content = content;
+        this.name = name;
         this.directory = directory;
     }
 
@@ -54,37 +54,16 @@ public final class Chunk implements Comparable<Chunk>
      * Constructs a chunk based off a file and the directory for the chunk.
      * @param inFile - the file that contains the chunk's content
      * @param directory - the directory for the chunk's IO
-     * @throws IOException is there is problem copying the file to the directory
-     * or reading the content
+     * @throws IOException if ther is a problem copying the file
      */
     public Chunk(final File inFile, final File directory) throws IOException
     {
         this.directory = directory;
-
-        final StringBuilder sb = new StringBuilder();
-        final BufferedReader br = new BufferedReader(new FileReader(inFile));
-        String line = br.readLine();
-        while (line != null) 
-        {
-            sb.append(line);
-            sb.append('\n');
-            line = br.readLine();
-        }
-        br.close();
-
-        this.content = sb.toString();
+        this.name = inFile.getName();
 
         // Write the content to a file in the directory
         Files.copy(inFile.toPath(), new File(getInFileName()).toPath()); 
 
-    }
-
-    /**
-     * @return the length of the chunk's content
-     */
-    public int length()
-    {
-        return this.content.length();
     }
 
     /**
@@ -212,6 +191,14 @@ public final class Chunk implements Comparable<Chunk>
     }
 
[…]

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/ChunkManager.java

@@ -42,7 +42,10 @@ public final class ChunkManager
      */
     private static final String EXTERNAL_MERGE_EXEC_NAME = "./merger";
 
-    private final String rootDir = "/tmp/";
+    /**
+     * The root diractory for the chunks.
+     */
+    private static final String ROOTDIR = "/tmp/";
 
     /**
      * The pattern used to split the input file.
@@ -115,7 +118,7 @@ public final class ChunkManager
                 final String content = sb.toString();
 
                 // Make a directory for that file
-                final File dir = new File(rootDir + content.hashCode());
+                final File dir = new File(ROOTDIR + content.hashCode());
                 dir.mkdir();
 
                 // Write the content to a file
@@ -150,7 +153,7 @@ public final class ChunkManager
         final File directory = new File(dir);
         for (File i : directory.listFiles())
         {
-            final File d = new File(rootDir + i.getName().hashCode());
+            final File d = new File(ROOTDIR + i.getName());
             d.mkdir();
             this.chunks.add(new Chunk(i , d));
         }
@@ -267,7 +270,7 @@ public final class ChunkManager
         try(final PrintWriter statsOut = new PrintWriter(outDir + "/stats.csv"))
         {
             final String comma = ",";
-            final String header = "Chunk #,Length,Runtime(ms)";
+            final String header = "Chunk #,Runtime(ms)";
             statsOut.print(workerStats);
             LOG.debug(workerStats);
 
@@ -277,8 +280,7 @@ public final class ChunkManager
             {
                 final Chunk c = this.chunks.get(i);
                 final StringBuilder sb = new StringBuilder();
-                sb.append(c.hashCode()).append(comma).append(c.length());
-                sb.append(comma).append(c.getRuntime());
+                sb.append(c.hashCode()).append(comma).append(c.getRuntime());
                 statsOut.println(sb.toString());
                 LOG.debug(sb.toString());
             }

### 2013-12-10 src/main/java/edu/unh/schwartz/epframework/worker/Worker.java

@@ -121,15 +121,16 @@ public final class Worker extends Thread
                 pb.redirectErrorStream(true);
 
                 // Start the work and capture the time it takes to run
-                LOG.info("Starting chunk on Worker " + this.idNum);
+                LOG.info("Starting chunk " + c.getName() + " on Worker " + 
+                        this.idNum);
                 final long start = System.currentTimeMillis();
                 final Process proc = pb.start();
                 proc.waitFor();
                 final long end = System.currentTimeMillis();
                 c.setRuntime(end - start);
                 runTime += (end - start);
-                LOG.info("Finished chunk on Worker " + this.idNum + " in " + 
-                        (end - start));
+                LOG.info("Finished chunk " + c.getName()+ "(Worker " + 
+                        this.idNum + ") in " + (end - start));
             }
             catch (InterruptedException|IOException e)
             {
@@ -171,14 +172,6 @@ public final class Worker extends Thread
                 commands.add(a);
             }
         }
-
-        // System.out.println("\n\n\n");
-        // for(String co : commands)
-        // {
-            // System.out.print(co);
-            // System.out.print(" ");
-        // }
-        // System.out.println();
 
         return new ProcessBuilder(commands);
     }

### 2013-12-10 paper/paper.tex
More paper changes. Tables etc

@@
 embarrassingly parallel programs in the biological sciences. Basic Local
-Alignment Search Tool, or BLAST\fotenote{blast.ncbi.nlm.nih.gov}, is an
+Alignment Search Tool, or BLAST\footnote{blast.ncbi.nlm.nih.gov}, is an
 algorithm that compares many aspects of DNA sequences, like the nucleotides or
@@
 A version of octupus was also run through the framework and was tested against
-two different sized data sets. Both sets were first clustered at 90\% similarity
-and the resulting clusters were used as the input for the framework's run, which
-is for 97\% similarity. The framework in this case was just run at four and
-eight threads and Figure \ref{fig:octugraph} shows that the running the
-framework once again provides a benefit for the user.
+two different sized data sets. Both sets were first clustered at 90\%, 95\% and
+97\% minimum similarity. The runtime for those tests can be seen in table
+\ref{tab:oct1}. The resulting clusters from the 90\% similarity run were used as
+the input for the framework's runs, which were all set for 97\% similarity. 
+The framework in this case was just run at six, eight and ten workers. Table 
+\ref{tab:octu2} shows that it is slightly faster to cluster first at 90\% and 
+then run the resulting clusters through the framework at a higher similarity.
 
-\begin{figure}
-{\resizebox{5.2in}{!}{\includegraphics{experiment/outoctu.png}}}
-\caption{Runtimes for the Ka/Ks Calculator though the framework}
-\label{fig:octugraph}
-\end{figure}
+\begin{table}
+    \begin{tabular}{|l|l|l|}
+        \hline
+        Number of Sequences & Minimum Similarity & Time(s) \\ \hline
+        1500                & 90\%               & 99      \\
+        ~                   & 95\%               & 115     \\
+        ~                   & 97\%               & 131     \\ \hline
+        6500                & 90\%               & 425     \\
+        ~                   & 95\%               & 496     \\
+        ~                   & 97\%               & 603     \\ \hline
+    \end{tabular}
+    \label{tab:octu1}
+\end{table}
+
+\begin{table}
+    \begin{tabular}{|l|l|l|}
+        \hline
+        Number of Sequences & Number of Workers & Time(s) \\ \hline
+        1500                & 6                 & 34      \\
+        ~                   & 8                 & 27      \\
+        ~                   & 10                & 27      \\ \hline
+        6500                & 6                 & 127     \\
+        ~                   & 8                 & 127     \\
+        ~                   & 10                & 123     \\ \hline
+    \end{tabular}
+    \label{tab:octu2}
+\end{table}
 

### 2013-12-11 paper/paper.tex
more paper stuff

@@
 \usepackage{cite}
-\usepackage{wrapfig}
+\usepackage{floatrow}
 
@@
 
-\begin{wrapfigure}{R}{0.5\textwidth}
+\begin{figure}
     \begin{center}
@@
     \caption{Embarrassingly Parallel Model}
+    \floatfoot{http://www.coopsoft.com/ar/i/fjGraph.jpg}
     \label{fig:ep}
-\end{wrapfigure}
+\end{figure}
 
@@
 
+\begin{figure}
+    \begin{center}
+        \resizebox{4.7in}{!}{\includegraphics{figures/MapReduce.jpg}}
+    \end{center}
+    \caption{MapReduce Model}
+    \label{fig:map}
+    \floatfoot{http://dme.rwth-aachen.de/en/system/files/file\_upload/project/MapReduce.jpg}
+\end{figure}
+
 Amazon also offers another service called Amazon Elastic
@@
 
-\begin{wrapfigure}{L}{0.5\textwidth}
-    \begin{center}
-        \includegraphics{figures/MapReduce.jpg}
-    \end{center}
-    \caption{MapReduce Model}
-    \label{fig:map}
-\end{wrapfigure}
-
 \section{Proposed Solution}
 \begin{figure}
-{\resizebox{5.2in}{!}{\includegraphics{figures/uml.png}}}
+    \begin{center}
+        \resizebox{4.7in}{!}{\includegraphics{figures/uml.png}}
+    \end{center}
     \caption{UML for the embarrassingly parallel framework}
@@
 \end{figure}
+
 The only requirements for a program to be wrapped by framework are that it 
@@
 \begin{figure}
-{\resizebox{5.2in}{!}{\includegraphics{experiment/out.png}}}
+    \begin{center}
+        \resizebox{5.2in}{!}{\includegraphics{experiment/time.png}}
+    \end{center}
     \caption{Runtimes for the Ka/Ks Calculator though the framework}
@@
 97\% minimum similarity. The runtime for those tests can be seen in table
-\ref{tab:oct1}. The resulting clusters from the 90\% similarity run were used as
+\ref{tab:octu1}. The resulting clusters from the 90\% similarity run were used as
 the input for the framework's runs, which were all set for 97\% similarity. 
@@
 \begin{table}
+    \begin{center}
     \begin{tabular}{|l|l|l|}
@@
     \end{tabular}
+    \caption{Times from serial octupus at various similarity levels.}
+    \end{center}
     \label{tab:octu1}
@@
     \end{tabular}
+    \caption{Times from octupus through the framework at 97\% similarirty.}
+    \end{center}
     \label{tab:octu2}

### 2013-12-11 paper/paper.tex
more paper stuff

@@
 
-\doublespacing
+% \doublespacing
 \begin{document}
@@
 similar service named Microsoft Azure\footnote{https://www.windowsazure.com}.
-AWS and Azure are essentially virtual instances run on machines in the cloud that
-can be spun up for extra computing power and shut down when not needed.
+AWS and Azure are essentially virtual instances run on machines in the cloud
+that can be spun up for extra computing power and shut down when not needed.
 
@@
     \begin{center}
-        \resizebox{5.2in}{!}{\includegraphics{experiment/time.png}}
+        \resizebox{4.7in}{!}{\includegraphics{experiment/time.png}}
     \end{center}
     \caption{Runtimes for the Ka/Ks Calculator though the framework}
-    \label{fig:kaksgraph}
+    \label{fig:time}
 \end{figure}
 
-Figure \ref{fig:kaksgraph} summarized the results; each line shows the time
-taken for each chunk of the data. As the numbers of threads increases, the
-runtime of the program decreases exponentially. In a few cases, there was an
-increase in time when attempting to max out the CPU usage. This occurs because
-the framework has to wait for the CPU to be finished with its previous work
-before it can start any further jobs.
+\begin{figure}
+    \begin{center}
+        \resizebox{4.7in}{!}{\includegraphics{experiment/speedup.png}}
+    \end{center}
+    \caption{Speedup of Ka/Ks Calculator program}
+    \label{fig:speedup}
+\end{figure}
 
-TODO(Keep?): In the cases when the framework executed faster while the CPU was 
-maxed out, it was only faster a minute at the most. However, running the 
-framework at 50\% of the CPU is more efficient than running using 100\% of the 
-CPU. The runtime drop achieved when using 100\% of the CPU versus 50\% is not 
-large enough to warrant using all of the machine's power.
+Figure \ref{fig:time} summarized the results; each line shows the time taken for
+each chunk of the data. As the numbers of threads increases, the runtime of the
+program decreases exponentially. In a few cases, there was an increase in time
+when attempting to max out the CPU usage. This occurs because the framework has
+to wait for the CPU to be finished with its previous work before it can start
+any further jobs.
 
+Figure \ref{fig:speedup} shows the speedup of the Ka/Ks Calculator program. 
+In most of the samples, the speedup seems to level off between 6 to 10 workers,
+and even goes down when increased to 16 workers. Running the framework at 50\% 
+of the CPU is more efficient than running using 100\% of the CPU in this 
+situation. The decrease in speedup from 8 workers to 16 workers shows that TODO.
+This is not true of all case, as seen in sample E. This sample has a higher
+speedup at 16 workers because the piece of work that comes Xth in the sample
+takes the longest. With 16 workers, this chunk is started immediately instead of
+most of the way through the total runtime of the framework.
 \subsection{Octupus}
@@
     \end{tabular}
-    \caption{Times from serial octupus at various similarity levels.}
+    \caption{Times from serial octupus at various similarity levels}
     \end{center}
@@
     \end{tabular}
-    \caption{Times from octupus through the framework at 97\% similarirty.}
+    \caption{Times from octupus through the framework at 97\% similarirty}
     \end{center}
@@
 add parallelism to a specific class of file-oriented embarrassingly parallel
-problems. Two sentences with specifics from the graphs. More self-praise
+problems. Two sentences with specifics from the graphs. More self-praise TODO
 
@@
 \bibitem{cloud}
-Crap, crap and Crap
+Gunarathne, T., Wu, T.-L., Choi, J. Y., Bae, S.-H. and Qiu, J., \emph{Cloud
+computing paradigms for pleasingly parallel biomedical applications},
+Concurrency and Computation: Practice and Experience, December 2011.
 \end{thebibliography}

### 2013-12-12 paper/paper.tex
MORE PAPER

@@
 of the CPU is more efficient than running using 100\% of the CPU in this 
-situation. The decrease in speedup from 8 workers to 16 workers shows that TODO.
+situation. The decrease in speedup from 8 workers to 16 workers shows this.
 This is not true of all case, as seen in sample E. This sample has a higher
-speedup at 16 workers because the piece of work that comes Xth in the sample
-takes the longest. With 16 workers, this chunk is started immediately instead of
-most of the way through the total runtime of the framework.
+speedup at 16 workers because there are multiple piece of work toward the end
+that take a majority of the runtime. With 16 workers, these chunks were started
+immediately instead of late during the total runtime of the framework.
+
 \subsection{Octupus}
@@
 add parallelism to a specific class of file-oriented embarrassingly parallel
-problems. Two sentences with specifics from the graphs. More self-praise TODO
+problems. Speedup of 4x can be achieved on simple samples with the same number
+of chunks as workers, and possibly slightly higher with real data, as seen with
+the octupus data. While many consumer-level computers will not have many options
+when it comes to chosing the proccesing power, the framework will help
+universities and companies who have the raw computing power, and are just not
+using it to their full potential.
 

### 2013-12-12 paper/paper.tex
audreys revision

@@
 to find the solution. Many problems in the biological sciences are
-embarrassingly parallel but often their authors do not have the expertise to
+embarrassingly parallel, but often their authors do not have the expertise to
 implement a parallel solution. We have written a framework, implemented in Java,
@@
 step is to separate the framework into a front-end that will run locally and a
-back-end which receives blocks of work and does the computations. This back-end
+back-end, which receives blocks of work and does the computations. This back-end
 should run in the cloud, on a machine that is dedicated to running
@@
 
-A computation graph consists of nodes that represent the functions or processes.
+A computation graph consists of nodes that represent the functions or processes,
 and edges that represent data being passed. If the graph is fully disconnected,
@@
 handling large file sizes, there is a lot of processing that goes into comparing
-and manipulating strings. This time adds up when there are hundreds of thousands
-of strings to process. However, these sequences often do not relate to each
-other and can be processed independently. Using an embarrassingly parallel
+and manipulating strings. The overall runtime adds up when there are hundreds of
+thousands of strings to process. However, these sequences often do not relate to
+each other and can be processed independently. Using an embarrassingly parallel
 approach, the processing time for all of the sequences can often be cut down
@@
 
-This paper describes a framework that makes it easy to parallelize a potentially
+This paper describes a framework that makes it easy to parallelize an
 embarrassingly parallel program that reads from a file, writes to a file and
@@
 subset of the input in the same manner and creating the output in the same
-format. The framework can result in a significant exponential decrease with very
-little programmer effort.
+format. The framework provides a ``wrapper'' for the original program, which is
+called on multiple Java threads. Each thread acts like the serial application,
+reading a subset of the input in the same manner. The output from the framework
+is also in the same format as the result of the serial program. Using the
+framework can cause a significant exponential decrease with very little
+programmer effort.
 
+%TODO
 \begin{figure}
@@
 Desi, are very different in size and color. The Desi is also more resistant to
-diseases and is more effective at root nodule symbiosis. The Kabuli has a large
+diseases and is more effective at root nodule symbiosis. The Kabuli has a large,
 but soft shell, which makes it a better food source for humans. Both forms are
@@
 variants, each with thousands of sequences. The Ka/Ks Calculator program took
-between five to thirty seconds to process one pair of sequences on a ordinary
+between five to thirty seconds to process one pair of sequences on an ordinary
 machine.
@@
 the expertise to develop a new parallel Ka/Ks program. We were also reluctant to
-revise the existing code to to implement the parallel computation because of the
+revise the existing code to implement the parallel computation because of the
 danger of introducing bugs into unfamiliar code and because of the learning
-curve required for C++ threading. Instead we wrote, a simple Java program to
+curve required for C++ threading. Instead we wrote a simple Java program to
 break up the input and spawn threads that would run the Ka/Ks Calculator process
-without having to make any changes to the code. When al of the threads ended,
+without having to make any changes to the code. When all of the threads ended,
 the contents of the output files were concatenated together to produce a final
@@
 Alignment Search Tool, or BLAST\footnote{blast.ncbi.nlm.nih.gov}, is an
-algorithm that compares many aspects of DNA sequences, like the nucleotides or
-amino acid sequences. In addition, the user can also compare to the sequences to
-a database of sequences to identity known subservience's. There are many
-implementations of BLAST, some of them already have parallel implementations.
-Many applications however do not have parallel processing capabilities. A class
-of problems that organize large amounts of data into similar groups called
+algorithm that compares many aspects of DNA sequences, like nucleotides or amino
+acid sequences. In addition, the user can also compare the sequences to a
+database of sequences to identity known subservience's. There are many
+implementations of BLAST, some of them already have parallel versions.  Hovever,
+many applications do not have parallel processing capabilities. There exists a
+class of problems that organize large amounts of data into similar groups called
 clusters. Two applications, octupus\footnote{octupus.sourceforge.com} and
@@
 
-This framework is designed to run locally but there are other options when more
+This framework is designed to run locally, but there are other options when more
 power is needed. Gunarathne et al.\cite{cloud} have investigated running much
@@
 services. These services offer on-demand computational power with flexibility.
-These services have built in hooks to various distributed services, such as
+These services have built-in hooks to various distributed services, such as
 storage and databases. Amazon has a set of cloud computing services called
@@
 DryadLINQ\footnote{https://research.microsoft.com/apps/mobile/showpage.aspx?page=/en-us/projects/draydlinq}
-is a framework developed released by Microsoft Research that allows the end-user
-to create directed acyclic computation graphs that run on Windows High
-Performance Computer(HPC)\footnote{https://www.microsoft.com/hpc} clusters.
-Gunarathne et al. compared the services using several applications to analyze
-performance, cost and usability.
+is a framework developed by Microsoft Research that allows the end-user to
+create directed acyclic computation graphs that run on Windows High Performance
+Computer(HPC)\footnote{https://www.microsoft.com/hpc} clusters.  Gunarathne et
+al. compared the services using several applications to analyze performance,
+cost and usability.
 
@@
 
-The only requirements for a program to be wrapped by framework are that it
-process the input in an embarrassingly parallel manner and that the input comes
-from a file. The processed results must also written to a file. The framework
-supports two forms of input: a directory of files that contain that each contain
+The only requirements for a program to be wrapped by our framework are that it
+processes the input in an embarrassingly parallel manner and that the input comes
+from a file. The framework, shown in figure \ref{fig:uml}, supports two forms of input: a directory of files that each contain
 one unit of work, which is represented by the Chunk class, or a single file that
@@
 done, all of the separate results are spread across several files. Those results
-must be retrieved and combined to construct the final output file. This output
+must be retrieved and combined to construct the final output file. CONTINUED
+
+This output
 file must look the same as the output file would look if the program were run
@@
 
+REWRITE ABOVE
+
 The end-user can control many aspects of the parallelization of the code,
-including the number of threads to use, various flags for the executable and the
+including the number of threads to use, various flags for the executable, and the
 statistics output.  A start-up wizard allows the end-user to choose the settings
@@
 Lastly, the worker threads keep records during execution. The threads record
-their total uptime and the number of Chunks they execute, and the runtime for
+their total uptime, the number of Chunks they execute, and the runtime for
 each piece of work. This information will be used to evaluate the effectiveness
 of the approach, but can also provide useful information the can help a user
-tine a particular application on a particular type of input data. The statistics
+time a particular application on a particular type of input data. The statistics
 for each thread can be found in the Worker subclass and the individual Chunk
@@
 containing sixteen units of work. Each sample was run by the framework thread
-counts, starting at 1 and increasing by multiple of two until the runtimes
+counts, starting at 1 and increasing by multiples of two until the runtimes
 leveled off. The samples were then all run again at 100\% processor usage (16
@@
 and even goes down when increased to 16 workers. Running the framework at 50\% 
-of the CPU is more efficient than running using 100\% of the CPU in this 
+of the CPU is more efficient than running at 100\% of the CPU in this 
 situation. The decrease in speedup from 8 workers to 16 workers shows this.
-This is not true of all case, as seen in sample E. This sample has a higher
-speedup at 16 workers because there are multiple piece of work toward the end
+This is not true for all cases, as seen in sample E. This sample has a higher
+speedup at 16 workers because there are multiple pieces of work toward the end
 that take a majority of the runtime. With 16 workers, these chunks were started
-immediately instead of late during the total runtime of the framework.
+immediately instead of later during the total runtime of the framework.
 
@@
 the input for the framework's runs, which were all set for 97\% similarity. 
-The framework in this case was just run at six, eight and ten workers. Table 
+The framework in this case was run at six, eight and ten workers. Table 
 \ref{tab:octu2} shows that it is slightly faster to cluster first at 90\% and 
@@
 extension by others, but it may not produce the fastest results. Languages like
-Hadoop, Clojure or other multithread oriented language may have been a better
+Hadoop, Clojure or other multithread oriented languages may have been a better
 choice due to their inherit parallel nature. In addition to a single machine
@@
 by using MPI or a cloud solution like Amazon instances. The MapReduce framework
-works similarly to our framework, there is a step that splits the data, the Map
-function is the user's executable and the merge step is the Reduce function in
+works similarly to our framework; there is a step that splits the data, the Map
+function is the user's executable, and the merge step is the Reduce function in
 the framework.

### 2013-12-12 examples/octupus/octu3.pl
Removed old example stuff

@@ -1,2007 +1,0 @@
-#!/usr/bin/perl
-#---  octu3.pl  - rdb derived from octu2.pl on 4/27/12
-#                 besides preserving existing code to simplify later 
-#                 (possibly extensive) comparisons. 
-#                 Goal of this version is to get all satisfactory hits
-#                 and pick the one with the longest match region -- or 
-#                 possibly other criteria.
-#
-# Way Sung 10/2008
-# Edited by Dan Bergeron March/April 2012
-#
-# rdb: This version is an attempt to reduce the i/o. It maintains all 
-#      octu information in hash tables, so it never needs to re-read it; it
-#      still needs to append to the octulist file when a new octu is created
-#      and re-write it whenever an octu's consensus is changed.
-#---------------------------------------------------------------------
-#    This file is part of OCTUPUS.
-
-#    OCTUPUS is free software: you can redistribute it and/or modify
-#    it under the terms of the GNU General Public License as published by
-#    the Free Software Foundation, either version 3 of the License, or
-#    (at your option) any later version.
-
-#    OCTUPUS is distributed in the hope that it will be useful,
-#    but WITHOUT ANY WARRANTY; without even the implied warranty of
-#    MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
-#    GNU General Public License for more details.
-
-#    You should have received a copy of the GNU General Public License
-#    along with OCTUPUS.  If not, see <http://www.gnu.org/licenses/>.
-#
-# History as of 03/29/2012 rdb
-#----------------- octu2.pl -----------------------------------------------
-# 03/29-4/5/2012 rdb
-#    Functional changes
-#    1. revised finishing code that used "sed"; it didn't work on Mac OS X
-#    2. changed command line parameter conventions and checking
-#          -test for non-numeric and invalid % and length
-#          -changed default directory to one composed of fasta file name, 
-#           % and min length such as: harvardSite_95_100. To use cwd, use "."
-#    3. Found bug in test for recomputing consensus; code tested exactMatchCount
-#       for the octu (%matchNum) rather than the octu count (%octuCount). This
-#       should actually give better results (for more time) since it was
-#       essentially nearly always recomputing the consensus.
-#       For a 500 sequence test, the matchNum version is about 50% slower than
-#       the octuCount version (32 secs vs 22 secs on macbook air). The octu
-#       result differences were very small; it looks like all the octus were
[…]

### 2013-12-13 paper/paper.tex
done paper

@@
 
-%TODO
 \begin{figure}
@@
 database of sequences to identity known subservience's. There are many
-implementations of BLAST, some of them already have parallel versions.  Hovever,
+implementations of BLAST, some of them already have parallel versions.  However,
 many applications do not have parallel processing capabilities. There exists a
@@
 virtual instance framework with Apache
-Hadoop\footnote{https://hadoop.apache.org}. As seen in figure \ref{fig:map},
+Hadoop\footnote{https://hadoop.apache.org}. As seen in Figure \ref{fig:map},
 Hadoop breaks down the input data into parts, runs them in parallel with the
@@
 The only requirements for a program to be wrapped by our framework are that it
-processes the input in an embarrassingly parallel manner and that the input comes
-from a file. The framework, shown in figure \ref{fig:uml}, supports two forms of input: a directory of files that each contain
-one unit of work, which is represented by the Chunk class, or a single file that
-the framework can break up into Chunks. For example, the Ka/Ks Calculator's
-input consists of a header and then two protein sequence lines followed by a
-blank line. The framework uses that blank line to know when one Chunk of work
-has ended and another has begun. The user can input a regular expression to
-define when lines of input are separated into Chunks. This occurs in the
-ChunkManager class.
+processes the input in an embarrassingly parallel manner and that the input
+comes from a file. The framework, shown in Figure \ref{fig:uml}, supports two
+forms of input: a directory of files that each contain one unit of work, which
+is represented by the Chunk class, or a single file that the framework can break
+up into Chunks. For example, the Ka/Ks Calculator's input consists of a header
+and then two protein sequence lines followed by a blank line. The framework uses
+that blank line to know when one Chunk of work has ended and another has begun.
+The user can input a regular expression to define when lines of input are
+separated into Chunks. This occurs in the ChunkManager class.
 
@@
 done, all of the separate results are spread across several files. Those results
-must be retrieved and combined to construct the final output file. CONTINUED
-
-This output
-file must look the same as the output file would look if the program were run
-serially; the output may need to come in the same order as the inputs in the
-input file and headers may need to be deleted from the separate files and added
-to the combined file. End-users can also choose to write their own merge code in
-Java, using the CustomMerge class, or write their own independent merge script.
-
-REWRITE ABOVE
+must be retrieved and combined to construct the final output file. This combined
+output file looks as if the program were run serially: the output must come in
+the same order and the headers need to be added. End-users can also choose to
+write their own merge code in Java, using the CustomMerge class, or write their
+own independent merge script.
 
 The end-user can control many aspects of the parallelization of the code,
-including the number of threads to use, various flags for the executable, and the
-statistics output.  A start-up wizard allows the end-user to choose the settings
-for the run and creates an instance of Configuration when it is completed to
-save the user's settings, allowing the user to rerun with the same settings
-without having to go through the wizard again.
+including the number of threads to use, various flags for the executable, and
+the statistics output.  A start-up wizard allows the end-user to choose the
+settings for the run and creates an instance of Configuration when it is
+completed to save the user's settings, allowing the user to rerun with the same
+settings without having to go through the wizard again.
 
@@
 applications: the Ka/Ks Calculator and a sequence clustering algorithms,
-ocutupus. In all cases, we compared the framework based application with the
+octupus. In all cases, we compared the framework based application with the
 original using different data partitions and different thread counts.
@@
 \subsection{Ka/Ks Calculator}
+
 Ka/Ks Calculator was run through the framework with five different samples, each
-containing sixteen units of work. Each sample was run by the framework thread
-counts, starting at 1 and increasing by multiples of two until the runtimes
-leveled off. The samples were then all run again at 100\% processor usage (16
-processors). These tests were run with minimal other activity on the server.
+containing sixteen units of work. Each sample was run with a range of thread
+counts, starting at 1 and increasing by a multiple of two until the runtimes
+leveled off and then once more with the maximum 16 processors. These tests were
+run with minimal other activity on the server.
 
@@
 
-Figure \ref{fig:time} summarized the results; each line shows the time taken for
+Figure \ref{fig:time} summarizes the results; each line shows the time taken for
 each chunk of the data. As the numbers of threads increases, the runtime of the
-program decreases exponentially. In a few cases, there was an increase in time
-when attempting to max out the CPU usage. This occurs because the framework has
-to wait for the CPU to be finished with its previous work before it can start
-any further jobs.
+program decreases exponentially for a while and then begins to flatten between 6
+and 10 processors. In a few cases, there was an increase in time when attempting
+to max out the CPU usage. This occurs because the framework has to wait for the
+CPU to be finished with its previous work before it can start any further jobs.
+Figure \ref{fig:speedup} shows the speedup of the Ka/Ks Calculator program.  In
+most of the samples, the speedup seems to level off between 6 to 10 workers, and
+even goes down when increased to 16 workers. Running the framework at 50\% of
+the CPU is more efficient than running at 100\% of the CPU in this situation.
+The decrease in speedup from 8 workers to 16 workers shows this.
 
-Figure \ref{fig:speedup} shows the speedup of the Ka/Ks Calculator program. 
-In most of the samples, the speedup seems to level off between 6 to 10 workers,
-and even goes down when increased to 16 workers. Running the framework at 50\% 
-of the CPU is more efficient than running at 100\% of the CPU in this 
-situation. The decrease in speedup from 8 workers to 16 workers shows this.
 This is not true for all cases, as seen in sample E. This sample has a higher
@@
 that take a majority of the runtime. With 16 workers, these chunks were started
-immediately instead of later during the total runtime of the framework.
+immediately instead of later during the total runtime of the framework. Another
+random sample was taken to show that sample E was an anomaly. This sample had
+similar runtimes at 8 and 16 workers, resulting in a negligible speedup increase
+when going up to 100\% of the CPU. This random sample behaving similarly to the
+majority of the sample shows that sample E behaved differently due to having a
+majority of its work later in the file. Some tests were run in the early stages
+of development to observe the behavior of sorting the data by length. In terms
+of Ka/Ks, there was no correlation between length of sequences and calculation
+time, so there was no way to sort the data to ensure the chunks of work that
+take the quickest segments happen last. This would prevent anomalies like sample
+E.
 
@@
 two different sized data sets. Both sets were first clustered at 90\%, 95\% and
-97\% minimum similarity. The runtime for those tests can be seen in table
-\ref{tab:octu1}. The resulting clusters from the 90\% similarity run were used as
-the input for the framework's runs, which were all set for 97\% similarity. 
-The framework in this case was run at six, eight and ten workers. Table 
-\ref{tab:octu2} shows that it is slightly faster to cluster first at 90\% and 
-then run the resulting clusters through the framework at a higher similarity.
+97\% minimum similarity with only one processor. The runtime for those tests can
+be seen in Table \ref{tab:octu1}. The resulting clusters from the 90\%
+similarity run were used as the input for the framework's runs, which were all
+set for 97\% similarity.  The framework in this case was run at six, eight and
+ten workers. Table \ref{tab:octu2} shows that it is slightly faster to cluster
+first at 90\% and then run the resulting clusters through the framework at a
+higher similarity.
 
@@
     \caption{Times from serial octupus at various similarity levels}
+    \label{tab:octu1}
     \end{center}
-    \label{tab:octu1}
 \end{table}
@@
         Number of Sequences & Number of Workers & Time(s) \\ \hline
-        1500                & 6                 & 34      \\
-        ~                   & 8                 & 27      \\
-        ~                   & 10                & 27      \\ \hline
-        6500                & 6                 & 127     \\
-        ~                   & 8                 & 127     \\
-        ~                   & 10                & 123     \\ \hline
+        1500                & 6                 & 133      \\
+        ~                   & 8                 & 126      \\
+        ~                   & 10                & 126      \\ \hline
+        6500                & 6                 & 552     \\
+        ~                   & 8                 & 552     \\
+        ~                   & 10                & 548     \\ \hline
     \end{tabular}
-    \caption{Times from octupus through the framework at 97\% similarirty}
+    \caption{Times from octupus through the framework at 97\% similarity}
+    \label{tab:octu2}
     \end{center}
-    \label{tab:octu2}
 \end{table}
@@
 the octupus data. While many consumer-level computers will not have many options
-when it comes to chosing the proccesing power, the framework will help
+when it comes to choosing the processing power, the framework will help
 universities and companies who have the raw computing power, and are just not
